### 2017-09-12 writing/draft.Rmd
added paper draft and notes

---
title: "deconvolve: a protocol and R package for thermogravimetric decay curve deconvolution for lignocellulosic biomass trait calculation"
author: "Saras M Windecker & Nick Golding"
date: "12/09/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

_Fraser-Suzuki deconvolution_
This equation flow comes from Chen et al 2017..

The key function in the deconvolve package, for which it is eponymously named, executes the three-part Fraser-Suzuki mixture model, using the following math (awkward...).

The Fraser-Suzuki function, due to its asymmetry, has been found to well predict kinetic curves and therefore be useful for deconvolution of parallel independent processes. The Fraser-Suzuki function is expressed as follows:

$y = h\ exp\bigg\{-\frac{ln2}{s^2}\Big[ln\Big(1 + 2s \frac{x- p}{w}\Big)\Big]^2\bigg\}$

where T is the independent variable, in this case temperature, and the parameters h, s, p, and w are height, skew, position, and width of the curve, respectively. The rate expression ($d\alpha/dT$) for a single curve can be written as follows:

$\frac{d\alpha}{dT} = h\ exp\bigg\{-\frac{ln2}{s^2}\Big[ln\Big(1 + 2s \frac{T- p}{w}\Big)\Big]^2\bigg\}$

$\alpha = \frac{M_0 - M_T}{M_0 - M_f}$

where $\alpha$ is the conversion of mass from the start to the final temperature, given the initial: M is the dimensionless weight of the sample at initial temperature ($M_0$), at a given temperature ($M_T$), and at final temperature ($M_f$). Because we are assuming independent reactions by the three main pseudo components, mass loss rate is expressed as follows:

$-\frac{dm}{dT} = \sum\limits_{i=1}^3 c_i\frac{d\alpha_{i}}{dT}$

$c_i = M_{0,i} - M_{char,i}$

$m = \frac{M_T}{M_0}$

where $c_i$ is the mass of pseudo component _i_ that is decayed, _i_ = 1, 2, and 3 refer to pseudo hemicellulose, pseudo cellulose, and pseudo lignin, respectively. $M_{0,i}$ and $M_{char,i}$ are the mass of the initial and final pyrolysis of the _i_-th component, respectively. When we introduce the Fraser-Suzuki function, the deconvolution can be expressed as:

$-\frac{dm}{dT} = \sum\limits_{i=1}^3 c_if_i(T)$

where $f_i(T)$ represents the Fraser-Suzuki function with parameters $h_i$, $s_i$, $p_i$, and $w_i$. In total the model estimates 12 parameters, one of each of the former for each of the three pseudo components. These are estimated using the nls.lm function as part of the minpack.lm package, which minimises the sum square of the vector returned by the function. The objective function used is the root mean square error of the predicted rate compared to the observed.

** input expression here for rmse? **

The deconvolve function returns a normal model output, from which users can extract parameter estimates themselves.

(talk about next function and add equations for back calculating the mass of each PC)

### 2017-09-14 R/fs_function.R
don't export descriptions from these functions

@@ -1,16 +1,14 @@
-#' Fraser-Suzuki function
-#'
-#' This function calculates the Fraser-Suzuki function.
-#'
-#' @param x temperature values
-#' @param h height value
-#' @param s shape value
-#' @param p position value
-#' @param w width value
-#' @return Fraser-Suzuki model output
-#' @keywords internal
-#'
-#' @export
+# Fraser-Suzuki function
+#
+# This function calculates the Fraser-Suzuki function.
+#
+# @param x temperature values
+# @param h height value
+# @param s shape value
+# @param p position value
+# @param w width value
+# @return Fraser-Suzuki model output
+# @keywords internal
 
 # Frazer-Suzuki function
 fs_function <- function (x, h, s, p, w) {

### 2017-09-14 R/fs_mixture.R

@@ -1,13 +1,11 @@
-#' Fraser-Suzuki three-part mixture
-#'
-#' This function combines three Fraser-Suzuki functions for the total mixture model.
-#'
-#' @param x temperature values
-#' @param params parameter starting values
-#' @return Fraser-Suzuki mixture model output
-#' @keywords internal
-#'
-#' @export
+# Fraser-Suzuki three-part mixture
+#
+# This function combines three Fraser-Suzuki functions for the total mixture model.
+#
+# @param x temperature values
+# @param params parameter starting values
+# @return Fraser-Suzuki mixture model output
+# @keywords internal
 
 # combine the FS function three times for the three pseudo-components
 fs_mixture <- function (x, params) {

### 2017-09-14 R/fs_mixture_wrap.R

@@ -1,22 +1,22 @@
-#' Wrapper for Fraser-Suzuki mixture model
-#'
-#' This function is a wrapper for the fsTotal function that modifies so it uses all 12 parameters as input.
-#'
-#' @param x temperature values
-#' @param h1 height value pc1
-#' @param h2 height value pc2
-#' @param h3 height value pc3
-#' @param s1 shape value pc1
-#' @param s2 shape value pc2
-#' @param s3 shape value pc3
-#' @param p1 position value pc1
-#' @param p2 position value pc2
-#' @param p3 position value pc3
-#' @param w1 width value pc1
-#' @param w2 width value pc2
-#' @param w3 width value pc3
-#' @return three-part Fraser-Suzuki mixture model output
-#' @keywords internal
+# Wrapper for Fraser-Suzuki mixture model
+#
+# This function is a wrapper for the fsTotal function that modifies so it uses all 12 parameters as input.
+#
+# @param x temperature values
+# @param h1 height value pc1
+# @param h2 height value pc2
+# @param h3 height value pc3
+# @param s1 shape value pc1
+# @param s2 shape value pc2
+# @param s3 shape value pc3
+# @param p1 position value pc1
+# @param p2 position value pc2
+# @param p3 position value pc3
+# @param w1 width value pc1
+# @param w2 width value pc2
+# @param w3 width value pc3
+# @return three-part Fraser-Suzuki mixture model output
+# @keywords internal
 
 # create wrapper to separately identify the 12 parameters
 fs_mixture_wrap <- function (x, h1, h2, h3, s1, s2, s3, p1, p2, p3, w1, w2, w3) {

### 2017-09-14 R/fs_model.R

@@ -1,13 +1,13 @@
-#' Non-linear model using Fraser-Suzuki mixture model
-#'
-#' Non-linear model output using optimised parameter values
-#' with a three-part mixture model using Fraser-Suzuki equation
-#'
-#' @param dataframe dataframe
-#' @param params starting parameter values
-#' @return model output
-#' @keywords internal
-#' @import minpack.lm
+# Non-linear model using Fraser-Suzuki mixture model
+#
+# Non-linear model output using optimised parameter values
+# with a three-part mixture model using Fraser-Suzuki equation
+#
+# @param dataframe dataframe
+# @param params starting parameter values
+# @return model output
+# @keywords internal
+# @import minpack.lm
 
 # function to do the nls fit with the correct starting values
 fs_model <- function (dataframe, params) {

### 2017-09-14 R/param_select.R

@@ -1,15 +1,15 @@
-#' Optimise parameters
-#'
-#' This function otimises parameter selection so that the model will ultimately converge.
-#'
-#' @param theta vector of starting values for each of 12 parameters
-#' @param lb vector of lower bounds on each of 12 parameters
-#' @param model mathematical function to be applied
-#' @param x temperature values
-#' @param obs DTG mass values
-#' @return optimised starting parameter values
-#' @keywords internal
-#' @import nloptr
+# Optimise parameters
+#
+# This function otimises parameter selection so that the model will ultimately converge.
+#
+# @param theta vector of starting values for each of 12 parameters
+# @param lb vector of lower bounds on each of 12 parameters
+# @param model mathematical function to be applied
+# @param x temperature values
+# @param obs DTG mass values
+# @return optimised starting parameter values
+# @keywords internal
+# @import nloptr
 
 # create params_opt with this function
 param_select <- function (theta, lb, model, x, obs, restarts = 300) {

### 2017-09-14 R/rmse.R

@@ -1,11 +1,11 @@
-#' Calculate room mean squared error
-#'
-#' This function calculated root mean squarer error of prediction.
-#'
-#' @param pred predicted parameter value
-#' @param obs DTG mass values
-#' @return root mean squared error
-#' @keywords internal
+# Calculate room mean squared error
+#
+# This function calculated root mean squarer error of prediction.
+#
+# @param pred predicted parameter value
+# @param obs DTG mass values
+# @return root mean squared error
+# @keywords internal
 
 rmse <- function (pred, obs) {
   sqrt(sum((obs - pred) ^ 2))

### 2017-09-14 R/mass_fractions.R
formatting

@@ -12,6 +12,7 @@
 #' 1, 2, and 3
 #' @keywords thermogravimetry fraser-suzuki deconvolution
 #' @importFrom stats integrate setNames
+#'
 #' @export
 
 #t <- mass_fractions(model, 400, 900, 18.9615, test$m_T)

### 2017-09-14 R/tga_process.R

@@ -13,7 +13,7 @@
 #' @return new dataframe
 #' @keywords derivative
 #' @import plyr
-
+#'
 #' @export
 
 tga_process <- function (data, temp, mass_loss, mass_init, lower, upper) {

### 2017-09-14 writing/draft.Rmd
writing updates

@@
 
-The Fraser-Suzuki function, due to its asymmetry, has been found to well predict kinetic curves and therefore be useful for deconvolution of parallel independent processes.
+The Fraser-Suzuki function, due to its asymmetry, is useful for predicting kinetic curves and therefore useful for the deconvolution of parallel independent processes.
 The Fraser-Suzuki function is expressed as follows:

### 2017-09-22 vignettes/Figures/three_graphs.R
revise Figure

@@ -1,9 +1,12 @@
 library(deconvolve)
 
-data(raw_data)
-raw_data$temp_K <- raw_data$temp_C + 273
-munge_data <- tga_process(raw_data, 'temp_K', 'mass_loss', 18.9615, 400, 900)
-fit <- deconvolve(munge_data, munge_data$temp_K, munge_data$deriv)
+data(juncus)
+output <- deconvolve(juncus, 'temp_C', 'mass_loss', 18.96, temp_type = 'C')
+munge_data <- output$data
+
+temp <- seq(output$bounds[1], output$bounds[2], length.out = nrow(output$data))
+munge_data <- output$data
+fit <- output$minpack.lm_object
 
 png('vignettes/Figures/plot1.png',
   width     = 3.25,
@@ -14,6 +17,7 @@ png('vignettes/Figures/plot1.png',
 )
 plot(munge_data$temp_K, munge_data$mass_T, xlab = '', ylab = '', cex.axis = 2)
 dev.off()
+
 png('vignettes/Figures/plot2.png',
     width     = 3.25,
     height    = 3.25,
@@ -23,6 +27,7 @@ png('vignettes/Figures/plot2.png',
 )
 plot(munge_data$temp_K, munge_data$deriv, xlab = '', ylab = '', cex.axis = 2)
 dev.off()
+
 png('vignettes/Figures/plot3.png',
     width     = 3.25,
     height    = 3.25,
@@ -30,24 +35,6 @@ png('vignettes/Figures/plot3.png',
     res       = 1200,
     pointsize = 4
 )
-decon_plot <- function (temp, deriv, fit, lower, upper) {
-
-  plot(temp, deriv, xlab = '', ylab = '', cex.axis = 2)
-  curve(fs_mixture_wrap(x, single_param(fit, 'h', '1'), single_param(fit, 'h', '2'), single_param(fit, 'h', '3'),
-                        single_param(fit, 's', '1'), single_param(fit, 's', '2'), single_param(fit, 's', '3'),
-                        single_param(fit, 'p', '1'), single_param(fit, 'p', '2'), single_param(fit, 'p', '3'),
-                        single_param(fit, 'w', '1'), single_param(fit, 'w', '2'), single_param(fit, 'w', '3')),
-        from = lower, to = upper, add = TRUE, col = 'red')
-  curve(fs_function(x, single_param(fit, 'h', '1'), single_param(fit, 's', '1'), single_param(fit, 'p', '1'),
[…]

### 2017-12-18 tests/testthat.R
get up to date

@@ -1,0 +1,4 @@
+library(testthat)
+library(deconvolve)
+
+test_check("deconvolve")

### 2017-12-18 vignettes/Figures/three_graphs.R

@@ -1,21 +1,33 @@
 library(deconvolve)
 
 data(juncus)
-output <- deconvolve(juncus, 'temp_C', 'mass_loss', 18.96, temp_type = 'C')
-munge_data <- output$data
+munge <- process(juncus, 'temp_C', 'mass_loss', 16.85, 'C')
+output <- deconvolve(munge, lower = 420, upper = 860)
+#
+# munge_data <- output$data
+#
+# temp <- seq(output$bounds[1], output$bounds[2], length.out = nrow(output$data))
+# munge_data <- output$data
+# fit <- output$minpack.lm_object
 
-temp <- seq(output$bounds[1], output$bounds[2], length.out = nrow(output$data))
-munge_data <- output$data
-fit <- output$minpack.lm_object
+data <- munge$data[munge$data$temp_K >400 & munge$data$temp_K<900,]
 
-png('vignettes/Figures/plot1.png',
-  width     = 3.25,
-  height    = 3.25,
-  units     = "in",
-  res       = 1200,
-  pointsize = 4
-)
-plot(munge_data$temp_K, munge_data$mass_T, xlab = '', ylab = '', cex.axis = 2)
+
+
+
+
+
+
+
+png('vignettes/Figures/plot1.png', width = 560, height = 480, 'px', bg = 'transparent')
+plot(data$temp_K, data$mass_T, yaxs = 'i', ylim = c(0, max(data$mass_T) + 0.06*max(data$mass_T)),
+     ylab = '', xlab = '', yaxt = 'n', pch = 20, cex = 0.3, cex.axis = 1.8)
+rect(par('usr')[1], par('usr')[3], par('usr')[2], par('usr')[4], col = 'white')
+plot(data$temp_K, data$mass_T, yaxs = 'i', ylim = c(0, max(data$mass_T) + 0.06*max(data$mass_T)),
+     ylab = '', xlab = '', yaxt = 'n', pch = 20, cex = 0.6, cex.axis = 1.8)
+increment <- max(data$mass_T)/2
+axis(side = 2, at = c(0, increment, max(data$mass_T)), cex.axis = 1.8,
+     labels = sprintf("%.2f", c(0, increment, max(data$mass_T))))
 dev.off()
 
 png('vignettes/Figures/plot2.png',

### 2018-07-23 vignettes/figures.R
add installation to readme, upload vignette

@@ -1,0 +1,99 @@
+
+tga_theory <- function (data) {
+
+  # read raw TGA
+  tmp <- deconvolve::process(data, 'temp_C', 'mass_loss', 18.96)
+
+  # plot TG curve
+  layout(matrix(c(1,2,3), nrow = 1, ncol = 3, byrow = TRUE), heights = c(0.8, 0.2))
+  par(oma = c(5, 3, 0, 2), mar = c(3, 6, 3, 3))
+
+  plot(tmp$data$temp_C, tmp$data$mass_T, yaxs = 'i', ylim = c(0, 22), xlim = c(0, 900),
+       xaxs = 'i', ylab = 'Mass (mg)', xlab = '', xaxt = 'n', yaxt = 'n',
+       pch = 20, cex = 0.3, cex.lab = 3)
+  axis(side = 1, at = c(0, 200, 400, 600, 800), cex.axis = 2.8, labels = c(0, 200, 400, 600, 800))
+  axis(side = 2, at = c(0, 10, 20), cex.axis = 2.8,
+       labels = c(0, 10, 20))
+  legend('topleft',
+         legend = '(a)',
+         bty = 'n',
+         cex = 2.5)
+  arrows(x0 = 266, y0 = 19, x1 = 266, y1 = 17, lwd = 2, length = 0.1)
+  arrows(x0 = 317, y0 = 15, x1 = 317, y1 = 13, lwd = 2, length = 0.1)
+  arrows(x0 = 340, y0 = 11.5, x1 = 340, y1 = 9.5, lwd = 2, length = 0.1)
+
+  # plot DTG curve
+  plot(tmp$data$temp_C, tmp$data$deriv, yaxs = 'i', ylim = c(0, 0.009),
+       xaxs = 'i', ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')), xlab = '', xaxt = 'n', yaxt = 'n',
+       pch = 20, cex.lab = 3, cex = 0.9)
+  axis(side = 1, at = c(0, 200, 400, 600, 800), cex.axis = 2.8, labels = c(0, 200, 400, 600, 800))
+  axis(side = 2, at = c(0, 0.004, 0.008), cex.axis = 2.8,
+       labels = c(0, 0.004, 0.008))
+  legend('topleft',
+         legend = '(b)',
+         bty = 'n',
+         cex = 2.5)
+
+  # deconvolve data
[…]

### 2018-07-23 vignettes/shiny-app/mixture_fs/app.R

@@ -1,0 +1,140 @@
+library(shiny)
+library(deconvolve)
+
+ui <- fluidPage(theme = 'bootstrap.css',
+
+                fluidRow(class = "myRow1",
+                         column(8,
+                                plotOutput('fsplot')
+                         ),
+
+                         column(4,
+                                tabsetPanel(
+
+                                  tabPanel(title = 'HC',
+
+                                           tags$style(HTML(".js-irs-0 .irs-single, .js-irs-0 .irs-bar-edge,
+                                                           .js-irs-0 .irs-bar {background: blue}")),
+                                           tags$style(HTML(".js-irs-1 .irs-single, .js-irs-1 .irs-bar-edge,
+                                                           .js-irs-1 .irs-bar {background: blue}")),
+                                           tags$style(HTML(".js-irs-2 .irs-single, .js-irs-2 .irs-bar-edge,
+                                                           .js-irs-2 .irs-bar {background: blue}")),
+                                           tags$style(HTML(".js-irs-3 .irs-single, .js-irs-3 .irs-bar-edge,
+                                                           .js-irs-3 .irs-bar {background: blue}")),
+
+                                           sliderInput(inputId = 'h_HC', ticks = FALSE,
+                                                       label = 'HEIGHT',
+                                                       value = 0.003, step = 0.001, min = 0, max = 0.01),
+                                           sliderInput(inputId = 's_HC', ticks = FALSE,
+                                                       label = 'SKEW',
+                                                       value = -0.15, step = 0.01, min = -1, max = 1),
+                                           sliderInput(inputId = 'p_HC', ticks = FALSE,
+                                                       label = 'POSITION',
+                                                       value = 250, step = 10, min = 120, max = 700),
+                                           sliderInput(inputId = 'w_HC', ticks = FALSE,
+                                                       label = 'WIDTH',
+                                                       value = 50, step = 10, min = 0, max = 250)
+                                           ),
+
+                                  tabPanel(title = 'CL',
+
+                                           tags$style(HTML(".js-irs-4 .irs-single, .js-irs-4 .irs-bar-edge,
+                                                           .js-irs-4 .irs-bar {background: green}")),
+                                           tags$style(HTML(".js-irs-5 .irs-single, .js-irs-5 .irs-bar-edge,
[…]

### 2018-07-23 vignettes/shiny-app/mixture_fs/app.R
change yaml of vignette so it builds build!

@@ -1,140 +1,141 @@
-library(shiny)
-library(deconvolve)
+shinyApp(
 
-ui <- fluidPage(theme = 'bootstrap.css',
+  ui <- fluidPage(theme = 'bootstrap.css',
 
-                fluidRow(class = "myRow1",
-                         column(8,
-                                plotOutput('fsplot')
-                         ),
+                  fluidRow(class = "myRow1",
+                           column(8,
+                                  plotOutput('fsplot')
+                           ),
 
-                         column(4,
-                                tabsetPanel(
+                           column(4,
+                                  tabsetPanel(
 
-                                  tabPanel(title = 'HC',
+                                    tabPanel(title = 'HC',
 
-                                           tags$style(HTML(".js-irs-0 .irs-single, .js-irs-0 .irs-bar-edge,
-                                                           .js-irs-0 .irs-bar {background: blue}")),
-                                           tags$style(HTML(".js-irs-1 .irs-single, .js-irs-1 .irs-bar-edge,
-                                                           .js-irs-1 .irs-bar {background: blue}")),
-                                           tags$style(HTML(".js-irs-2 .irs-single, .js-irs-2 .irs-bar-edge,
-                                                           .js-irs-2 .irs-bar {background: blue}")),
-                                           tags$style(HTML(".js-irs-3 .irs-single, .js-irs-3 .irs-bar-edge,
-                                                           .js-irs-3 .irs-bar {background: blue}")),
+                                             tags$style(HTML(".js-irs-0 .irs-single, .js-irs-0 .irs-bar-edge,
+                                                             .js-irs-0 .irs-bar {background: blue}")),
+                                             tags$style(HTML(".js-irs-1 .irs-single, .js-irs-1 .irs-bar-edge,
+                                                             .js-irs-1 .irs-bar {background: blue}")),
+                                             tags$style(HTML(".js-irs-2 .irs-single, .js-irs-2 .irs-bar-edge,
+                                                             .js-irs-2 .irs-bar {background: blue}")),
+                                             tags$style(HTML(".js-irs-3 .irs-single, .js-irs-3 .irs-bar-edge,
+                                                             .js-irs-3 .irs-bar {background: blue}")),
 
-                                           sliderInput(inputId = 'h_HC', ticks = FALSE,
-                                                       label = 'HEIGHT',
-                                                       value = 0.003, step = 0.001, min = 0, max = 0.01),
-                                           sliderInput(inputId = 's_HC', ticks = FALSE,
[…]

### 2018-07-24 R/plot.process.R
change shape size of points

@@ -18,17 +18,17 @@ plot.process <- function (x, plot_type = NULL, ...) {
   df <- x$data
 
   p_massloss <- function (data) {
-    plot(data$temp_C, data$mass_T, xlab = 'Temperature (K)', ylab = 'Mass Remaining (mg)')
+    plot(data$temp_C, data$mass_T, xlab = 'Temperature (K)', ylab = 'Mass Remaining (mg)', pch = 20, cex = 0.7)
   }
 
   p_dtg <- function (data) {
-    plot(data$temp_C, data$deriv, xlab = 'Temperature (K)', ylab = 'DTG (dm/dT) (K-1)')
+    plot(data$temp_C, data$deriv, xlab = 'Temperature (K)', ylab = 'DTG (dm/dT) (K-1)', pch = 20, cex = 0.7)
   }
 
   p_both <- function (data) {
-    par(mfrow=c(1,2))
-    plot(data$temp_C, data$mass_T, xlab = 'Temperature (K)', ylab = 'Mass Remaining (mg)')
-    plot(data$temp_C, data$deriv, xlab = 'Temperature (K)', ylab = 'DTG (dm/dT) (K-1)')
+    par(mfrow = c(1,2), mar = c(5, 5, 1, 1))
+    plot(data$temp_C, data$mass_T, xlab = 'Temperature (K)', ylab = 'Mass Remaining (mg)', pch = 20, cex = 0.7)
+    plot(data$temp_C, data$deriv, xlab = 'Temperature (K)', ylab = 'DTG (dm/dT) (K-1)', pch = 20, cex = 0.7)
   }
 
   if (!is.null(plot_type) && plot_type == 'mass_loss') {

### 2018-07-24 R/plot.decon.R
revise plot functions so they have correct x and y labels

@@ -22,7 +22,8 @@ plot.decon <- function (x, ...) {
 
   par(xpd = TRUE, mar = par()$mar + c(0, 1, 0, 0))
 
-  plot(data$temp_C, data$deriv, xlab = 'Temperature (C)', ylab = 'DTG (dm/dT) (C-1)',
+  plot(data$temp_C, data$deriv, xlab = 'Temperature (C)',
+       ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
        yaxs = 'i', ylim = c(0, max(data$deriv) + 0.06*max(data$deriv)),
        pch = 20, cex = 0.3, cex.axis = 1.2)
 

### 2018-07-24 R/plot.process.R

@@ -18,23 +18,22 @@ plot.process <- function (x, plot_type = NULL, ...) {
   df <- x$data
 
   p_massloss <- function (data) {
-    plot(data$temp_C, data$mass_T, xlab = 'Temperature (K)', ylab = 'Mass Remaining (mg)', pch = 20, cex = 0.7)
+    plot(data$temp_C, data$mass_T, xlab = 'Temperature (C)',
+         ylab = 'Mass Remaining (mg)', pch = 20, cex = 0.7)
   }
 
   p_dtg <- function (data) {
-    plot(data$temp_C, data$deriv, xlab = 'Temperature (K)', ylab = 'DTG (dm/dT) (K-1)', pch = 20, cex = 0.7)
-  }
-
-  p_both <- function (data) {
-    par(mfrow = c(1,2), mar = c(5, 5, 1, 1))
-    plot(data$temp_C, data$mass_T, xlab = 'Temperature (K)', ylab = 'Mass Remaining (mg)', pch = 20, cex = 0.7)
-    plot(data$temp_C, data$deriv, xlab = 'Temperature (K)', ylab = 'DTG (dm/dT) (K-1)', pch = 20, cex = 0.7)
+    plot(data$temp_C, data$deriv, xlab = 'Temperature (C)',
+         ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
+         pch = 20, cex = 0.7)
   }
 
   if (!is.null(plot_type) && plot_type == 'mass_loss') {
     p_massloss(df)
   } else if (!is.null(plot_type) && plot_type == 'both') {
-    p_both(df)
+    par(mfrow = c(1,2), mar = c(5, 5, 1, 1))
+    p_massloss(df)
+    p_dtg(df)
   } else {
     p_dtg(df)
   }

### 2018-07-27 R/fs_function.R
change fraser-suzuki functions to explicitly write out parmeter names

@@ -1,24 +1,24 @@
-#' Fraser-Suzuki function
+#' Fraser-Suzuki function for a single curve
 #'
 #' This function calculates the Fraser-Suzuki function.
 #'
-#' @param x temperature values
-#' @param h height value
-#' @param s shape value
-#' @param p position value
-#' @param w width value
+#' @param temp temperature values
+#' @param height height value
+#' @param skew shape value
+#' @param position position value
+#' @param width width value
 #' @return Fraser-Suzuki function
 #'
 #' @export
 
-fs_function <- function (x, h, s, p, w) {
+fs_function <- function (temp, height, skew, position, width) {
 
-  interior <- 2 * s * ((x - p) / w)
-  exterior <- -log(2) / s^2
+  interior <- 2 * skew * ((temp - position) / width)
+  exterior <- -log(2) / skew^2
 
   answer <- rep(0, length(interior))
   valid <- interior >= -1
-  answer[valid] <- h * exp(exterior * (log(1 + interior[valid])^2))
+  answer[valid] <- height * exp(exterior * (log(1 + interior[valid])^2))
   answer
 
 }

### 2018-07-27 R/fs_mixture.R

@@ -1,44 +1,47 @@
-#' Mixture model for TGA data
+#' Fraser-Suzuki mixture model
 #'
-#' @param x temperature values
-#' @param h1 height value for curve 1
-#' @param s1 shape value for curve 1
-#' @param p1 position value for curve 1
-#' @param w1 width value for curve 1
-#' @param h2 height value for curve 2
-#' @param s2 shape value for curve 2
-#' @param p2 position value for curve 2
-#' @param w2 width value for curve 2
-#' @param h3 height value for curve 3
-#' @param s3 shape value for curve 3
-#' @param p3 position value for curve 3
-#' @param w3 width value for curve 3
-#' @param h0 height value for curve 0, if present
-#' @param s0 shape value for curve 0, if present
-#' @param p0 position value for curve 0, if present
-#' @param w0 width value for curve 0, if present
+#' @param temp temperature values
+#' @param height_1 height value for hemicellulose
+#' @param skew_1 shape value for hemicellulose
+#' @param position_1 position value for hemicellulose
+#' @param width_1 width value for hemicellulose
+#' @param height_2 height value for cellulose
+#' @param skew_2 shape value for cellulose
+#' @param position_2 position value for cellulose
+#' @param width_2 width value for cellulose
+#' @param height_3 height value for lignin
+#' @param skew_3 shape value for lignin
+#' @param position_3 position value for lignin
+#' @param width_3 width value for lignin
+#' @param height_0 height value for second hemicellulose curve, if present
+#' @param skew_0 shape value for second hemicellulose curve, if present
+#' @param position_0 position value for second hemicellulose curve, if present
+#' @param width_0 width value for second hemicellulose curve, if present
 #' @return Fraser-Suzuki model output
 #'
 #' @export
 
-fs_mixture <- function (x,
-                        h1, s1, p1, w1,
-                        h2, s2, p2, w2,
-                        h3, s3, p3, w3,
-                        h0 = NULL, s0 = NULL, p0 = NULL, w0 = NULL) {
+fs_mixture <- function (temp,
+                        height_1, skew_1, position_1, width_1,
+                        height_2, skew_2, position_2, width_2,
+                        height_3, skew_3, position_3, width_3,
[…]

### 2018-07-27 R/fs_model.R

@@ -16,22 +16,29 @@ fs_model <- function (dataframe, params, lb, ub) {
 
   if (length(params) == 12) {
 
-    frm <- deriv ~ fs_mixture(temp_C, h1, s1, p1, w1, h2, s2, p2, w2, h3, s3, p3, w3)
+    frm <- deriv ~ fs_mixture(temp_C,
+                              height_1, skew_1, position_1, width_1,
+                              height_2, skew_2, position_2, width_2,
+                              height_3, skew_3, position_3, width_3)
 
-    start_list <- list(h1 = params[1], s1 = params[2], p1 = params[3], w1 = params[4],
-                       h2 = params[5], s2 = params[6], p2 = params[7], w2 = params[8],
-                       h3 = params[9], s3 = params[10], p3 = params[11], w3 = params[12])
+    start_list <- list(height_1 = params[1], skew_1 = params[2], position_1 = params[3], width_1 = params[4],
+                       height_2 = params[5], skew_2 = params[6], position_2 = params[7], width_2 = params[8],
+                       height_3 = params[9], skew_3 = params[10], position_3 = params[11], width_3 = params[12])
 
   }
 
   if (length(params) == 16) {
 
-    frm <- deriv ~ fs_mixture(temp_C, h1, s1, p1, w1, h2, s2, p2, w2, h3, s3, p3, w3, h0, s0, p0, w0)
+    frm <- deriv ~ fs_mixture(temp_C,
+                              height_1, skew_1, position_1, width_1,
+                              height_2, skew_2, position_2, width_2,
+                              height_3, skew_3, position_3, width_3,
+                              height_0, skew_0, position_0, width_0)
 
-    start_list <- list(h0 = params[1], s0 = params[2], p0 = params[3], w0 = params[4],
-                       h1 = params[5], s1 = params[6], p1 = params[7], w1 = params[8],
-                       h2 = params[9], s2 = params[10], p2 = params[11], w2 = params[12],
-                       h3 = params[13], s3 = params[14], p3 = params[15], w3 = params[16])
+    start_list <- list(height_0 = params[1], skew_0 = params[2], position_0 = params[3], width_0 = params[4],
+                       height_1 = params[5], skew_1 = params[6], position_1 = params[7], width_1 = params[8],
+                       height_2 = params[9], skew_2 = params[10], position_2 = params[11], width_2 = params[12],
+                       height_3 = params[13], skew_3 = params[14], position_3 = params[15], width_3 = params[16])
 
   }
 

### 2018-07-27 R/inflection.R
specify function required from zoo

@@ -3,8 +3,8 @@
 #' @param x numeric
 #' @keywords internal
 
-three_peaks <- function(x) {
-  return(length(x) == 0)
+three_peaks <- function (x) {
+  return (length(x) == 0)
 }
 
 #' Function to determine x-value of peak < 500 K
@@ -13,13 +13,13 @@ three_peaks <- function(x) {
 #' @param y y-values
 #' @keywords internal
 #' @return returns a list of values. $x returns the inflections points within x.
-#' @import zoo
+#' @importFrom zoo rollapply
 ## script cred https://stats.stackexchange.com/questions/36309/how-do-i-find-peaks-in-a-dataset
 
 inflection <- function(x, y, w = 1, ...) {
   n <- length(y)
   y.smooth <- loess(y ~ x, ...)$fitted
-  y.max <- rollapply(zoo(y.smooth), 2*w+1, max, align="center")
+  y.max <- zoo::rollapply(zoo(y.smooth), 2*w+1, max, align = "center")
   delta <- y.max - y.smooth[-c(1:w, n+1-1:w)]
   i.max <- which(delta <= 0) + w
   list(x = x[i.max], i = i.max, y.hat = y.smooth)

### 2018-07-27 README.Rmd
move readme from .md to .Rmd so can visualise chunk outputs. add repo status badge

---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Build Status](https://travis-ci.com/smwindecker/deconvolve.svg?branch=master)](https://travis-ci.org/smwindecker/deconvolve)
[![codecov](https://codecov.io/gh/smwindecker/deconvolve/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/deconvolve)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

# deconvolve
notes to self: avoid 'easy' 'simple' etc
don't go into so much jargon so early!
convince reader of the problem

This package provides an easy and straightforward way to quantify proportions of lignocellulosic biomass components (typically considered hemicellulose, cellulose, and lignin) from the mass loss data generated during thermogravimetric analysis (TGA).

Proportions of the main carbon types in litter can be used as functional traits to understand ecosystem processes such as litter decomposition, or to aid in calculation of kinetic decay constants. Thermogravimetric analysis is the process of pyrolysing dry, ground plant litter, and results in mass loss data across a temperature range. Since different carbon types break down during different temperature phases, we can separate the multi-peaked rate of mass loss curve into independent decay phases and estimate proportions of each carbon type by integrating under their respective individual decay curve. This package conducts this analysis in an open-source and reproducible fashion.

## Installation

You can install deconvolve from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("smwindecker/deconvolve", build_vignettes = TRUE)
```
## Basic use

Data from thermogravimetric analysis is usually exported as mass loss with temperature. An example dataset for the species *Juncus amabilis* is included in the package:
```{r}
data(juncus)
```

We can use the function `process()` to take the derivative of this mass loss data, resulting in rate of mass loss over temperature data. To do so you simply need to specify the dataset, identify which columns contain temperature and mass loss data, and provide a value for the starting mass of the sample. The function defaults to temperature data in Celsius, but you can also modify to indicate the data is provided in Kelvin, by adding `temp_type = 'K'`.
```{r}
tmp <- process(juncus, temp = 'temp_C', mass = 'mass_loss', init_mass = 16.85)
```

The default plot function for the derivative data shows you both the original mass loss curve and the derivative rate of mass loss curve.

Processed data then simply needs to be deconvolved into its constituent parts. The deconvolve function takes care of this step, by cropping the derivative data to exclude dehydration and then running the Fraser-Suzuki mixture model and estimating individual curve parameters and weights.
```{r}
output <- deconvolve(tmp)
```

Although most biomass samples have only three main components (corresponding to hemicellulose, cellulose, and lignin), some have a second hemicellulose curve in the low temperature range. The function will decide whether three or four curves are best, but you can override it by modifying the `n_curves` argument. The function also has built in starting values for the nonlinear optimisation. If you'd like to modify those or the upper and lower bounds for the estimates, you can also do so with the `start_vec`, `lower_vec`, and `upper_vec` arguments to `deconvolve()`.

The `deconvolve()` function results in a variety of outputs. You can use a variety of accessor functions to look at these. `component_weights()` will display the weights of each carbon component, `rate_data()` will show you the modified dataset used for fitting, `model_fit()` will show you the model fit, and `temp_bounds()` will print the temperature values at which the data were cropped for analysis. You can also plot the resulting output using the default plotting function.

You can see the full worked example in the vignette, which you can access on the [website](http://smwindecker.github.io/deconvolve/) or in R:
```{r}
vignette('deconvolve')
```

This is still a work in progress! If you see any mistakes, or find that the code is not functioning well on your data, let me know by logging a bug on the [issues page](http://www.github.com/smwindecker/deconvolve/issues).

## Acknowledgements
Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project. Nick Tierney for valuable feedback during development.

### 2018-07-27 R/objective.R
explicitly call x temperature

@@ -1,25 +1,25 @@
 # Objective function
 #
-#' This function evaluates a model using rmse.
+#' This function evaluates root mean squared error of a model
 #'
 #' @param theta values for each of the parameters
 #' @param model mathematical function to be used to model data
-#' @param x temperature values
+#' @param temp temperature values
 #' @param obs DTG mass values
 #' @return root mean square error of model output
 #' @keywords internal
 
-objective <- function (theta, model, x, obs) {
+objective <- function (theta, model, temp, obs) {
 
   if (length(theta) == 12) {
-    pred <- model(x,
+    pred <- model(temp,
                   theta[1], theta[2], theta[3], theta[4],
                   theta[5], theta[6], theta[7], theta[8],
                   theta[9], theta[10], theta[11], theta[12])
   }
 
   if (length(theta) == 16) {
-    pred <- model(x,
+    pred <- model(temp,
                   theta[5], theta[6], theta[7], theta[8],
                   theta[9], theta[10], theta[11], theta[12],
                   theta[13], theta[14], theta[15], theta[16],

### 2018-07-27 R/param_select.R

@@ -5,7 +5,7 @@
 #' @param theta vector of starting values for each of 12 parameters
 #' @param lb vector of lower bounds on each of 12 parameters
 #' @param model mathematical function to be applied
-#' @param x temperature values
+#' @param temp temperature values
 #' @param obs DTG mass values
 #' @param restarts number of times for optimiser to restart
 #' @param ranseed random seed for optimiser
@@ -14,7 +14,7 @@
 #' @importFrom nloptr nloptr
 
 # create params_opt with this function
-param_select <- function (theta, lb, ub, model, x, obs, ranseed, restarts = 300) {
+param_select <- function (theta, lb, ub, model, temp, obs, ranseed, restarts = 300) {
 
   opts <- list("algorithm" = "NLOPT_LN_BOBYQA",
                "xtol_rel" = 1.0e-12,
@@ -27,7 +27,7 @@ param_select <- function (theta, lb, ub, model, x, obs, ranseed, restarts = 300)
                                      lb = lb,
                                      ub = ub,
                                      model = model,
-                                     x = x,
+                                     temp = temp,
                                      obs = obs,
                                      opts = opts),
                       simplify = FALSE)

### 2018-07-27 R/process.R
change argument names to be simpler

@@ -1,11 +1,11 @@
-#' Processes Thermogravimetric Data
+#' Calculates the derivative rate of mass loss of thermogravimetric data
 #'
 #' This function processes thermogravimetric data by calculating
 #' the derivative of mass loss
 #'
 #' @param data dataframe
-#' @param temp_col column name containing temperature values
-#' @param massloss_col column name containing mass loss values in grams
+#' @param temp column name containing temperature values
+#' @param mass column name containing mass loss values in grams
 #' @param init_mass numeric value of initial sample mass in grams
 #' @param temp_type specify units of temperature, default = Celsius. Specify 'K' if in Kelvin
 #' @return decon list containing amended dataframe, bounds, model output, mass fractions
@@ -18,13 +18,21 @@
 #'
 #' @export
 
-process <- function (data, temp_col, massloss_col, init_mass,
-                        temp_type = 'C') {
+process <- function (data, temp, mass, init_mass,
+                     temp_type = 'C') {
 
-  if (temp_type == 'K') {
-    data$temp_C <- data[, temp_col] - 273
-  } else {
-    data$temp_C <- data[, temp_col]
+  temp_measures <- c('C', 'Celsius', 'K', 'Kelvin')
+
+  if (!is.TRUE(is.element(temp_type, temp_measures))) {
+    stop('Specify temperature either in Celsius or Kelvin')
+  }
+
+  if (temp_type == 'K' | temp_type == 'Kelvin') {
+    data$temp_C <- data[, temp] - 273
+  }
+
+  if (temp_type == 'C' | temp_type == 'Celsius') {
+    data$temp_C <- data[, temp]
   }
 
   if (data[1, 'temp_C']%%1!=0) {
@@ -35,7 +43,7 @@ process <- function (data, temp_col, massloss_col, init_mass,
   }
 
   # adjust mass loss given initial mass, use this for derivative
-  data_1$adj_massloss <- data_1[, massloss_col] / init_mass
+  data_1$adj_massloss <- data_1[, mass] / init_mass
 
   d <- -as.data.frame(diff(data_1$adj_massloss)/diff(data_1$temp_C))
   x <- rep(NA, ncol(d))
@@ -43,7 +51,7 @@ process <- function (data, temp_col, massloss_col, init_mass,
   colnames(deriv) <- 'deriv'
   data_2 <- cbind(data_1, deriv)
   data_2 <- data_2[-1,]
[…]

### 2018-07-27 R/get_weights.R
consolidate common scripts containing internal functions

@@ -1,34 +1,0 @@
-#' Calculate weight quantiles
-#'
-#' @param param_vec parameter estimates from minpack model
-#' @param output deconvolve output of model
-#' @importFrom stats coef deviance
-#' @return weights for each component
-#'
-
-get_weights <- function (param_vec, output) {
-
-  n_peaks <- output$n_peaks
-  lower_temp <- output$bounds[1]
-  upper_temp <- output$bounds[2]
-
-  if (n_peaks == 3) {
-    wt_percent <- c('HC' = NA, 'CL' = NA, 'LG' = NA)
-    curve_vec <- 1:3
-  }
-
-  if (n_peaks == 4) {
-    wt_percent <- c('HC_1' = NA, 'HC_2' = NA, 'CL' = NA, 'LG' = NA)
-    curve_vec <- 0:3
-  }
-
-  wt_percent <- sapply(curve_vec, wt_component,
-                       param_vec = param_vec,
-                       lower_temp = lower_temp,
-                       upper_temp = upper_temp)
-
-  if (length(wt_percent) == 3) names(wt_percent) <- c('HC', 'CL', 'LG')
-  if (length(wt_percent) == 4) names(wt_percent) <- c('HC_1', 'HC_2', 'CL', 'LG')
-
-  wt_percent
-}

### 2018-07-27 R/inflection.R

@@ -13,13 +13,13 @@ three_peaks <- function (x) {
 #' @param y y-values
 #' @keywords internal
 #' @return returns a list of values. $x returns the inflections points within x.
-#' @importFrom zoo rollapply
+#' @importFrom zoo rollapply zoo
 ## script cred https://stats.stackexchange.com/questions/36309/how-do-i-find-peaks-in-a-dataset
 
 inflection <- function(x, y, w = 1, ...) {
   n <- length(y)
   y.smooth <- loess(y ~ x, ...)$fitted
-  y.max <- zoo::rollapply(zoo(y.smooth), 2*w+1, max, align = "center")
+  y.max <- zoo::rollapply(zoo::zoo(y.smooth), 2*w+1, max, align = "center")
   delta <- y.max - y.smooth[-c(1:w, n+1-1:w)]
   i.max <- which(delta <= 0) + w
   list(x = x[i.max], i = i.max, y.hat = y.smooth)

### 2018-07-27 R/objective.R

@@ -1,35 +1,0 @@
-# Objective function
-#
-#' This function evaluates root mean squared error of a model
-#'
-#' @param theta values for each of the parameters
-#' @param model mathematical function to be used to model data
-#' @param temp temperature values
-#' @param obs DTG mass values
-#' @return root mean square error of model output
-#' @keywords internal
-
-objective <- function (theta, model, temp, obs) {
-
-  if (length(theta) == 12) {
-    pred <- model(temp,
-                  theta[1], theta[2], theta[3], theta[4],
-                  theta[5], theta[6], theta[7], theta[8],
-                  theta[9], theta[10], theta[11], theta[12])
-  }
-
-  if (length(theta) == 16) {
-    pred <- model(temp,
-                  theta[5], theta[6], theta[7], theta[8],
-                  theta[9], theta[10], theta[11], theta[12],
-                  theta[13], theta[14], theta[15], theta[16],
-                  theta[1], theta[2], theta[3], theta[4])
-  }
-
-  # see how good it is
-  target <- rmse(pred, obs)
-
-  target
-
-}
-

### 2018-07-27 R/param_select.R

@@ -42,3 +42,51 @@ param_select <- function (theta, lb, ub, model, temp, obs, ranseed, restarts = 3
   o$solution
 
 }
+
+# Objective function
+#
+#' This function evaluates root mean squared error of a model
+#'
+#' @param theta values for each of the parameters
+#' @param model mathematical function to be used to model data
+#' @param temp temperature values
+#' @param obs DTG mass values
+#' @return root mean square error of model output
+#' @keywords internal
+
+objective <- function (theta, model, temp, obs) {
+
+  if (length(theta) == 12) {
+    pred <- model(temp,
+                  theta[1], theta[2], theta[3], theta[4],
+                  theta[5], theta[6], theta[7], theta[8],
+                  theta[9], theta[10], theta[11], theta[12])
+  }
+
+  if (length(theta) == 16) {
+    pred <- model(temp,
+                  theta[5], theta[6], theta[7], theta[8],
+                  theta[9], theta[10], theta[11], theta[12],
+                  theta[13], theta[14], theta[15], theta[16],
+                  theta[1], theta[2], theta[3], theta[4])
+  }
+
+  # see how good it is
+  target <- rmse(pred, obs)
+
+  target
+
+}
+
+#' Calculate room mean squared error
+#'
+#' This function calculated root mean squarer error of prediction.
+#'
+#' @param pred predicted parameter value
+#' @param obs DTG mass values
+#' @return root mean squared error
+#' @keywords internal
+
+rmse <- function (pred, obs) {
+  sqrt(sum((obs - pred) ^ 2))
+}

### 2018-07-27 R/rmse.R

@@ -1,12 +1,0 @@
-#' Calculate room mean squared error
-#'
-#' This function calculated root mean squarer error of prediction.
-#'
-#' @param pred predicted parameter value
-#' @param obs DTG mass values
-#' @return root mean squared error
-#' @keywords internal
-
-rmse <- function (pred, obs) {
-  sqrt(sum((obs - pred) ^ 2))
-}

### 2018-07-27 R/weight_quantiles.R

@@ -51,3 +51,69 @@ weight_quantiles <- function (output, seed) {
 
   list(weights = all_weights)
 }
+
+#' Calculate weight quantiles
+#'
+#' @param param_vec parameter estimates from minpack model
+#' @param output deconvolve output of model
+#' @importFrom stats coef deviance
+#' @return weights for each component
+#'
+
+get_weights <- function (param_vec, output) {
+
+  n_peaks <- output$n_peaks
+  lower_temp <- output$bounds[1]
+  upper_temp <- output$bounds[2]
+
+  if (n_peaks == 3) {
+    wt_percent <- c('HC' = NA, 'CL' = NA, 'LG' = NA)
+    curve_vec <- 1:3
+  }
+
+  if (n_peaks == 4) {
+    wt_percent <- c('HC_1' = NA, 'HC_2' = NA, 'CL' = NA, 'LG' = NA)
+    curve_vec <- 0:3
+  }
+
+  wt_percent <- sapply(curve_vec, wt_component,
+                       param_vec = param_vec,
+                       lower_temp = lower_temp,
+                       upper_temp = upper_temp)
+
+  if (length(wt_percent) == 3) names(wt_percent) <- c('HC', 'CL', 'LG')
+  if (length(wt_percent) == 4) names(wt_percent) <- c('HC_1', 'HC_2', 'CL', 'LG')
+
+  wt_percent
+}
+
+#' Calculate weight single component
+#'
+#' @param j component
+#' @param param_vec vector of parameters
+#' @param lower_temp lower temperature bound
+#' @param upper_temp upper temperature bound
+#' @importFrom glue glue
+#' @return weight of component
+#'
+
+wt_component <- function (j, param_vec, lower_temp, upper_temp) {
+
+  # extract relevant parameter vector
+  p <- c('height', 'skew', 'position', 'width')
+  names <- glue::glue('{p}_{j}')
+
+  idx <- match(names, names(param_vec))
+  param_sub <- param_vec[idx]
+
+  f_j <- function (x) {
+    fs_function(x, param_sub[1], param_sub[2], param_sub[3], param_sub[4])
+  }
+
+  # weight percent of each component, where the integral is the fraction
+  # of initial mass of that compoenent.
+  wt <- integrate(Vectorize(f_j), lower = lower_temp,
+                  upper = upper_temp)$value * 100
+
+  wt
+}

### 2018-07-27 R/wt_component.R

@@ -1,30 +1,0 @@
-#' Calculate weight single component
-#'
-#' @param j component
-#' @param param_vec vector of parameters
-#' @param lower_temp lower temperature bound
-#' @param upper_temp upper temperature bound
-#' @importFrom glue glue
-#' @return weight of component
-#'
-
-wt_component <- function (j, param_vec, lower_temp, upper_temp) {
-
-  # extract relevant parameter vector
-  p <- c('height', 'skew', 'position', 'width')
-  names <- glue::glue('{p}_{j}')
-
-  idx <- match(names, names(param_vec))
-  param_sub <- param_vec[idx]
-
-  f_j <- function (x) {
-    fs_function(x, param_sub[1], param_sub[2], param_sub[3], param_sub[4])
-  }
-
-  # weight percent of each component, where the integral is the fraction
-  # of initial mass of that compoenent.
-  wt <- integrate(Vectorize(f_j), lower = lower_temp,
-                  upper = upper_temp)$value * 100
-
-  wt
-}

### 2018-07-27 README.Rmd
more accessible introduction

@@
 
-# deconvolve
-notes to self: avoid 'easy' 'simple' etc
-don't go into so much jargon so early!
-convince reader of the problem
+## Why deconvolution?
 
-This package provides an easy and straightforward way to quantify proportions of lignocellulosic biomass components (typically considered hemicellulose, cellulose, and lignin) from the mass loss data generated during thermogravimetric analysis (TGA).
+Ecologists are often interested in determining the composition of plant cell wall biomass, primarily hemicellulose, cellulose, and lignin carbon types.
+Proportions of these carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.
+Traditional methods for calculation of these components involve wet chemistry methods that can be monetarily and environmentally costly.
+Thermogravimetric analysis (TGA) is an alternative method, already used in the biofuel field, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in a $N_2$ environment, termed pyrolysis).
 
-Proportions of the main carbon types in litter can be used as functional traits to understand ecosystem processes such as litter decomposition, or to aid in calculation of kinetic decay constants.
-Thermogravimetric analysis is the process of pyrolysing dry, ground plant litter, and results in mass loss data across a temperature range.
-Since different carbon types break down during different temperature phases, we can separate the multi-peaked rate of mass loss curve into independent decay phases and estimate proportions of each carbon type by integrating under their respective individual decay curve.
-This package conducts this analysis in an open-source and reproducible fashion.
+To estimate carbon components from this mass loss data we have to take the derivative, to find the rate of mass loss across temperature, and then use a mixture model to separate the multi-peaked derivative curve into constituent parts.
+This process is called deconvolution, and is typically conducted in proprietary peak-fitting softwares, which, while effective, are not open source.
+This package seeks to provide a platform for reproducible deconvolution using R.
+This methodology has been tested on a range of plant litter composed primarily of soluble carbohydrates, hemicellulose, cellulose, and lignin.
+For more details (link paper here).
+
+<hr>
 
@@
 
-You can install deconvolve from [GitHub](https://github.com/) with:
+You can install `deconvolve` from [GitHub](https://github.com/) with:
 
@@
 ```{r}
-data(juncus)
+library(deconvolve)
+head(juncus)
 ```
@@
 tmp <- process(juncus, temp = 'temp_C', mass = 'mass_loss', init_mass = 16.85)
+tmp
 ```
@@
 This is still a work in progress!
-If you see any mistakes, or find that the code is not functioning well on your data, let me know by logging a bug on the [issues page](http://www.github.com/smwindecker/deconvolve/issues).
+If you see any mistakes, or find that the code is not functioning well on your data, let us know by logging a bug on the [issues page](http://www.github.com/smwindecker/deconvolve/issues).
 
 ## Acknowledgements
-Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project. Nick Tierney for valuable feedback during development.
+Thank you to Nick Tierney for valuable feedback during development. Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project.

### 2018-07-27 R/process.R
specify plyr function used

@@ -10,7 +10,7 @@
 #' @param temp_type specify units of temperature, default = Celsius. Specify 'K' if in Kelvin
 #' @return decon list containing amended dataframe, bounds, model output, mass fractions
 #' @keywords thermogravimetry fraser-suzuki deconvolution
-#' @import plyr
+#' @importFrom plyr round_any
 #' @importFrom stats integrate setNames
 #' @examples
 #' data(juncus)
@@ -23,7 +23,7 @@ process <- function (data, temp, mass, init_mass,
 
   temp_measures <- c('C', 'Celsius', 'K', 'Kelvin')
 
-  if (!is.TRUE(is.element(temp_type, temp_measures))) {
+  if (!isTRUE(is.element(temp_type, temp_measures))) {
     stop('Specify temperature either in Celsius or Kelvin')
   }
 
@@ -36,7 +36,7 @@ process <- function (data, temp, mass, init_mass,
   }
 
   if (data[1, 'temp_C']%%1!=0) {
-    data$roundC <- round_any(data$temp_C, 1)
+    data$roundC <- plyr::round_any(data$temp_C, 1)
     data_1 <- data[!duplicated(data$roundC),]
   } else {
     data_1 <- data[!duplicated(data$temp_C),]

### 2018-07-27 R/rate_data.R
aesthetic

@@ -11,7 +11,5 @@
 #' @export
 
 rate_data <- function (object) {
-
   object$data
-
 }

### 2018-07-27 R/deconvolve.R
adjust seed call

@@ -5,7 +5,7 @@
 #' @param process_object process object obtained from process function
 #' @param lower_temp lower temperature bound to crop dataset, default to 120
 #' @param upper_temp upper temperature bound to crop dataset, default to 700
-#' @param ranseed random seed for nloptr optimiser
+#' @param seed random seed for nloptr optimiser
 #' @param n_curves number of curves optional specification
 #' @param start_vec vector of starting values for nls function. Only specify this vector if
 #' you have selected the number of curves in the n_curves parameter.
@@ -23,8 +23,10 @@
 #'
 #' @export
 
-deconvolve <- function (process_object, lower_temp = 120, upper_temp = 700, ranseed = 1,
+deconvolve <- function (process_object, lower_temp = 120, upper_temp = 700, seed = 1,
                         n_curves = NULL, start_vec = NULL, lower_vec = NULL, upper_vec = NULL) {
+
+  set.seed(seed)
 
   # identify dataframe
   mod_df <- process_object$data
@@ -48,10 +50,10 @@ deconvolve <- function (process_object, lower_temp = 120, upper_temp = 700, rans
   if (is.null(n_curves) & fourth_peak == TRUE) {
     n_peaks <- 4
   }
-  if (n_curves == 3) {
+  if (isTRUE(n_curves == 3)) {
     n_peaks <- 3
   }
-  if (n_curves == 4) {
+  if (isTRUE(n_curves == 4)) {
     n_peaks <- 4
   }
 
@@ -101,7 +103,7 @@ deconvolve <- function (process_object, lower_temp = 120, upper_temp = 700, rans
   }
 
   # parameter optimisation
-  params_opt <- param_select(theta, lb, ub, fs_mixture, temp, obs, ranseed = ranseed, restarts = 300)
+  params_opt <- param_select(theta, lb, ub, fs_mixture, temp, obs, seed = seed, restarts = 300)
 
   # model fit
   fit <- fs_model(mod_df, params_opt, lb, ub)
@@ -112,7 +114,7 @@ deconvolve <- function (process_object, lower_temp = 120, upper_temp = 700, rans
                  minpack.lm = fit,
                  n_peaks = n_peaks)
 
-  weights <- weight_quantiles(output, ranseed)
+  weights <- weight_quantiles(output, seed)
 
   decon_output <- c(output, weights)
 

### 2018-07-27 R/param_select.R

@@ -14,11 +14,11 @@
 #' @importFrom nloptr nloptr
 
 # create params_opt with this function
-param_select <- function (theta, lb, ub, model, temp, obs, ranseed, restarts = 300) {
+param_select <- function (theta, lb, ub, model, temp, obs, seed, restarts = 300) {
 
   opts <- list("algorithm" = "NLOPT_LN_BOBYQA",
                "xtol_rel" = 1.0e-12,
-               "ranseed" = ranseed)
+               "ranseed" = seed)
 
   # fit the model `restarts` times with different starting locations
   o_list <- replicate(restarts,

### 2018-07-27 tests/testthat/test-accessor_functions.R

@@ -1,36 +1,14 @@
 context("Test for accessor functions")
 
-test_that("Bounds returns bounds", {
+test_that("accessor functions return correct values", {
 
   data(juncus)
   tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96)
   output <- deconvolve(tmp, lower_temp = 130, upper_temp = 660)
-  expect_equal(Bounds(output), output$bounds)
 
-})
-
-test_that("ModData returns data", {
-
-  data(juncus)
-  tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96)
-  expect_identical(ModData(tmp), tmp$data)
-
-})
-
-test_that("Model returns model output", {
-
-  data(juncus)
-  tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96)
-  expect_identical(Model(tmp), tmp$minpack.lm)
-
-})
-
-test_that("Weights returns weight estimates", {
-
-  data(juncus)
-  tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96)
-  output <- deconvolve(tmp)
-
-  expect_identical(Weights(output), output$weights)
+  expect_equal(temp_bounds(output), output$bounds)
+  expect_identical(rate_data(tmp), tmp$data)
+  expect_identical(model_fit(tmp), tmp$minpack.lm)
+  expect_identical(component_weights(output), output$weights)
 
 })

### 2018-07-27 R/juncus-data.R
correct species name for juncus

@@ -1,6 +1,6 @@
-#' Thermogravimetric data for Juncus usitatus
+#' Thermogravimetric data for Juncus amabilis
 #'
-#' Raw thermogravimetric data from the wetland rush, J. usitatus.
+#' Raw thermogravimetric data from the wetland rush, J. amabilis
 #'
 #' @docType data
 #'

### 2018-07-27 README.Rmd
minor tidying up - add isTRUE statments to if

@@
 ```{r}
-tmp <- process(juncus, temp = 'temp_C', mass = 'mass_loss', init_mass = 16.85)
+tmp <- process(juncus, temp = 'temp_C', mass = 'mass_loss', init_mass = 18.96)
 tmp
@@
 
-You can see the full worked example in the vignette, which you can access on the [website](http://smwindecker.github.io/deconvolve/) or in R:
+You can see the full worked example in the vignette, which you can access on the or in R:
 ```{r}

### 2018-07-27 R/plot.process.R

@@ -27,10 +27,10 @@ plot.process <- function (x, plot_type = NULL, ...) {
          pch = 20, cex = 0.7)
   }
 
-  if (plot_type == 'mass') {
+  if (!is.null(plot_type) & isTRUE(plot_type == 'mass')) {
     p_massloss(df)
   }
-  if (plot_type == 'rate') {
+  if (!is.null(plot_type) & isTRUE(plot_type == 'rate')) {
     p_dtg(df)
   }
   if (is.null(plot_type)) {

### 2018-08-01 R/plot.process.R
rename title

@@ -1,4 +1,4 @@
-#' Sets default plotting for process objects
+#' Default S3 plot method for process objects (derived from `process()`)
 #'
 #' This function sets up the default plotting method
 #' for outputs from process function
@@ -18,7 +18,7 @@ plot.process <- function (x, plot_type = NULL, ...) {
 
   p_massloss <- function (data) {
     plot(data$temp_C, data$mass_T, xlab = 'Temperature (C)',
-         ylab = 'Mass Remaining (mg)', pch = 20, cex = 0.7)
+         ylab = 'Mass remaining (mg)', pch = 20, cex = 0.7)
   }
 
   p_dtg <- function (data) {

### 2018-08-01 logo/logo.R
add logo docs

@@ -1,0 +1,32 @@
+png('hex_bg.png', width = 1500, height = 1500, bg = 'transparent')
+hexd <- data.frame(x = 1 + c(rep(-sqrt(3)/2, 2), 0, rep(sqrt(3)/2, 2), 0),
+                   y = 1 + c(0.5, -0.5, -1, -0.5, 0.5, 1))
+hexd <- rbind(hexd, hexd[1, ])
+x_lim <- range(hexd$x)
+y_lim <- range(hexd$y)
+plot.new()
+plot.window(x_lim, y_lim)
+polygon(hexd, col = "#ededed", border = NA)
+segments(x0 = hexd$x[1] + .03,
+         y0 = hexd$y[1] - .03,
+         x1 = hexd$x[2] + .03,
+         y1 = hexd$y[2] + .03, lwd = 16, col = '#000000')
+segments(x0 = hexd$x[3],
+         y0 = hexd$y[3] + .033,
+         x1 = hexd$x[4] - .03,
+         y1 = hexd$y[4] + .02, lwd = 13, col = '#000000')
+segments(x0 = hexd$x[5] - .03,
+         y0 = hexd$y[5] - .02,
+         x1 = hexd$x[6],
+         y1 = hexd$y[6] - .033, lwd = 13, col = '#000000')
+img <- png::readPNG("mixchar_logo.png")
+rasterImage(img, .4, .4, 1.6, 1.6)
+dev.off()
+
+hexSticker::sticker('hex_bg.png', s_x = .985, s_y = .99, s_width = 1.1,
+        package = '', h_color = '#000000', h_fill = '#ededed',
+        filename = "hexsticker.png")
+
+
+
+

### 2018-08-01 manuscript/manuscript.Rnw
change default for manuscript to knitr not Sweave and add manuscript

%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham Universtiy, UK.

\documentclass{jors}

%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

%% packages
% bibliography
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\renewcommand{\refname}{}
\renewcommand{\bibname}{}

\usepackage{hyperref} % for \url

\usepackage{graphicx}
\usepackage{booktabs}

\usepackage{tabularx}
\usepackage{float}

\usepackage{multirow}

\usepackage{caption}
\captionsetup{justification=raggedright, singlelinecheck=false}
\usepackage[font=small,labelfont=bf,labelsep=space]{caption}

\usepackage{subfig}
\captionsetup{justification=raggedright, singlelinecheck=false}

\usepackage{pgfplots}
\pgfplotsset{width=16cm}

\usepackage{amsmath}

\usepackage{listings}

\begin{document}

<<echo = FALSE>>=
opts_chunk$set(size = 'footnotesize',
               fig.pos = 'H',
               root.dir = 'manuscript/')
@

{\bf Software paper for submission to the Journal of Open Research Software} \\

Please submit the completed paper to: editor.jors@ubiquitypress.com

\rule{\textwidth}{1pt}

\section*{(1) Overview}

\vspace{0.5cm}

\section*{Title}
deconvolve: An R package for the deconvolution of thermal decay curves

\section*{Paper Authors}
1. Windecker, Saras Mei \\
2. Vesk, Peter Anton \\
3. Golding, Nick.

\section*{Paper Author Roles and Affiliations}
1. PhD Candidate, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
2. Associate Professor, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
3. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia

\section*{Abstract}
This package provides way to quantify proportions of lignocellulosic biomass components (typically considered hemicellulose, cellulose, and lignin) from the mass loss data generated during thermogravimetric analysis (TGA).

Proportions of the main carbon types in litter can be used as functional traits to understand ecosystem processes such as litter decomposition, or to aid in calculation of kinetic decay constants. Thermogravimetric analysis is the process of pyrolysing dry, ground plant litter, and results in mass loss data across a temperature range. Since different carbon types break down during different temperature phases, we can separate the multi-peaked rate of mass loss curve into independent decay phases and estimate proportions of each carbon type by integrating under their respective individual decay curve. This package conducts this analysis in an open-source and reproducible fashion.

\section*{Keywords}
thermogravimetric analysis; deconvolution; decay; Fraser-Suzuki; R package; plant traits

\section*{Introduction}
Plant cell wall biomass is composed of a range of different types of carbon. Ecologists can use these proportions of biomass carbon as functional traits, enabling us to make generalisations about species' effects on ecosystem processes such as litter decomposition, which links plant biomass to the global carbon cycle \citep{cornwell2008}. Biofuels researchers use proportions of biomass carbon types to estimate kinetic decay parameters of species' tissue. Traditional methods for calculation of lignocellulosic biomass involve wet chemistry assays for carbon component analysis are time-consuming and adversely impact the environment through use of sulfuric acid and acetic anhydride, among other chemicals. Thermogravimetric analysis (TGA) is an alternative method, already in use among biofuels researchers, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in a $N_2$ environment, termed pyrolysis). \\
\\
Mass loss during pyrolysis can be regarded as the sum of the degradation of the main components of the sample \textemdash hemicelluloses, cellulose, and lignin \citep{hu2016,cheng2015,perejon2011,orfao2001,muller-hagedorn2007}. Therefore, the multi-peaked rate of mass loss curve (derivative of mass loss curve) can be mathematically separated, or deconvolved, with a mixture model into individual peaks \textemdash each representing a single primary component. This method has been validated by studies comparing estimates to experimental measurements \citep{yang2006}. Plant trait measurement is guided by the principle of standardised, widely reproducible methods \citep{perez-harguindeguy2013}, but much of the published literature use commercial software to deconvolve the rate of mass loss curve \citetext{for example OriginPro \citealp{chen2017}, PeakFit \citealp{perejon2011}, Fityk \citealp{perejon2011}, or Datafit \citealp{cheng2015}}. Software accessibility and reproducibility may be one reason why thermogravimetric analysis has not yet been widely adopted by functional ecologists, despite being previously used to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucaplyts \citealp{orfao2001}}. \\
\\
The \verb|deconvolve| package provides an open-source set of functions to perform this deconvolution. Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, \verb|deconvolve| aims to provide context specific guidelines related to use of this model for thermal decay curve analysis and carbon component estimation, in order to maximise its utility and ease of uptake for researchers interested in this method.

\section*{Implementation and architecture}

\textbf{\textit{Collect and load data}}\\
We developed and tested the functions in this package using the thermogravimetric decay data for litter of 29 different plant species. Two species from this set are available as datasets in the package \textemdash the freshwater reed \textit{Juncus amabilis} (accessed as \verb|juncus|) and the freshwater fern \textit{Marsilea drumondii} (accessed as \verb|marsilea|). To ensure component estimates are an accurate representation of the original composition of the litter, it is important to dry samples as quickly as possible to prevent decomposition. Plant litter collected for this analysis was placed in moist plastic bags and stored in dark coolers until transported to the lab, and then moved to a dark, refrigerated room. We dried the fresh litter at 60 $^{\circ}$C for 72 hours and ground litter to \textless $40 \mu m$ using a Retsch Centrifugal Mill ZM200. We used 10\textendash20 mg subsamles of dry, ground litter for thermogravimetric analysis (TGA). Each sample was pyrolysed in an N$_2$ environment from 30\textendash800 $^{\circ}$C at a temperature ramp of 10 $^{\circ}$C/min using a Netzsch TGA-FTIR thermogravimetric analyser (Department of Biomedical Engineering, University of Melbourne). The resulting data is mass loss in grams against temperature (Fig.~\ref{Fig:massloss}).

<<>>=
library(deconvolve)
head(juncus)
@

\textbf{\textit{Process data}}\\
After we've loaded our data, we need to calculate the rate of mass loss across temperature. To do so, the \verb|process| function takes the derivative of our mass loss data, taking as arguments the dataset, the column names for the temperature and mass loss data, and a value for the starting mass of the sample. The function defaults to temperature data in Celsius, but you can also indicate the data is provided in Kelvin, by specifying the argument \verb|temp_type = K|.

<<>>=
deriv_juncus <- process(juncus,
                        temp = 'temp_C',
                        mass = 'mass_loss',
                        init_mass = 18.96)
deriv_juncus
@

The output of the \verb|process| function is a list of three items: the modified dataframe including the derivative thermogravimetric rate of mass loss data (DTG), the initial mass value that you supplied, and the maximum and minimum temperature of your data. If you \verb|plot()| the output of the \verb|process| function you will get two curves: the mass of sample across time and the rate of mass loss curve (Fig.~\ref{Fig:process}). If you're only interested in one plot, you can specify \verb|plot_type = mass| or \verb|plot_type = rate|.

<<eval = FALSE>>=
plot(deriv_juncus)
@

<<echo = FALSE, fig.cap = '\\label{Fig:process} Process function output from \\textit{Juncus amabilis} example dataset.', fig.subcap = c('\\label{Fig:massloss} Thermogravimetric mass loss curve.', '\\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample.'), out.width = '.49\\linewidth', fig.asp = 1, fig.ncol = 2>>=
plot(deriv_juncus, plot_type = 'mass')
plot(deriv_juncus, plot_type = 'rate')
@

\begin{table}[!ht]
	\caption{Exported functions}
	\label{Tab:functions}
	\centering
	\footnotesize
	\begin{tabularx}{\linewidth}{llX}
        		\toprule
        		Function family & Function name & Description \\
        		\midrule
		Data & \verb|juncus| & Example thermogravimetric data for \textit{Juncus amabilis} \\
		Data & \verb|marsilea| & Example thermogravimetric data for \textit{Marsilea drumondii} \\
		Basic use & \verb|process()| & Calculates the derivative rate of mass loss of thermogravimetric data \\
		Basic use & \verb|deconvolve()| & Deconvolves derivative rate of mass loss data \\
		Accessor function & \verb|temp_bounds()| & Access temperature bounds used to crop data for mixture model \\
		Accessor function & \verb|rate_data()| & Access processed dataframe including mass loss, rate of mass loss, and temperature \\
		Accessor function & \verb|model_fit()| & Access fit of nonlinear mixture model \\
		Accessor function & \verb|component_weights()| & Access mean, upper, and lower bounds for component weight estimates \\
		Fraser-Suzuki function & \verb|fs_function()| & Fraser-Suzuki equation for a single curve \\
		Fraser-Suzuki function & \verb|fs_mixture()| & Fraser-Suzuki mixture model equation \\
		Fraser-Suzuki function & \verb|fs_model()| & Non-linear model implementation of Fraser-Suzuki mixture model \\
		S3 method & \verb|print(<process>)| & Default print method for process object (derived from \verb|process()|) \\
		S3 method & \verb|plot(<process>)| & Default plot method for process object (derived from \verb|process()|) \\
		S3 method & \verb|print(<deconvolve>)| & Default print method for decon object (derived from \verb|deconvolve()|) \\
		S3 method & \verb|plot(<deconvolve>)| & Default plot method for process object (derived from \verb|deconvolve()|) \\
        		\bottomrule
	\end{tabularx}
\end{table}

\textbf{\textit{Deconvolve data}}\\
Once we have calculated the rate of mass loss, we use the \verb|deconvolve| function to estimate the proportions of carbon components. Under the hood, it does so with a series of steps that are described in detail below. First it crops the derivative rate of mass loss data, then estimates parameter values from the non-linear model, and finally integrates under each resulting curve to estimate weight proportions of primary components. We explain these steps in detail below. \\
\\
\textit{Cropping DTG data}\\
The rate of mass loss (i.e. negative first derivative or DTG) is a multi-peaked curve (Fig.~\ref{Fig:rateloss}) encompassing three main phases \citep{orfao2001}:
\begin{enumerate}
	\item A short period with a pronounced peak of moisture evolution, up until approximately 120 $^{\circ}$C.
	\item A wide mid-range of high mass loss, caused by devolatilisation of primary biomass carbon components, between approximately 120\textendash650 $^{\circ}$C.
	\item A final period of little mass loss when carbonaceous material associated with the inorganic fraction decomposes, after approximately 650 $^{\circ}$C.
\end{enumerate}
Since the overall DTG curve thus represents the loss of extractives, water, inorganic matter, and volatiles in addition to our components of interest \citep{hu2016}, we isolate mass loss from our primary biomass components by cropping the DTG data to Phase 2 (120\textendash650 $^{\circ}$C). The \verb|deconvolve| function defaults to cropping at 120 $^{\circ}$C and 700 $^{\circ}$C, but these can be modified with the \verb|lower_temp| and \verb|upper_temp| arguments.\\
\\
\textit{Non-linear mixture model}\\
Biomass components decompose relatively independently because they do not interact much during thermal volatilisation \citep{yang2006}.
Therefore, the cropped DTG curve can be mathematically deconvolved into constituent parts using a mixture model. The derivative rate of mass loss equation ($\frac{dm}{dT}$) can be expressed as the sum of $n$ independent reactions (Eq.~\ref{eqn:mixture_model}), as follows \citep{orfao2001}:

\begin{align}
	-\frac{dm}{dT} &= \sum\limits_{i=1}^n c_i\frac{d\alpha_{i}}{dT} \label{eqn:mixture_model} \\
	m &= \frac{M_T}{M_0} \label{eqn:fraction} \\
	c_i &= M_{0i} - M_{\infty i} \label{eqn:decayed_mass} \\
	\alpha_i &= \frac{M_{0i} - M_{Ti}}{M_{0i} - M_{\infty i}} \label{eqn:alpha}
\end{align}

where mass ($m$) is expressed as a fraction of mass at temperature $T$ ($M_T$) of the initial sample mass ($M_0$) (Eq.~\ref{eqn:fraction}), $c_i$ is the mass of component $i$ that is decayed (Eq.~\ref{eqn:decayed_mass}), and the mass loss curve of each individual component ($\frac{d\alpha_{i}}{dT}$) is the derivative of $\alpha_i$, the conversion of mass at a given temperature ($M_{Ti}$), from the initial ($M_{0i}$), given total mass lost between the initial and final ($M_{\infty i}$) temperature for each curve  (Eq.~\ref{eqn:alpha}).\\
\\
Although most of our results can be described with only $n = 3$ peaks, corresponding to a single curve each of hemicelluose, cellulose, and lignin, some species yield a second hemicellulose peak at a lower temperature, resulting in $n = 4$ independent curves This is because the soluble carbohydrates in plant tissue can take many forms, including xylan, amylose, etc., which apparently degrade at different temperatures \citep[see also][]{chen2017,muller-hagedorn2007}. \verb|deconvolve| will decide whether three or four curves are best using an internal function that determines if there is a peak below 220 $^{\circ}$C. Upon inspection of your curve you can override this by modifying the \verb|n_curves| argument.\\
\\
In order to fit the mixture model, we must determine the shape of the individual curves ($\frac{d\alpha_{i}}{dT}$) that are summed to produce it. Many different functions have been proposed: the asymmetric bi-Gaussian \citep{sun2015}, logistic \citep{barbadillo2007}, Weibull \citep{cai2007}, asymmetric double sigmoidal \citep{chen2017}, and the Fraser-Suzuki function \citep{perejon2011,hu2016}. Comparisons of several techniques \citep{svoboda2013,perejon2011,cheng2015} found that the Fraser-Suzuki function best fit these kinetic curves, since it allows for asymmetry (a parametric examination of the Fraser-Suzuki function can be found in Fig.~\ref{Fig:fs_simulation}). We therefore use the Fraser-Suzuki function to describe the rate expression of a single curve (Eq.~\ref{eqn:fs_function}) as follows:

\begin{gather}\label{eqn:fs_function}
	\frac{d\alpha_i}{dT} = h_i\ exp\bigg\{-\frac{ln2}{s_i^2}\Big[ln\Big(1 + 2s_i \frac{T - p_i}{w_i}\Big)\Big]^2\bigg\}
\end{gather}

where T is temperature ($^\circ$C), and the parameters $h_i$, $s_i$, $p_i$, and $w_i$ are height, skew, position, and width of the curve, respectively. In total, our model estimates 12 or 16 parameters, one for each parameter of Eq.~\ref{eqn:fs_function} for either 3 or 4 primary components.

<<echo = FALSE, fig.cap = '\\label{Fig:fs_simulation} Parametric examination of Fraser-Suzuki function using simulated data', out.width = '.9\\linewidth', fig.asp = 1>>=
simulate_fraser_suzuki <- function () {

  x <- seq(200, 700)
  h1 <- deconvolve::fs_function(x, 0.004, -0.25, 400, 60)
  h2 <- deconvolve::fs_function(x, 0.006, -0.25, 400, 60)
  h3 <- deconvolve::fs_function(x, 0.008, -0.25, 400, 60)
  h4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)

  s1 <- deconvolve::fs_function(x, 0.010, -0.55, 400, 60)
  s2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  s3 <- deconvolve::fs_function(x, 0.010, 0.25, 400, 60)
  s4 <- deconvolve::fs_function(x, 0.010, 0.55, 400, 60)

  p1 <- deconvolve::fs_function(x, 0.010, -0.25, 350, 60)
  p2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  p3 <- deconvolve::fs_function(x, 0.010, -0.25, 450, 60)
  p4 <- deconvolve::fs_function(x, 0.010, -0.25, 500, 60)

  w1 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 30)
  w2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  w3 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 90)
  w4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 120)

  par(oma = c(5, 5, 0, 2), mar = c(1, 3, 2, 0), mfrow = c(2, 2))

  plot(x, h4, type = 'l', lty = 4, xaxt = 'n', yaxt = 'n', cex = 1.6,
       xlab = '',
       ylab = '')
  axis(side = 2, at = c(0, 0.002, 0.004, 0.006, 0.008, 0.010), cex.axis = 1.2,
       labels = c(0, 0.002, 0.004, 0.006, 0.008, 0.010))
  lines(x, h2, lty = 2)
  lines(x, h3, lty = 3)
  lines(x, h1, lty = 1)
  legend('topleft', legend = '(a)', bty = 'n', cex = 1.6)
  legend('topright', legend = c(expression(paste('h = 0.004 C'^'-1')),
                                expression(paste('h = 0.006 C'^'-1')),
                                expression(paste('h = 0.008 C'^'-1')),
                                expression(paste('h = 0.010 C'^'-1')),
                                's = -0.25',
                                'p = 400 C',
                                'w = 60 C'),
         bty = 'n', cex = 1.2,
         lty = c(1, 2, 3, 4, NA, NA, NA)
  )

  plot(x, s1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
       xlab = '',
       ylab = '')
  lines(x, s2, lty = 2)
  lines(x, s3, lty = 3)
  lines(x, s4, lty = 4)
  legend('topleft', legend = '(b)', bty = 'n', cex = 1.6)
  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
                                's = -0.5',
                                's = -0.25',
                                's = 0.25',
                                's = 0.55',
                                'p = 400 C',
                                'w = 60 C'),
         bty = 'n', cex = 1.2,
         lty = c(NA, 1, 2, 3, 4, NA, NA)
  )

  plot(x, p1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
       xlab = '',
       ylab = '')
  axis(side = 1, at = c(200, 300, 400, 500, 600, 700), cex.axis = 1.2,
       labels = c(200, 300, 400, 500, 600, 700))
  axis(side = 2, at = c(0, 0.002, 0.004, 0.006, 0.008, 0.010), cex.axis = 1.2,
       labels = c(0, 0.002, 0.004, 0.006, 0.008, 0.010))
  lines(x, p2, lty = 2)
  lines(x, p3, lty = 3)
  lines(x, p4, lty = 4)
  legend('topleft', legend = '(c)', bty = 'n', cex = 1.6)
  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
                                's = -0.25',
                                'p = 350 C',
                                'p = 400 C',
                                'p = 450 C',
                                'p = 500 C',
                                'w = 60 C'),
         bty = 'n', cex = 1.2,
         lty = c(NA, NA, 1, 2, 3, 4, NA)
  )

  plot(x, w1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
       xlab = '',
       ylab = '')
  axis(side = 1, at = c(200, 300, 400, 500, 600, 700), cex.axis = 1.2,
       labels = c(200, 300, 400, 500, 600, 700))
  lines(x, w2, lty = 2)
  lines(x, w3, lty = 3)
  lines(x, w4, lty = 4)
  legend('topleft', legend = '(d)', bty = 'n', cex = 1.6)
  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
                                's = -0.25',
                                'p = 400 C',
                                'w = 30 C',
                                'w = 60 C',
                                'w = 90 C',
                                'w = 120'),
         bty = 'n', cex = 1.2,
         lty = c(NA, NA, NA, 1, 2, 3, 4))

  mtext(text = 'Temperature (C)',
        side = 1,
        line = 2.1,
        outer = TRUE,
        cex = 1.8)
  mtext(text = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
        side = 2,
        line = 0.9,
        outer = TRUE,
        cex = 1.8)
}
simulate_fraser_suzuki()
@

\verb|deconvolve| uses non-linear optimisation with residual sum of squares to fit the rate expression \citetext{as in \citealp{cheng2015}}. Starting values were selected based on curves depicted in the literature \citep{muller-hagedorn2007} and from the results of running an identical deconvolution on pure cellulose and lignin samples. Hemicelluloses decay in a reasonably narrow band beginning at a lower temperature \citep{muller-hagedorn2007}, so we used 270 for position and 50 for width. Linear cellulose crystals decay at a higher temperature, but decay more rapidly after peak temperatures are reached, so starting position was set to 310 and width to 30. Lignin typically decays beginning at a high temperature and over a wide interval \citep{chen2015}, so position and width began at 410 and 200, respectively. If necessary, these starting values can also be modified in the \verb|deconvolve| function with the \verb|start_vec|, \verb|lower_vec|, and \verb|upper_vec| arguments. These initial starting values are optimised before model fitting using the \verb|NLOPTR_LN_BOBYQA| algorithm \citep{bobyqa} within the \verb|nloptr| \citep{nloptr} package. Finally, optimised starting values are fit to the non-linear mixture model using \verb|nlsLM()| in the \verb|minpack.lm| \citep{minpack.lm} package.\\
\\
\textit{Component weights}\\
Once overall curve parameters are fit, we can use the pass each components's paremeter estimates to a single Fraser-Suzuki function, and calculate the weight of the component in the overall sample by integrating under the curve (Eq.~\ref{eqn:integration}). To estimate the uncertainty of the weight predictions we calculated the 95\% interval of the weight estimates across a random sample of parameter estimates, drawn in proportion to their likelihood. We assumed a truncated multivariate normal distribution, since the parameters are constrained to positive values, using the modelling package \verb|tmvtnorm| \citep{tmvtnorm}.

\begin{gather}\label{eqn:integration}
	\alpha_i = \int_{120}^{650} h_i\ exp\bigg\{-\frac{ln2}{s_i^2}\Big[ln\Big(1 + 2s_i \frac{T - p_i}{w_i}\Big)\Big]^2\bigg\} dT
\end{gather}

We interpret that the curve located around 250\textendash270 $^\circ$C corresponds to primary hemicelluloses (HC), around 310\textendash330 $^\circ$C to cellulose (CL), and around 330\textendash350 $^\circ$C to lignin (LG). If present, the fourth curve located below 200 $^\circ$C corresponds to the most simple hemicelluloses (HC-1). The second dataset included in the package, \verb|marsilea|, is an example of a four-curve deconvolution. A worked example can be found in the package vignettes.

<<>>=
output_juncus <- deconvolve(deriv_juncus)
output_juncus
@

The output of the \verb|deconvolve| function is a list of five items:
\begin{enumerate}
\item{the data used to fit the function,
<<>>=
DTG_data <- rate_data(output_juncus)
head(DTG_data)
@
}
\item{the upper and lower temperature bounds to which the data were cropped,
<<>>=
temp_bounds(output_juncus)
@

}
\item{the model fit including parameter estimates,
<<eval = FALSE>>=
model_fit(output_juncus)
@

<<echo = FALSE>>=
cat(paste0('Nonlinear regression model\n',
          '  model: deriv ~ fs_mixture(temp_C, height_1, skew_1, position_1,\n',
          '    width_1, height_2, skew_2, position_2, width_2, height_3,\n',
          '    skew_3, position_3, width_3)\n',
          '  data: dataframe\n',
          '  height_1   skew_1     position_1 width_1    height_2   skew_2\n',
          '  3.944e-03  1.258e-01  2.662e+02  5.106e+01  5.793e-03  1.344e-02\n',
          '  position_2 width_2    height_3   skew_3     position_3 width_3\n',
          '  3.173e+02  2.866e+01  1.163e-03  1.085e-01  3.300e+02  2.500e+02\n',
          '  residual sum-of-squares: 9.299e-06\n\n',
          'Number of iterations to convergence: 23\n',
          'Achieved convergence tolerance: 1.49e-08'))
@
}
\item{the number of curves,
<<>>=
output_juncus$n_curves
@
}
\item{and the mean and upper and lower estimates of the weight of each component.
<<>>=
component_weights(output_juncus)
@
}
\end{enumerate}
If you \verb|plot()| the output of the \verb|deconvolve| function you will see the result of the deconvolution (Fig.~\ref{Fig:decon}). This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components curves.

<<fig.cap = '\\label{Fig:decon} Deconvolution of \textit{Juncus amabilis} example dataset. Mass loss data overlaid with output of deconvolution. Rate of mass loss scaled by initial mass of sample.'>>=
plot(output_juncus)
@

All analyses were conducted within the statistical computing environment, R \citep{R}, and data and R code for this paper are available on the package Github (\url{https://github.com/smwindecker/deconvolve/}. In order to aid in the reproducibility of this work, our code was written using a \verb|remake| framework \citep{remake}. This allows others to readily reproduce our work by calling \verb|remake()| in R.

This work is the first attempt to use thermogravimetric analysis (TGA) with a mixture model to estimate the partitioning of carbon in a suite of wetland plants.

\section*{Quality control}
All the functions of \verb|deconvolve| were tested to see if they produced the desired output. ?... The structure of the package successfully passed the \verb|CRAN R CMD| check and the results from this check can be found on CRAN.

\section*{(2) Availability}
\vspace{0.5cm}
\section*{Operating system}
The package can work with either Windows, Mac OS X, or Linux.

\section*{Programming language}
R version XXX or higher.

\section*{Additional system requirements}
An internet connection is required to install the \verb|deconvolve| package.

\section*{Dependencies}
R packages: \verb|graphics|, \verb|minpack.lm|, \verb|nloptr|, \verb|stats|, \verb|tmvtnorm|, \verb|zoo|.

\section*{List of contributors}
This package was created by Saras Windecker and Dr. Nick Golding.

\section*{Software location:}

{\bf Archive} (e.g. institutional repository, general repository) (required – please see instructions on journal website for depositing archive copy of software in a suitable repository)

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] The name of the archive.
	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
	\item[Licence:] Open license under which the software is licensed.
	\item[Publisher:] Name of the person who deposited the software.
	\item[Version published:] The version number of the software archived.
	\item[Date published:] dd/mm/yy
\end{description}

{\bf Code repository} GitHub

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \url{https://github.com/smwindecker/deconvolve/}
	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
	\item[Licence:] Open license under which the software is licensed.
	\item[Date published:] dd/mm/yy
\end{description}

\section*{Language}
R

\section*{(3) Reuse potential}
This should include the use cases for the software,

The Fraser-Suzuki family of functions are exported to allow the user to create their own plots from the model outputs. Detailed descriptions of how to do so are included in the package vignettes.

This package was designed with both the user and developer in mind. There are several vignettes available with the package and on the package website (\url{https://smwindecker.github.io/deconvolve/}) facilitating exploration of package functionality. For those that wish to contribute to the package, it is hosted on Github, and they can log issues via the issues tracker (\url{https://github.com/smwindecker/deconvolve/issues}) or submit a pull request to add functionality to the package.

\section*{Acknowledgements}
The authors would like to thank Dr. Nick Tierney for reviewing an early version of the package. We would like to thank the University of Melbourne Department of Chemical and Biomolecular Engineering for access to and training on the TGA-FTIR. Vegetation collection for data used to build and verify the model was conducted under Victorian Department of Environment, Land, Water and Planning Permit No 10007429. We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for assistance in the field collecting plant specimens.

\section*{Funding statement}
The authors would like to acknowledge support from the Australian Research Council Centre of Excellence for Environmental Decisions, the Holsworth Wildlife Reseach Endowment \& The Ecological Society of Australia, and the Melbourne International Research Scholarship and Melbourne International Fee Remission Scholarship from University of Melbourne.

\section*{Competing interests}
The authors declare that they have no competing interests.

\section*{References}
\bibliography{bibliography_papers,bibliography_packages}

\vspace{2cm}

\end{document}

### 2018-08-01 manuscript/manuscript.tex
change default for manuscript to knitr not Sweave and add manuscript

--- 2018-08-01 manuscript/manuscript.Rnw
@@
 
-\documentclass{jors}
+\documentclass{jors}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 \usepackage{listings}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
-
-<<echo = FALSE>>=
-opts_chunk$set(size = 'footnotesize',
-               fig.pos = 'H',
-               root.dir = 'manuscript/')
-@
 
@@
 
-<<>>=
-library(deconvolve)
-head(juncus)
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{library}\hlstd{(deconvolve)}
+\hlkwd{head}\hlstd{(juncus)}
+\end{alltt}
+\begin{verbatim}
+##   temp_C mass_loss
+## 1 31.453 -0.000931
+## 2 31.452 -0.001340
+## 3 31.450 -0.001350
+## 4 31.450 -0.001660
+## 5 31.450 -0.001680
+## 6 31.450 -0.001800
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 
-<<>>=
-deriv_juncus <- process(juncus,
-                        temp = 'temp_C',
-                        mass = 'mass_loss',
-                        init_mass = 18.96)
-deriv_juncus
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{deriv_juncus} \hlkwb{<-} \hlkwd{process}\hlstd{(juncus,}
+                        \hlkwc{temp} \hlstd{=} \hlstr{'temp_C'}\hlstd{,}
+                        \hlkwc{mass} \hlstd{=} \hlstr{'mass_loss'}\hlstd{,}
+                        \hlkwc{init_mass} \hlstd{=} \hlnum{18.96}\hlstd{)}
+\hlstd{deriv_juncus}
+\end{alltt}
+\begin{verbatim}
+## Derivative thermogravimetry data (DTG) calculated for
+##  768 datapoints from 31.5 to 798.52 degrees C.
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 
-<<eval = FALSE>>=
-plot(deriv_juncus)
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{plot}\hlstd{(deriv_juncus)}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
 
-<<echo = FALSE, fig.cap = '\\label{Fig:process} Process function output from \\textit{Juncus amabilis} example dataset.', fig.subcap = c('\\label{Fig:massloss} Thermogravimetric mass loss curve.', '\\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample.'), out.width = '.49\\linewidth', fig.asp = 1, fig.ncol = 2>>=
-plot(deriv_juncus, plot_type = 'mass')
-plot(deriv_juncus, plot_type = 'rate')
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+\subfloat[\label{Fig:massloss} Thermogravimetric mass loss curve.\label{fig:unnamed-chunk-51}]{\includegraphics[width=.49\linewidth]{figure/unnamed-chunk-5-1} }
+\subfloat[\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample.\label{fig:unnamed-chunk-52}]{\includegraphics[width=.49\linewidth]{figure/unnamed-chunk-5-2} }\caption{\label{Fig:process} Process function output from \textit{Juncus amabilis} example dataset.}\label{fig:unnamed-chunk-5}
+\end{figure}
+
+\end{knitrout}
 
@@
 
-<<echo = FALSE, fig.cap = '\\label{Fig:fs_simulation} Parametric examination of Fraser-Suzuki function using simulated data', out.width = '.9\\linewidth', fig.asp = 1>>=
-simulate_fraser_suzuki <- function () {
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+\includegraphics[width=.9\linewidth]{figure/unnamed-chunk-6-1} \caption{\label{Fig:fs_simulation} Parametric examination of Fraser-Suzuki function using simulated data}\label{fig:unnamed-chunk-6}
+\end{figure}
 
-  x <- seq(200, 700)
-  h1 <- deconvolve::fs_function(x, 0.004, -0.25, 400, 60)
-  h2 <- deconvolve::fs_function(x, 0.006, -0.25, 400, 60)
-  h3 <- deconvolve::fs_function(x, 0.008, -0.25, 400, 60)
-  h4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
-
-  s1 <- deconvolve::fs_function(x, 0.010, -0.55, 400, 60)
-  s2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
-  s3 <- deconvolve::fs_function(x, 0.010, 0.25, 400, 60)
-  s4 <- deconvolve::fs_function(x, 0.010, 0.55, 400, 60)
-
-  p1 <- deconvolve::fs_function(x, 0.010, -0.25, 350, 60)
-  p2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
-  p3 <- deconvolve::fs_function(x, 0.010, -0.25, 450, 60)
-  p4 <- deconvolve::fs_function(x, 0.010, -0.25, 500, 60)
-
-  w1 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 30)
-  w2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
-  w3 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 90)
-  w4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 120)
-
-  par(oma = c(5, 5, 0, 2), mar = c(1, 3, 2, 0), mfrow = c(2, 2))
-
-  plot(x, h4, type = 'l', lty = 4, xaxt = 'n', yaxt = 'n', cex = 1.6,
-       xlab = '',
-       ylab = '')
-  axis(side = 2, at = c(0, 0.002, 0.004, 0.006, 0.008, 0.010), cex.axis = 1.2,
-       labels = c(0, 0.002, 0.004, 0.006, 0.008, 0.010))
-  lines(x, h2, lty = 2)
-  lines(x, h3, lty = 3)
-  lines(x, h1, lty = 1)
-  legend('topleft', legend = '(a)', bty = 'n', cex = 1.6)
-  legend('topright', legend = c(expression(paste('h = 0.004 C'^'-1')),
-                                expression(paste('h = 0.006 C'^'-1')),
-                                expression(paste('h = 0.008 C'^'-1')),
-                                expression(paste('h = 0.010 C'^'-1')),
-                                's = -0.25',
-                                'p = 400 C',
-                                'w = 60 C'),
-         bty = 'n', cex = 1.2,
-         lty = c(1, 2, 3, 4, NA, NA, NA)
-  )
-
-  plot(x, s1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
-       xlab = '',
-       ylab = '')
-  lines(x, s2, lty = 2)
-  lines(x, s3, lty = 3)
-  lines(x, s4, lty = 4)
-  legend('topleft', legend = '(b)', bty = 'n', cex = 1.6)
-  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
-                                's = -0.5',
-                                's = -0.25',
-                                's = 0.25',
-                                's = 0.55',
-                                'p = 400 C',
-                                'w = 60 C'),
-         bty = 'n', cex = 1.2,
-         lty = c(NA, 1, 2, 3, 4, NA, NA)
-  )
-
-  plot(x, p1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
-       xlab = '',
-       ylab = '')
-  axis(side = 1, at = c(200, 300, 400, 500, 600, 700), cex.axis = 1.2,
-       labels = c(200, 300, 400, 500, 600, 700))
-  axis(side = 2, at = c(0, 0.002, 0.004, 0.006, 0.008, 0.010), cex.axis = 1.2,
-       labels = c(0, 0.002, 0.004, 0.006, 0.008, 0.010))
-  lines(x, p2, lty = 2)
-  lines(x, p3, lty = 3)
-  lines(x, p4, lty = 4)
-  legend('topleft', legend = '(c)', bty = 'n', cex = 1.6)
-  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
-                                's = -0.25',
-                                'p = 350 C',
-                                'p = 400 C',
-                                'p = 450 C',
-                                'p = 500 C',
-                                'w = 60 C'),
-         bty = 'n', cex = 1.2,
-         lty = c(NA, NA, 1, 2, 3, 4, NA)
-  )
-
-  plot(x, w1, type = 'l', lty = 1, xaxt = 'n', yaxt = 'n', cex = 1.6,
-       xlab = '',
-       ylab = '')
-  axis(side = 1, at = c(200, 300, 400, 500, 600, 700), cex.axis = 1.2,
-       labels = c(200, 300, 400, 500, 600, 700))
-  lines(x, w2, lty = 2)
-  lines(x, w3, lty = 3)
-  lines(x, w4, lty = 4)
-  legend('topleft', legend = '(d)', bty = 'n', cex = 1.6)
-  legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
-                                's = -0.25',
-                                'p = 400 C',
-                                'w = 30 C',
-                                'w = 60 C',
-                                'w = 90 C',
-                                'w = 120'),
-         bty = 'n', cex = 1.2,
-         lty = c(NA, NA, NA, 1, 2, 3, 4))
-
-  mtext(text = 'Temperature (C)',
-        side = 1,
-        line = 2.1,
-        outer = TRUE,
-        cex = 1.8)
-  mtext(text = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
-        side = 2,
-        line = 0.9,
-        outer = TRUE,
-        cex = 1.8)
-}
-simulate_fraser_suzuki()
-@
+\end{knitrout}
 
@@
 
-<<>>=
-output_juncus <- deconvolve(deriv_juncus)
-output_juncus
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{output_juncus} \hlkwb{<-} \hlkwd{deconvolve}\hlstd{(deriv_juncus)}
+\hlstd{output_juncus}
+\end{alltt}
+\begin{verbatim}
+## Deconvolution by 3-part Fraser-Suzuki mixture model fitted to 
+## 580 datapoints from 120 to 700 degrees C.
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 \item{the data used to fit the function,
-<<>>=
-DTG_data <- rate_data(output_juncus)
-head(DTG_data)
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{DTG_data} \hlkwb{<-} \hlkwd{rate_data}\hlstd{(output_juncus)}
+\hlkwd{head}\hlstd{(DTG_data)}
+\end{alltt}
+\begin{verbatim}
+##       temp_C        deriv   mass_T
+## 5325 120.514 9.570652e-05 17.91630
+## 5384 121.501 9.885901e-05 17.91445
+## 5445 122.515 1.003878e-04 17.91252
+## 5505 123.514 9.133606e-05 17.91079
+## 5565 124.513 6.493836e-05 17.90956
+## 5625 125.509 8.578618e-05 17.90794
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 }
 \item{the upper and lower temperature bounds to which the data were cropped,
-<<>>=
-temp_bounds(output_juncus)
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{temp_bounds}\hlstd{(output_juncus)}
+\end{alltt}
+\begin{verbatim}
+## [1] 120 700
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 \item{the model fit including parameter estimates,
-<<eval = FALSE>>=
-model_fit(output_juncus)
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{model_fit}\hlstd{(output_juncus)}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
 
-<<echo = FALSE>>=
-cat(paste0('Nonlinear regression model\n',
-          '  model: deriv ~ fs_mixture(temp_C, height_1, skew_1, position_1,\n',
-          '    width_1, height_2, skew_2, position_2, width_2, height_3,\n',
-          '    skew_3, position_3, width_3)\n',
-          '  data: dataframe\n',
-          '  height_1   skew_1     position_1 width_1    height_2   skew_2\n',
-          '  3.944e-03  1.258e-01  2.662e+02  5.106e+01  5.793e-03  1.344e-02\n',
-          '  position_2 width_2    height_3   skew_3     position_3 width_3\n',
-          '  3.173e+02  2.866e+01  1.163e-03  1.085e-01  3.300e+02  2.500e+02\n',
-          '  residual sum-of-squares: 9.299e-06\n\n',
-          'Number of iterations to convergence: 23\n',
-          'Achieved convergence tolerance: 1.49e-08'))
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## Nonlinear regression model
+##   model: deriv ~ fs_mixture(temp_C, height_1, skew_1, position_1,
+##     width_1, height_2, skew_2, position_2, width_2, height_3,
+##     skew_3, position_3, width_3)
+##   data: dataframe
+##   height_1   skew_1     position_1 width_1    height_2   skew_2
+##   3.944e-03  1.258e-01  2.662e+02  5.106e+01  5.793e-03  1.344e-02
+##   position_2 width_2    height_3   skew_3     position_3 width_3
+##   3.173e+02  2.866e+01  1.163e-03  1.085e-01  3.300e+02  2.500e+02
+##   residual sum-of-squares: 9.299e-06
+## 
+## Number of iterations to convergence: 23
+## Achieved convergence tolerance: 1.49e-08
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 }
 \item{the number of curves,
-<<>>=
-output_juncus$n_curves
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{output_juncus}\hlopt{$}\hlstd{n_curves}
+\end{alltt}
+\begin{verbatim}
+## NULL
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 }
 \item{and the mean and upper and lower estimates of the weight of each component.
-<<>>=
-component_weights(output_juncus)
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{component_weights}\hlstd{(output_juncus)}
+\end{alltt}
+\begin{verbatim}
+##   HC CL LG value_type
+## 1  0  0  0       2.5%
+## 2  0  0  0      97.5%
+## 3  0  0  0       mean
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 }
@@
 
-<<fig.cap = '\\label{Fig:decon} Deconvolution of \textit{Juncus amabilis} example dataset. Mass loss data overlaid with output of deconvolution. Rate of mass loss scaled by initial mass of sample.'>>=
-plot(output_juncus)
-@
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{plot}\hlstd{(output_juncus)}
+\end{alltt}
+\end{kframe}\begin{figure}[H]
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-14-1} \caption{\label{Fig:decon} Deconvolution of 	extit{Juncus amabilis} example dataset.
+Mass loss data overlaid with output of deconvolution.
+Rate of mass loss scaled by initial mass of sample.}\label{fig:unnamed-chunk-14}
+\end{figure}
+
+\end{knitrout}
 

### 2018-08-01 README.Rmd
ange name to mixchar

@@
 
-[![Build Status](https://travis-ci.com/smwindecker/deconvolve.svg?branch=master)](https://travis-ci.org/smwindecker/deconvolve)
-[![codecov](https://codecov.io/gh/smwindecker/deconvolve/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/deconvolve)
+[![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
+[![codecov](https://codecov.io/gh/smwindecker/mixchar/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/mixchar)
 [![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
@@
 
-You can install `deconvolve` from [GitHub](https://github.com/) with:
+You can install `mixchar` from [GitHub](https://github.com/) with:
 
@@
 # install.packages("devtools")
-devtools::install_github("smwindecker/deconvolve", build_vignettes = TRUE)
+devtools::install_github("smwindecker/mixchar", build_vignettes = TRUE)
 ```
@@
 ```{r}
-library(deconvolve)
+library(mixchar)
 head(juncus)
@@
 ```{r}
-vignette('deconvolve')
+vignette('mixchar')
 ```
@@
 This is still a work in progress!
-If you see any mistakes, or find that the code is not functioning well on your data, let us know by logging a bug on the [issues page](http://www.github.com/smwindecker/deconvolve/issues).
+If you see any mistakes, or find that the code is not functioning well on your data, let us know by logging a bug on the [issues page](http://www.github.com/smwindecker/mixchar/issues).
 

### 2018-08-01 manuscript/manuscript.Rnw
ange name to mixchar

@@
 \section*{Title}
-deconvolve: An R package for the deconvolution of thermal decay curves
+mixchar: An R package for the deconvolution of thermal decay curves
 
@@
 \\
-The \verb|deconvolve| package provides an open-source set of functions to perform this deconvolution.
-Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, \verb|deconvolve| aims to provide context specific guidelines related to use of this model for thermal decay curve analysis and carbon component estimation, in order to maximise its utility and ease of uptake for researchers interested in this method.
+The \verb|mixchar| package provides an open-source set of functions to perform this deconvolution.
+Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, \verb|mixchar| aims to provide context specific guidelines related to use of this model for thermal decay curve analysis and carbon component estimation, in order to maximise its utility and ease of uptake for researchers interested in this method.
 
@@
 <<>>=
-library(deconvolve)
+library(mixchar)
 head(juncus)
@@
   x <- seq(200, 700)
-  h1 <- deconvolve::fs_function(x, 0.004, -0.25, 400, 60)
-  h2 <- deconvolve::fs_function(x, 0.006, -0.25, 400, 60)
-  h3 <- deconvolve::fs_function(x, 0.008, -0.25, 400, 60)
-  h4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
+  h1 <- mixchar::fs_function(x, 0.004, -0.25, 400, 60)
+  h2 <- mixchar::fs_function(x, 0.006, -0.25, 400, 60)
+  h3 <- mixchar::fs_function(x, 0.008, -0.25, 400, 60)
+  h4 <- mixchar::fs_function(x, 0.010, -0.25, 400, 60)
 
-  s1 <- deconvolve::fs_function(x, 0.010, -0.55, 400, 60)
-  s2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
-  s3 <- deconvolve::fs_function(x, 0.010, 0.25, 400, 60)
-  s4 <- deconvolve::fs_function(x, 0.010, 0.55, 400, 60)
+  s1 <- mixchar::fs_function(x, 0.010, -0.55, 400, 60)
+  s2 <- mixchar::fs_function(x, 0.010, -0.25, 400, 60)
+  s3 <- mixchar::fs_function(x, 0.010, 0.25, 400, 60)
+  s4 <- mixchar::fs_function(x, 0.010, 0.55, 400, 60)
 
-  p1 <- deconvolve::fs_function(x, 0.010, -0.25, 350, 60)
-  p2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
-  p3 <- deconvolve::fs_function(x, 0.010, -0.25, 450, 60)
-  p4 <- deconvolve::fs_function(x, 0.010, -0.25, 500, 60)
+  p1 <- mixchar::fs_function(x, 0.010, -0.25, 350, 60)
+  p2 <- mixchar::fs_function(x, 0.010, -0.25, 400, 60)
+  p3 <- mixchar::fs_function(x, 0.010, -0.25, 450, 60)
+  p4 <- mixchar::fs_function(x, 0.010, -0.25, 500, 60)
 
-  w1 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 30)
-  w2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
-  w3 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 90)
-  w4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 120)
+  w1 <- mixchar::fs_function(x, 0.010, -0.25, 400, 30)
+  w2 <- mixchar::fs_function(x, 0.010, -0.25, 400, 60)
+  w3 <- mixchar::fs_function(x, 0.010, -0.25, 400, 90)
+  w4 <- mixchar::fs_function(x, 0.010, -0.25, 400, 120)
 
@@
 
-All analyses were conducted within the statistical computing environment, R \citep{R}, and data and R code for this paper are available on the package Github (\url{https://github.com/smwindecker/deconvolve/}.
+All analyses were conducted within the statistical computing environment, R \citep{R}, and data and R code for this paper are available on the package Github (\url{https://github.com/smwindecker/mixchar/}.
 In order to aid in the reproducibility of this work, our code was written using a \verb|remake| framework \citep{remake}.
@@
 \section*{Quality control}
-All the functions of \verb|deconvolve| were tested to see if they produced the desired output.
+All the functions of \verb|mixchar| were tested to see if they produced the desired output.
 ?...
@@
 \section*{Additional system requirements}
-An internet connection is required to install the \verb|deconvolve| package.
+An internet connection is required to install the \verb|mixchar| package.
 
@@
 \begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] \url{https://github.com/smwindecker/deconvolve/}
+	\item[Name:] \url{https://github.com/smwindecker/mixchar/}
 	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
@@
 This package was designed with both the user and developer in mind.
-There are several vignettes available with the package and on the package website (\url{https://smwindecker.github.io/deconvolve/}) facilitating exploration of package functionality.
-For those that wish to contribute to the package, it is hosted on Github, and they can log issues via the issues tracker (\url{https://github.com/smwindecker/deconvolve/issues}) or submit a pull request to add functionality to the package.
+There are several vignettes available with the package and on the package website (\url{https://smwindecker.github.io/mixchar/}) facilitating exploration of package functionality.
+For those that wish to contribute to the package, it is hosted on Github, and they can log issues via the issues tracker (\url{https://github.com/smwindecker/mixchar/issues}) or submit a pull request to add functionality to the package.
 

### 2018-08-01 tests/testthat.R

@@ -1,4 +1,4 @@
 library(testthat)
-library(deconvolve)
+library(mixchar)
 
-test_check("deconvolve")
+test_check("mixchar")

### 2018-08-01 tic.R

@@ -2,7 +2,7 @@ add_package_checks()
 
 if (Sys.getenv("id_rsa") != "") {
   # pkgdown documentation can be built optionally. Other example criteria:
-  # - `inherits(ci(), "TravisCI")`: Only for Travis CI
+  inherits(ci(), "TravisCI")#`: Only for Travis CI
   # - `ci()$is_tag()`: Only for tags, not for branches
   # - `Sys.getenv("BUILD_PKGDOWN") != ""`: If the env var "BUILD_PKGDOWN" is set
   # - `Sys.getenv("TRAVIS_EVENT_TYPE") == "cron"`: Only for Travis cron jobs

### 2018-08-01 vignettes/figures.R

@@ -1,99 +1,0 @@
-
-tga_theory <- function (data) {
-
-  # read raw TGA
-  tmp <- deconvolve::process(data, 'temp_C', 'mass_loss', 18.96)
-
-  # plot TG curve
-  layout(matrix(c(1,2,3), nrow = 1, ncol = 3, byrow = TRUE), heights = c(0.8, 0.2))
-  par(oma = c(5, 3, 0, 2), mar = c(3, 6, 3, 3))
-
-  plot(tmp$data$temp_C, tmp$data$mass_T, yaxs = 'i', ylim = c(0, 22), xlim = c(0, 900),
-       xaxs = 'i', ylab = 'Mass (mg)', xlab = '', xaxt = 'n', yaxt = 'n',
-       pch = 20, cex = 0.3, cex.lab = 3)
-  axis(side = 1, at = c(0, 200, 400, 600, 800), cex.axis = 2.8, labels = c(0, 200, 400, 600, 800))
-  axis(side = 2, at = c(0, 10, 20), cex.axis = 2.8,
-       labels = c(0, 10, 20))
-  legend('topleft',
-         legend = '(a)',
-         bty = 'n',
-         cex = 2.5)
-  arrows(x0 = 266, y0 = 19, x1 = 266, y1 = 17, lwd = 2, length = 0.1)
-  arrows(x0 = 317, y0 = 15, x1 = 317, y1 = 13, lwd = 2, length = 0.1)
-  arrows(x0 = 340, y0 = 11.5, x1 = 340, y1 = 9.5, lwd = 2, length = 0.1)
-
-  # plot DTG curve
-  plot(tmp$data$temp_C, tmp$data$deriv, yaxs = 'i', ylim = c(0, 0.009),
-       xaxs = 'i', ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')), xlab = '', xaxt = 'n', yaxt = 'n',
-       pch = 20, cex.lab = 3, cex = 0.9)
-  axis(side = 1, at = c(0, 200, 400, 600, 800), cex.axis = 2.8, labels = c(0, 200, 400, 600, 800))
-  axis(side = 2, at = c(0, 0.004, 0.008), cex.axis = 2.8,
-       labels = c(0, 0.004, 0.008))
-  legend('topleft',
-         legend = '(b)',
-         bty = 'n',
-         cex = 2.5)
-
-  # deconvolve data
[…]

### 2018-08-01 manuscript/manuscript.tex
update docs after re running with new version

@@
 \begin{alltt}
-\hlkwd{library}\hlstd{(deconvolve)}
+\hlkwd{library}\hlstd{(mixchar)}
 \hlkwd{head}\hlstd{(juncus)}
@@
 \begin{verbatim}
-## NULL
+## [1] 3
 \end{verbatim}

### 2018-08-01 R/plot.decon.R

@@ -29,7 +29,7 @@ plot.decon <- function (x, bw = TRUE, ...) {
 
   if (isTRUE(bw)) {
 
-    if (x$n_peaks == 4) {
+    if (x$n_curves == 4) {
       y1 <- fs_mixture(temp = temp,
                        height_1 = params['height_1',], skew_1 = params['skew_1',],
                        position_1 = params['position_1',], width_1 = params['width_1',],
@@ -56,7 +56,7 @@ plot.decon <- function (x, bw = TRUE, ...) {
 
     }
 
-    if (x$n_peaks == 3) {
+    if (x$n_curves == 3) {
 
       y1 <- fs_mixture(temp = temp,
                        height_1 = params['height_1',], skew_1 = params['skew_1',],
@@ -97,7 +97,7 @@ plot.decon <- function (x, bw = TRUE, ...) {
 
   if(!isTRUE(bw)) {
 
-    if (x$n_peaks == 4) {
+    if (x$n_curves == 4) {
       y1 <- fs_mixture(temp = temp,
                        height_1 = params['height_1',], skew_1 = params['skew_1',],
                        position_1 = params['position_1',], width_1 = params['width_1',],
@@ -126,7 +126,7 @@ plot.decon <- function (x, bw = TRUE, ...) {
 
     }
 
-    if (x$n_peaks == 3) {
+    if (x$n_curves == 3) {
 
       y1 <- fs_mixture(temp = temp,
                        height_1 = params['height_1',], skew_1 = params['skew_1',],

### 2018-08-01 logo/logo.R

@@ -1,4 +1,4 @@
-png('hex_bg.png', width = 1500, height = 1500, bg = 'transparent')
+png('logo/hex_bg.png', width = 1500, height = 1500, bg = 'transparent')
 hexd <- data.frame(x = 1 + c(rep(-sqrt(3)/2, 2), 0, rep(sqrt(3)/2, 2), 0),
                    y = 1 + c(0.5, -0.5, -1, -0.5, 0.5, 1))
 hexd <- rbind(hexd, hexd[1, ])
@@ -19,14 +19,11 @@ segments(x0 = hexd$x[5] - .03,
          y0 = hexd$y[5] - .02,
          x1 = hexd$x[6],
          y1 = hexd$y[6] - .033, lwd = 13, col = '#000000')
-img <- png::readPNG("mixchar_logo.png")
+img <- png::readPNG("logo/mixchar_logo.png")
 rasterImage(img, .4, .4, 1.6, 1.6)
 dev.off()
 
-hexSticker::sticker('hex_bg.png', s_x = .985, s_y = .99, s_width = 1.1,
+hexSticker::sticker('logo/hex_bg.png', s_x = .985, s_y = .99, s_width = 1.1,
         package = '', h_color = '#000000', h_fill = '#ededed',
-        filename = "hexsticker.png")
-
-
-
+        filename = "logo/hexsticker.png")
 

### 2018-08-01 README.Rmd
fix build issue! move manuscript and logo folder to buildignore

@@
 ---
-output: github_document
+title: "mixchar"
+output:
+  md_document:
+    variant: markdown_github
 ---
@@
   comment = "#>",
-  fig.path = "man/figures/README-",
   out.width = "100%"
 )
+```
+
+```{r top_banner, echo=FALSE, fig.height=3, fig.width=4}
+knitr::include_graphics('logo/mixchar_logo.png')
 ```

### 2018-08-01 R/plot.decon.R
add bw argument to yaml plot.decon

@@ -4,6 +4,7 @@
 #' for outputs from deconvolve function
 #'
 #' @param x decon object as generated by deconvolve
+#' @param bw logical argument indicating whether the plot should be in black and white or colour
 #' @param ... other options passed to plot
 #' @return plot
 #' @method plot decon

### 2018-08-01 logo/logo.R
add banner!

@@ -27,3 +27,33 @@ hexSticker::sticker('logo/hex_bg.png', s_x = .985, s_y = .99, s_width = 1.1,
         package = '', h_color = '#000000', h_fill = '#ededed',
         filename = "logo/hexsticker.png")
 
+
+
+png('logo/hex_bg2.png', width = 1500, height = 1500, bg = 'transparent')
+hexd <- data.frame(x = 1 + c(rep(-sqrt(3)/2, 2), 0, rep(sqrt(3)/2, 2), 0),
+                   y = 1 + c(0.5, -0.5, -1, -0.5, 0.5, 1))
+hexd <- rbind(hexd, hexd[1, ])
+x_lim <- range(hexd$x)
+y_lim <- range(hexd$y)
+plot.new()
+plot.window(x_lim, y_lim)
+polygon(hexd, col = "#ededed", border = NA)
+segments(x0 = hexd$x[1] + .03,
+         y0 = hexd$y[1] - .03,
+         x1 = hexd$x[2] + .03,
+         y1 = hexd$y[2] + .03, lwd = 16, col = '#000000')
+segments(x0 = hexd$x[3],
+         y0 = hexd$y[3] + .033,
+         x1 = hexd$x[4] - .03,
+         y1 = hexd$y[4] + .02, lwd = 13, col = '#000000')
+segments(x0 = hexd$x[5] - .03,
+         y0 = hexd$y[5] - .02,
+         x1 = hexd$x[6],
+         y1 = hexd$y[6] - .033, lwd = 13, col = '#000000')
+img <- png::readPNG("logo/mixchar_bg2.png")
+rasterImage(img, .4, .5, 1.6, 1.3)
+dev.off()
+
+hexSticker::sticker('logo/hex_bg2.png', s_x = .985, s_y = .99, s_width = 1.1,
+                    package = '', h_color = '#000000', h_fill = '#ededed',
+                    filename = "logo/hexsticker_banner.png")

### 2018-08-01 README.Rmd
modify logo size
add banner!
resize banner

@@
 
+<img src = "logo/mixchar_banner.png" height="350" width="350" />
+
 ```{r setup, include = FALSE}
@@
   collapse = TRUE,
-  comment = "#>",
-  out.width = "100%"
+  comment = "#>"
 )
-```
-
-```{r top_banner, echo=FALSE, fig.height=3, fig.width=4}
-knitr::include_graphics('logo/mixchar_logo.png')
 ```

### 2018-08-02 design/hexsticker.R
logo and imagery to different folder structure

@@ -1,0 +1,59 @@
+## mixchar with three carbons hexsticker
+png('logo/hex_bg.png', width = 1500, height = 1500, bg = 'transparent')
+hexd <- data.frame(x = 1 + c(rep(-sqrt(3)/2, 2), 0, rep(sqrt(3)/2, 2), 0),
+                   y = 1 + c(0.5, -0.5, -1, -0.5, 0.5, 1))
+hexd <- rbind(hexd, hexd[1, ])
+x_lim <- range(hexd$x)
+y_lim <- range(hexd$y)
+plot.new()
+plot.window(x_lim, y_lim)
+polygon(hexd, col = "#ededed", border = NA)
+segments(x0 = hexd$x[1] + .03,
+         y0 = hexd$y[1] - .03,
+         x1 = hexd$x[2] + .03,
+         y1 = hexd$y[2] + .03, lwd = 16, col = '#000000')
+segments(x0 = hexd$x[3],
+         y0 = hexd$y[3] + .033,
+         x1 = hexd$x[4] - .03,
+         y1 = hexd$y[4] + .02, lwd = 13, col = '#000000')
+segments(x0 = hexd$x[5] - .03,
+         y0 = hexd$y[5] - .02,
+         x1 = hexd$x[6],
+         y1 = hexd$y[6] - .033, lwd = 13, col = '#000000')
+img <- png::readPNG("logo/mixchar_hex.png")
+rasterImage(img, .3, .5, 1.7, 1.3)
+dev.off()
+
+hexSticker::sticker('logo/hex_bg.png', s_x = .985, s_y = .99, s_width = 1.1,
+                    package = '', h_color = '#000000', h_fill = '#ededed',
+                    filename = "logo/hexsticker.png")
+
+## slanted mix char hex sticker
+# png('logo/hex_bg.png', width = 1500, height = 1500, bg = 'transparent')
+# hexd <- data.frame(x = 1 + c(rep(-sqrt(3)/2, 2), 0, rep(sqrt(3)/2, 2), 0),
+#                    y = 1 + c(0.5, -0.5, -1, -0.5, 0.5, 1))
+# hexd <- rbind(hexd, hexd[1, ])
+# x_lim <- range(hexd$x)
+# y_lim <- range(hexd$y)
+# plot.new()
+# plot.window(x_lim, y_lim)
+# polygon(hexd, col = "#ededed", border = NA)
+# segments(x0 = hexd$x[1] + .03,
[…]

### 2018-08-02 logo/logo.R

@@ -1,59 +1,0 @@
-png('logo/hex_bg.png', width = 1500, height = 1500, bg = 'transparent')
-hexd <- data.frame(x = 1 + c(rep(-sqrt(3)/2, 2), 0, rep(sqrt(3)/2, 2), 0),
-                   y = 1 + c(0.5, -0.5, -1, -0.5, 0.5, 1))
-hexd <- rbind(hexd, hexd[1, ])
-x_lim <- range(hexd$x)
-y_lim <- range(hexd$y)
-plot.new()
-plot.window(x_lim, y_lim)
-polygon(hexd, col = "#ededed", border = NA)
-segments(x0 = hexd$x[1] + .03,
-         y0 = hexd$y[1] - .03,
-         x1 = hexd$x[2] + .03,
-         y1 = hexd$y[2] + .03, lwd = 16, col = '#000000')
-segments(x0 = hexd$x[3],
-         y0 = hexd$y[3] + .033,
-         x1 = hexd$x[4] - .03,
-         y1 = hexd$y[4] + .02, lwd = 13, col = '#000000')
-segments(x0 = hexd$x[5] - .03,
-         y0 = hexd$y[5] - .02,
-         x1 = hexd$x[6],
-         y1 = hexd$y[6] - .033, lwd = 13, col = '#000000')
-img <- png::readPNG("logo/mixchar_logo.png")
-rasterImage(img, .4, .4, 1.6, 1.6)
-dev.off()
-
-hexSticker::sticker('logo/hex_bg.png', s_x = .985, s_y = .99, s_width = 1.1,
-        package = '', h_color = '#000000', h_fill = '#ededed',
-        filename = "logo/hexsticker.png")
-
-
-
-png('logo/hex_horizontal.png', width = 1500, height = 1500, bg = 'transparent')
-hexd <- data.frame(x = 1 + c(rep(-sqrt(3)/2, 2), 0, rep(sqrt(3)/2, 2), 0),
-                   y = 1 + c(0.5, -0.5, -1, -0.5, 0.5, 1))
-hexd <- rbind(hexd, hexd[1, ])
-x_lim <- range(hexd$x)
-y_lim <- range(hexd$y)
-plot.new()
-plot.window(x_lim, y_lim)
-polygon(hexd, col = "#ededed", border = NA)
-segments(x0 = hexd$x[1] + .03,
-         y0 = hexd$y[1] - .03,
-         x1 = hexd$x[2] + .03,
[…]

### 2018-08-02 tests/testthat/test-component_weights.R
revise test with changes to fs_function and parameter names

@@ -1,12 +1,12 @@
 context("Test for extracting weights of components")
 
-test_that("wt_component returns correct weight", {
+test_that("correct weights returned", {
 
-  params3 <- c(h1 = .1, s1 = .3, p1 = 200, w1 = 100,
-               h2 = .2, s2 = .25, p2 = 400, w2 = 60,
-               h3 = .15, s3 = .26, p3 = 600, w3 = 200)
+  params3 <- c(height_1 = .1, skew_1 = .3, position_1 = 200, width_1 = 100,
+               height_2 = .2, skew_2 = .25, position_2 = 400, width_2 = 60,
+               height_3 = .15, skew_3 = .26, position_3 = 600, width_3 = 200)
 
-  param_vec <- c(.1, .3, 200, 100)
+  param_vec <- c(params3[[1]], params3[[2]], params3[[3]], params3[[4]])
   lower <- 120
   upper <- 700
 
@@ -21,22 +21,15 @@ test_that("wt_component returns correct weight", {
 
   expect_equal(wt_component(1, params3, lower, upper), val, tolerance = 1e-3)
 
-})
+  params4 <- c(height_1 = .1, skew_1 = .3, position_1 = 200, width_1 = 100,
+               height_2 = .2, skew_2 = .25, position_2 = 400, width_2 = 60,
+               height_3 = .15, skew_3 = .26, position_3 = 600, width_3 = 200,
+               height_0 = .08, skew_0 = .22, position_0 = 180, width_0 = 150)
 
-test_that("get_weights returns correct weight values for each component", {
+  output3 <- list(n_curves = 3, bounds = c(120, 700))
+  output4 <- list(n_curves = 4, bounds = c(120, 700))
 
-  params3 <- c(h1 = .1, s1 = .3, p1 = 200, w1 = 100,
-               h2 = .2, s2 = .25, p2 = 400, w2 = 60,
-               h3 = .15, s3 = .26, p3 = 600, w3 = 200)
-  params4 <- c(h1 = .1, s1 = .3, p1 = 200, w1 = 100,
-               h2 = .2, s2 = .25, p2 = 400, w2 = 60,
-               h3 = .15, s3 = .26, p3 = 600, w3 = 200,
-               h0 = .08, s0 = .22, p0 = 180, w0 = 150)
-
-  output3 <- list(n_peaks = 3, bounds = c(120, 700))
[…]

### 2018-08-02 manuscript/manuscript.Rnw
add extra manuscript documents to gitignore

@@
 <<echo = FALSE>>=
-opts_chunk$set(size = 'footnotesize',
+knitr::opts_chunk$set(size = 'footnotesize',
                       fig.pos = 'H',
@@
 <<echo = FALSE, fig.cap = '\\label{Fig:process} Process function output from \\textit{Juncus amabilis} example dataset.', fig.subcap = c('\\label{Fig:massloss} Thermogravimetric mass loss curve.', '\\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample.'), out.width = '.49\\linewidth', fig.asp = 1, fig.ncol = 2>>=
+par(mar = c(5, 5, 2, 1))
 plot(deriv_juncus, plot_type = 'mass')
+par(mar = c(5, 5, 2, 1))
 plot(deriv_juncus, plot_type = 'rate')
@@
 
-<<echo = FALSE, fig.cap = '\\label{Fig:fs_simulation} Parametric examination of Fraser-Suzuki function using simulated data', out.width = '.9\\linewidth', fig.asp = 1>>=
+<<echo = FALSE, fig.cap = '\\label{Fig:fs_simulation} Parametric study of the Fraser-Suzuki function for deconvolution of derivative thermogravimetric biomass curves: (a) Effect of modifying height; (b) skew; (c) position; and (d) width.', out.width = '\\linewidth', fig.asp = 1>>=
+legend_subfig <- function (subfig) {
+  legend(200, .01, legend = paste0('(', subfig, ')'), bty = 'n', cex = 1.2)
+}
+
 simulate_fraser_suzuki <- function () {
@@
 
-  par(oma = c(5, 5, 0, 2), mar = c(1, 3, 2, 0), mfrow = c(2, 2))
+  par(oma = c(4, 3, 0, 1), mar = c(1, 2, 1, 0), mfrow = c(2, 2))
 
@@
        ylab = '')
-  axis(side = 2, at = c(0, 0.002, 0.004, 0.006, 0.008, 0.010), cex.axis = 1.2,
-       labels = c(0, 0.002, 0.004, 0.006, 0.008, 0.010))
+  axis(side = 2, at = c(0, 0.005, 0.010), cex.axis = 1.2,
+       labels = c(0, 0.005, 0.010))
   lines(x, h2, lty = 2)
@@
   lines(x, h1, lty = 1)
-  legend('topleft', legend = '(a)', bty = 'n', cex = 1.6)
+  legend_subfig('a')
   legend('topright', legend = c(expression(paste('h = 0.004 C'^'-1')),
@@
                                 'w = 60 C'),
-         bty = 'n', cex = 1.2,
+         bty = 'n', cex = 0.8,
          lty = c(1, 2, 3, 4, NA, NA, NA)
@@
   lines(x, s4, lty = 4)
-  legend('topleft', legend = '(b)', bty = 'n', cex = 1.6)
+  legend_subfig('b')
   legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
@@
                                 'w = 60 C'),
-         bty = 'n', cex = 1.2,
+         bty = 'n', cex = 0.8,
          lty = c(NA, 1, 2, 3, 4, NA, NA)
@@
        ylab = '')
-  axis(side = 1, at = c(200, 300, 400, 500, 600, 700), cex.axis = 1.2,
-       labels = c(200, 300, 400, 500, 600, 700))
-  axis(side = 2, at = c(0, 0.002, 0.004, 0.006, 0.008, 0.010), cex.axis = 1.2,
-       labels = c(0, 0.002, 0.004, 0.006, 0.008, 0.010))
+  axis(side = 1, at = c(200, 325, 450, 575, 700), cex.axis = 1.2,
+       labels = c(200, 325, 450, 575, 700))
+  axis(side = 2, at = c(0, 0.005, 0.010), cex.axis = 1.2,
+       labels = c(0, 0.005, 0.010))
   lines(x, p2, lty = 2)
@@
   lines(x, p4, lty = 4)
-  legend('topleft', legend = '(c)', bty = 'n', cex = 1.6)
+  legend_subfig('c')
   legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
@@
                                 'w = 60 C'),
-         bty = 'n', cex = 1.2,
+         bty = 'n', cex = 0.8,
          lty = c(NA, NA, 1, 2, 3, 4, NA)
@@
        ylab = '')
-  axis(side = 1, at = c(200, 300, 400, 500, 600, 700), cex.axis = 1.2,
-       labels = c(200, 300, 400, 500, 600, 700))
+  axis(side = 1, at = c(200, 325, 450, 575, 700), cex.axis = 1.2,
+       labels = c(200, 325, 450, 575, 700))
   lines(x, w2, lty = 2)
@@
   lines(x, w4, lty = 4)
-  legend('topleft', legend = '(d)', bty = 'n', cex = 1.6)
+  legend_subfig('d')
   legend('topright', legend = c(expression(paste('h = 0.010 C'^'-1')),
@@
                                 'w = 120'),
-         bty = 'n', cex = 1.2,
+         bty = 'n', cex = 0.8,
          lty = c(NA, NA, NA, 1, 2, 3, 4))
@@
         outer = TRUE,
-        cex = 1.8)
+        cex = 1.3)
   mtext(text = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
@@
         outer = TRUE,
-        cex = 1.8)
+        cex = 1.3)
 }
@@
 This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components curves.
+The default plot is in black and white, but you can plot a colour version using colour-blind friendly \verb|viridis| colours by specifying \verb|bw = FALSE|.
 
-<<fig.cap = '\\label{Fig:decon} Deconvolution of \textit{Juncus amabilis} example dataset. Mass loss data overlaid with output of deconvolution. Rate of mass loss scaled by initial mass of sample.'>>=
-plot(output_juncus)
+<<fig.cap = '\\label{Fig:decon} Deconvolution of \\textit{Juncus amabilis} example dataset.
+Mass loss data overlaid with output of deconvolution.
+Rate of mass loss scaled by initial mass of sample.', out.width = '0.7\\linewidth', asp = 1, fig.align = 'center'>>=
+par(mar = c(5,5,1,1))
+plot(output_juncus, bw = FALSE)
 @

### 2018-08-02 R/plot.decon.R
plot plot formatting

@@ -20,13 +20,10 @@ plot.decon <- function (x, bw = TRUE, ...) {
 
   params <- as.data.frame(summary(fit)$coefficients[,1])
 
-  par(xpd = TRUE, mar = par()$mar + c(0, 1, 0, 0))
-
   plot(data$temp_C, data$deriv, xlab = 'Temperature (C)',
        ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
        yaxs = 'i', ylim = c(0, max(data$deriv) + 0.06*max(data$deriv)),
-       pch = 20, cex = 0.3, cex.axis = 1.2)
-
+       pch = 20, cex = 0.5, cex.axis = 1.2, cex.lab = 1.5)
 
   if (isTRUE(bw)) {
 
@@ -49,11 +46,11 @@ plot.decon <- function (x, bw = TRUE, ...) {
       legend('topright',
              legend = c('DTG data', 'DTG modelled', 'Hemicellulose 1', 'Hemicellulose 2', 'Cellulose', 'Lignin'),
              ncol = 1,
-             cex = 2.2,
+             cex = 1.2,
              bty = 'n',
              lty = c(NA, 1, 6, 3, 4, 5),
              pch = c(20, NA, NA, NA, NA, NA),
-             lwd = 3.5)
+             lwd = 2)
 
     }
 
@@ -70,11 +67,10 @@ plot.decon <- function (x, bw = TRUE, ...) {
       legend('topright',
              legend = c('DTG data', 'DTG modelled', 'Hemicellulose', 'Cellulose', 'Lignin'),
              ncol = 1,
-             cex = 2.2,
+             cex = 1.2,
              bty = 'n',
              lty = c(NA, 1, 3, 4, 5),
              pch = c(20, NA, NA, NA, NA),
-             col = c('black', 'black', '#440154FF', '#B8DE29FF', '#3CBB75FF'),
              lwd = 2)
 
     }
@@ -118,12 +114,12 @@ plot.decon <- function (x, bw = TRUE, ...) {
       legend('topright',
              legend = c('DTG data', 'DTG modelled', 'Hemicellulose 1', 'Hemicellulose 2', 'Cellulose', 'Lignin'),
              ncol = 1,
-             cex = 2.2,
+             cex = 1.2,
              bty = 'n',
              lty = c(NA, 1, 6, 3, 4, 5),
              pch = c(20, NA, NA, NA, NA, NA),
[…]

### 2018-08-02 R/plot.process.R

@@ -18,13 +18,29 @@ plot.process <- function (x, plot_type = NULL, ...) {
 
   p_massloss <- function (data) {
     plot(data$temp_C, data$mass_T, xlab = 'Temperature (C)',
-         ylab = 'Mass remaining (mg)', pch = 20, cex = 0.7)
+         ylim = c(0, max(data$mass_T) + 0.5),
+         yaxt = 'n',
+         xaxt = 'n',
+         ylab = 'Mass remaining (mg)', pch = 20, cex = 0.7,
+         cex.lab = 2)
+    axis(side = 1, at = c(100, 300, 500, 700), cex.axis = 1.8,
+         labels = c(100, 300, 500, 700))
+    top_y <- round(max(data$mass_T), 0)
+    mid_y <- top_y/2
+    axis(side = 2, at = c(0, mid_y, top_y), cex.axis = 1.8,
+         labels = c(0, mid_y, top_y))
   }
 
   p_dtg <- function (data) {
-    plot(data$temp_C, data$deriv, xlab = 'Temperature (C)',
+    plot(data$temp_C, data$deriv, xlab = 'Temperature (C)', ylim = c(0, max(data$deriv) + .0002),
          ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
-         pch = 20, cex = 0.7)
+         pch = 20, cex = 0.7, cex.lab = 2, yaxt = 'n', xaxt = 'n')
+    axis(side = 1, at = c(100, 300, 500, 700), cex.axis = 1.8,
+         labels = c(100, 300, 500, 700))
+    top_y <- round(max(data$deriv), 3)
+    mid_y <- top_y/2
+    axis(side = 2, at = c(0, mid_y, top_y), cex.axis = 1.8,
+         labels = c(0, mid_y, top_y))
   }
 
   if (!is.null(plot_type) & isTRUE(plot_type == 'mass')) {

### 2018-08-02 R/weight_quantiles.R
fix typo -- assure parameter names are correctly specified

@@ -99,7 +99,7 @@ get_weights <- function (param_vec, output) {
 wt_component <- function (j, param_vec, lower_temp, upper_temp) {
 
   # extract relevant parameter vector
-  names <- paste0(c("height_", "skew_", "position", "width"), j)
+  names <- paste0(c("height_", "skew_", "position_", "width_"), j)
 
   idx <- match(names, names(param_vec))
   param_sub <- param_vec[idx]
@@ -115,3 +115,4 @@ wt_component <- function (j, param_vec, lower_temp, upper_temp) {
 
   wt
 }
+

### 2018-08-02 test-print_plot.R
remove cached files

@@ -1,4 +1,4 @@
-Context("Test print and plot functions")
+context("Test print and plot functions")
 
 test_that("print functions produce correct output", {
 
@@ -11,7 +11,6 @@ test_that("print functions produce correct output", {
 
   expect_identical(tmp, pro_output)
   expect_identical(output, out_output)
-
 
   vdiffr::expect_doppelganger("process plot", plot(tmp))
   vdiffr::expect_doppelganger("deconvolve plot", plot(out_output))

### 2018-08-02 tests/testthat/test-deconvolve.R

@@ -1,5 +1,0 @@
-context("test-deconvolve.R")
-
-test_that("multiplication works", {
-  expect_equal(2 * 2, 4)
-})

### 2018-08-02 tests/testthat/test-optimisation.R

@@ -1,0 +1,11 @@
+context("Test for non-linear optimisation")
+
+test_that("param_select function produces the same results with random seed set", {
+
+
+
+
+
+
+
+})

### 2018-08-03 README.Rmd
test resize
aesthetic reformatting
remove cached files
revised manuscript

@@
 ---
-
-<img src = "logo/mixchar_banner.png" height="350" width="350" />
 
@@
 
+# <img src = "man/figures/logo.png" height="80" width="350" />
+
 [![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
@@
 ## Why deconvolution?
+four-curve vignette
+create your own plot vignette
 
-Ecologists are often interested in determining the composition of plant cell wall biomass, primarily hemicellulose, cellulose, and lignin carbon types.
+Ecologists are often interested in determining the composition of plant cell wall biomass, compoased primarily of hemicellulose, cellulose, and lignin carbons.
 Proportions of these carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.

### 2018-08-03 manuscript/manuscript.Rnw
revised manuscript

@@
 \usepackage{pgfplots}
+\pgfplotsset{compat=1.16}
 \pgfplotsset{width=16cm}
@@
 \section*{Paper Authors}
-1. Windecker, Saras Mei \\
-2. Vesk, Peter Anton \\
-3. Golding, Nick.
+1. Windecker, Saras M. \\
+2. Vesk, Peter A. \\
+3. Catford, Jane A. \\
+4. Golding, Nick.
 
@@
 2. Associate Professor, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
-3. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia
+3. Assistant Professor, Biological Sciences, University of Southampton, Highfield Campus, Southampton SO17 1BJ, UK \\
+4. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia
 
 \section*{Abstract}
-This package provides way to quantify proportions of lignocellulosic biomass components (typically considered hemicellulose, cellulose, and lignin) from the mass loss data generated during thermogravimetric analysis (TGA).
 
-Proportions of the main carbon types in litter can be used as functional traits to understand ecosystem processes such as litter decomposition, or to aid in calculation of kinetic decay constants.
-Thermogravimetric analysis is the process of pyrolysing dry, ground plant litter, and results in mass loss data across a temperature range.
-Since different carbon types break down during different temperature phases, we can separate the multi-peaked rate of mass loss curve into independent decay phases and estimate proportions of each carbon type by integrating under their respective individual decay curve.
-This package conducts this analysis in an open-source and reproducible fashion.
+Ecologists are often interested in determining the composition of plant cell wall biomass.
+Proportions of the primary carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.
+Traditional methods for calculation of these components involve wet chemistry methods that can be monetarily and environmentally costly.
+Thermogravimetric analysis is an alternative method, already in use in the biofuel field, that involves pyrolysing dry, ground plant litter and estimating components from resulting mass decay peaks.
+Since different carbon types break down relatively independently during different temperature phases, we can separate the multi-peaked rate of mass loss curve into constituent parts using a mixture model.
+This package conducts this peak separation analysis in a open-source and reproducible way using R.
+This methodology has been tested on a range of plant litter composed primarily of soluble carbohydrates, hemicellulose, cellulose, and lignin.
 
 \section*{Keywords}
-thermogravimetric analysis; deconvolution; decay; Fraser-Suzuki; R package; plant traits
+thermogravimetric analysis; deconvolution; decay; Fraser-Suzuki; R package; plant traits; kinetics; biofuel
 
@@
 Plant cell wall biomass is composed of a range of different types of carbon.
-Ecologists can use these proportions of biomass carbon as functional traits, enabling us to make generalisations about species' effects on ecosystem processes such as litter decomposition, which links plant biomass to the global carbon cycle \citep{cornwell2008}.
+Ecologists can use these proportions of biomass carbon to make generalisations about species' effects on ecosystem processes such as litter decomposition, which links plant biomass to the global carbon cycle \citep{cornwell2008}.
 Biofuels researchers use proportions of biomass carbon types to estimate kinetic decay parameters of species' tissue.
-Traditional methods for calculation of lignocellulosic biomass involve wet chemistry assays for carbon component analysis are time-consuming and adversely impact the environment through use of sulfuric acid and acetic anhydride, among other chemicals.
+Traditional methods for calculation of lignocellulosic biomass involve wet chemistry assays for carbon component analysis, which are time-consuming and adversely impact the environment through use of sulfuric acid and acetic anhydride, among other chemicals.
 Thermogravimetric analysis (TGA) is an alternative method, already in use among biofuels researchers, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in a $N_2$ environment, termed pyrolysis).
@@
 Mass loss during pyrolysis can be regarded as the sum of the degradation of the main components of the sample \textemdash hemicelluloses, cellulose, and lignin \citep{hu2016,cheng2015,perejon2011,orfao2001,muller-hagedorn2007}.
-Therefore, the multi-peaked rate of mass loss curve (derivative of mass loss curve) can be mathematically separated, or deconvolved, with a mixture model into individual peaks \textemdash each representing a single primary component.
+Therefore, the multi-peaked rate of mass loss curve can be mathematically separated into constituent parts with a mixture model \textemdash termed deconvolution.
+By integrating under these individual curves, we can estimate the contribution of each component to the overall initial sample.
 This method has been validated by studies comparing estimates to experimental measurements \citep{yang2006}.
 Plant trait measurement is guided by the principle of standardised, widely reproducible methods \citep{perez-harguindeguy2013}, but much of the published literature use commercial software to deconvolve the rate of mass loss curve \citetext{for example OriginPro \citealp{chen2017}, PeakFit \citealp{perejon2011}, Fityk \citealp{perejon2011}, or Datafit \citealp{cheng2015}}.
-Software accessibility and reproducibility may be one reason why thermogravimetric analysis has not yet been widely adopted by functional ecologists, despite being previously used to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucaplyts \citealp{orfao2001}}.
+Software accessibility and reproducibility may be one reason why thermogravimetric analysis for carbon type estimation has not yet been widely adopted by functional ecologists, despite being previously used to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucaplyts \citealp{orfao2001}}.
+In addition, proprietary software inhibits researchers already conducting this type of analysis from making their analyses independently reproducible.
 \\
@@
 The \verb|mixchar| package provides an open-source set of functions to perform this deconvolution.
-Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, \verb|mixchar| aims to provide context specific guidelines related to use of this model for thermal decay curve analysis and carbon component estimation, in order to maximise its utility and ease of uptake for researchers interested in this method.
+Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, \verb|mixchar| provides specific guidelines related to thermal decay curve analysis and carbon component estimation.
+Detailed vignettes and several default plotting options are included in order to maximise utility and ease of uptake for researchers interested in this method.
 
@@
 We dried the fresh litter at 60 $^{\circ}$C for 72 hours and ground litter to \textless $40 \mu m$ using a Retsch Centrifugal Mill ZM200.
-We used 10\textendash20 mg subsamles of dry, ground litter for thermogravimetric analysis (TGA).
-Each sample was pyrolysed in an N$_2$ environment from 30\textendash800 $^{\circ}$C at a temperature ramp of 10 $^{\circ}$C/min using a Netzsch TGA-FTIR thermogravimetric analyser (Department of Biomedical Engineering, University of Melbourne).
+We pyrolysed 10\textendash20 mg subsamles of dry, ground litter in an N$_2$ environment from 30\textendash800 $^{\circ}$C at a temperature ramp of 10 $^{\circ}$C/min using a Netzsch TGA-FTIR thermogravimetric analyser (Department of Biomedical Engineering, University of Melbourne).
 The resulting data is mass loss in grams against temperature (Fig.~\ref{Fig:massloss}).
@@
 Once we have calculated the rate of mass loss, we use the \verb|deconvolve| function to estimate the proportions of carbon components.
-Under the hood, it does so with a series of steps that are described in detail below.
-First it crops the derivative rate of mass loss data, then estimates parameter values from the non-linear model, and finally integrates under each resulting curve to estimate weight proportions of primary components.
+Under the hood, it does so with a series of steps: it crops the derivative rate of mass loss data, estimates parameter values from the non-linear model, and finally integrates under each resulting curve to estimate weight proportions of primary components.
 We explain these steps in detail below.
@@
 \\
-Although most of our results can be described with only $n = 3$ peaks, corresponding to a single curve each of hemicelluose, cellulose, and lignin, some species yield a second hemicellulose peak at a lower temperature, resulting in $n = 4$ independent curves This is because the soluble carbohydrates in plant tissue can take many forms, including xylan, amylose, etc., which apparently degrade at different temperatures \citep[see also][]{chen2017,muller-hagedorn2007}.
+Although most of our results can be described with only $n = 3$ peaks, corresponding to a single curve each of hemicelluose, cellulose, and lignin, some species yield a second hemicellulose peak at a lower temperature, resulting in $n = 4$ independent curves.
+This is because the soluble carbohydrates in plant tissue can take many forms, including xylan, amylose, etc., which apparently degrade at different temperatures \citep[see also][]{chen2017,muller-hagedorn2007}.
 \verb|deconvolve| will decide whether three or four curves are best using an internal function that determines if there is a peak below 220 $^{\circ}$C.
@@
 Lignin typically decays beginning at a high temperature and over a wide interval \citep{chen2015}, so position and width began at 410 and 200, respectively.
-If necessary, these starting values can also be modified in the \verb|deconvolve| function with the \verb|start_vec|, \verb|lower_vec|, and \verb|upper_vec| arguments.
+These starting values can also be modified in the \verb|deconvolve| function with the \verb|start_vec|, \verb|lower_vec|, and \verb|upper_vec| arguments.
 These initial starting values are optimised before model fitting using the \verb|NLOPTR_LN_BOBYQA| algorithm \citep{bobyqa} within the \verb|nloptr| \citep{nloptr} package.
@@
 \textit{Component weights}\\
-Once overall curve parameters are fit, we can use the pass each components's paremeter estimates to a single Fraser-Suzuki function, and calculate the weight of the component in the overall sample by integrating under the curve (Eq.~\ref{eqn:integration}).
-To estimate the uncertainty of the weight predictions we calculated the 95\% interval of the weight estimates across a random sample of parameter estimates, drawn in proportion to their likelihood.
-We assumed a truncated multivariate normal distribution, since the parameters are constrained to positive values, using the modelling package \verb|tmvtnorm| \citep{tmvtnorm}.
+Once overall curve parameters are fit, we can pass each components's parameter estimates to a single Fraser-Suzuki function, and calculate the weight of the component in the overall sample by integrating under the curve (Eq.~\ref{eqn:integration}).
+To estimate the uncertainty of the weight predictions, \verb|deconvolve| will calculate the 95\% interval of the weight estimates across a random sample of parameter estimates, drawn in proportion to their likelihood.
+We assume a truncated multivariate normal distribution, since the parameters are constrained to positive values, using the modelling package \verb|tmvtnorm| \citep{tmvtnorm}.
 
@@
 This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components curves.
-The default plot is in black and white, but you can plot a colour version using colour-blind friendly \verb|viridis| colours by specifying \verb|bw = FALSE|.
+The default plot is in black and white, but you can plot a colour version that uses colour-blind friendly \verb|viridis| colours \citep{viridis} by specifying \verb|bw = FALSE|.
 
@@
 
-All analyses were conducted within the statistical computing environment, R \citep{R}, and data and R code for this paper are available on the package Github (\url{https://github.com/smwindecker/mixchar/}.
-In order to aid in the reproducibility of this work, our code was written using a \verb|remake| framework \citep{remake}.
-This allows others to readily reproduce our work by calling \verb|remake()| in R.
-
-This work is the first attempt to use thermogravimetric analysis (TGA) with a mixture model to estimate the partitioning of carbon in a suite of wetland plants.
+The Fraser-Suzuki family of functions are exported to allow users to create their own plots from the model outputs. Detailed descriptions of how to do so are included in the package vignettes.
 
@@
 All the functions of \verb|mixchar| were tested to see if they produced the desired output.
-?...
-The structure of the package successfully passed the \verb|CRAN R CMD| check and the results from this check can be found on CRAN.
 
@@
 \section*{Dependencies}
-R packages: \verb|graphics|, \verb|minpack.lm|, \verb|nloptr|, \verb|stats|, \verb|tmvtnorm|, \verb|zoo|.
+R packages: \verb|minpack.lm|, \verb|nloptr|, \verb|tmvtnorm|, \verb|zoo|.
 
@@
 \section*{(3) Reuse potential}
-This should include the use cases for the software,
-
-The Fraser-Suzuki family of functions are exported to allow the user to create their own plots from the model outputs. Detailed descriptions of how to do so are included in the package vignettes.
-
 This package was designed with both the user and developer in mind.
 There are several vignettes available with the package and on the package website (\url{https://smwindecker.github.io/mixchar/}) facilitating exploration of package functionality.
-For those that wish to contribute to the package, it is hosted on Github, and they can log issues via the issues tracker (\url{https://github.com/smwindecker/mixchar/issues}) or submit a pull request to add functionality to the package.
+We expect that this package will be useful to researchers already using thermogravimetric analysis for carbon component estimation, as well as to functional ecologists seeking to test out this approach as an alternative to wet chemistry methods.
+For all users, this method provides a significant improvement on most current softwares available, as it allows fully open-source and transparent analyses.
+
+For those that wish to contribute to the package, it is hosted on Github.
+Contributors can log issues via the issues tracker (\url{https://github.com/smwindecker/mixchar/issues}) or submit a pull request to add functionality to the package.
 

### 2018-08-03 manuscript/manuscript.Rnw
Add authors

@@
 2. Vesk, Peter A. \\
-3. Catford, Jane A. \\
+3. Trevathan-Tackett, Stacey M. \\
+4. Catford, Jane A. \\
+5. Macreadie, Peter I. \\
 4. Golding, Nick.
@@
 2. Associate Professor, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
-3. Assistant Professor, Biological Sciences, University of Southampton, Highfield Campus, Southampton SO17 1BJ, UK \\
-4. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia
+3. Research Fellow, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
+4. Assistant Professor, Biological Sciences, University of Southampton, Highfield Campus, Southampton SO17 1BJ, UK \\
+5. Associate Professor, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
+6. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia
 

### 2018-08-03 README.Rmd
revise introduction

@@
 ## Why deconvolution?
-four-curve vignette
-create your own plot vignette
 
-Ecologists are often interested in determining the composition of plant cell wall biomass, compoased primarily of hemicellulose, cellulose, and lignin carbons.
-Proportions of these carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.
+Ecologists are often interested in determining the composition of plant cell wall biomass.
+Proportions of the primary carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.
 Traditional methods for calculation of these components involve wet chemistry methods that can be monetarily and environmentally costly.
-Thermogravimetric analysis (TGA) is an alternative method, already used in the biofuel field, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in a $N_2$ environment, termed pyrolysis).
-
-To estimate carbon components from this mass loss data we have to take the derivative, to find the rate of mass loss across temperature, and then use a mixture model to separate the multi-peaked derivative curve into constituent parts.
-This process is called deconvolution, and is typically conducted in proprietary peak-fitting softwares, which, while effective, are not open source.
-This package seeks to provide a platform for reproducible deconvolution using R.
+Thermogravimetric analysis is an alternative method, already in use in the biofuel field, that involves pyrolysing dry, ground plant litter and estimating components from resulting mass decay peaks.
+Since different carbon types break down relatively independently during different temperature phases, we can separate the multi-peaked rate of mass loss curve into constituent parts using a mixture model.
+This package conducts this peak separation analysis in a open-source and reproducible way using R.
 This methodology has been tested on a range of plant litter composed primarily of soluble carbohydrates, hemicellulose, cellulose, and lignin.
-For more details (link paper here).
 
@@
 
-``` r
-# install.packages("devtools")
+``` {r, eval = FALSE}
+install.packages("devtools")
 devtools::install_github("smwindecker/mixchar", build_vignettes = TRUE)
 ```
+
 ## Basic use

### 2018-08-05 R/plot.decon.R
modify size options for plot functions

@@ -20,6 +20,7 @@ plot.decon <- function (x, bw = TRUE, ...) {
 
   params <- as.data.frame(summary(fit)$coefficients[,1])
 
+  par(mar = c(5, 5, 1, 1))
   plot(data$temp_C, data$deriv, xlab = 'Temperature (C)',
        ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
        yaxs = 'i', ylim = c(0, max(data$deriv) + 0.06*max(data$deriv)),

### 2018-08-05 R/plot.process.R

@@ -8,11 +8,11 @@
 #' @param ... other options passed to plot
 #' @return plot
 #' @method plot process
-#' @importFrom graphics legend lines par plot
+#' @importFrom graphics legend lines par plot axis
 #'
 #' @export
 
-plot.process <- function (x, plot_type = NULL, ...) {
+plot.process <- function (x, plot_type = NULL, cex = 1, ...) {
 
   df <- x$data
 
@@ -21,25 +21,25 @@ plot.process <- function (x, plot_type = NULL, ...) {
          ylim = c(0, max(data$mass_T) + 0.5),
          yaxt = 'n',
          xaxt = 'n',
-         ylab = 'Mass remaining (mg)', pch = 20, cex = 0.7,
-         cex.lab = 2)
-    axis(side = 1, at = c(100, 300, 500, 700), cex.axis = 1.8,
+         ylab = 'Mass remaining (mg)', pch = 20, cex = 0.7*cex,
+         cex.lab = 1.2*cex)
+    axis(side = 1, at = c(100, 300, 500, 700), cex.axis = cex,
          labels = c(100, 300, 500, 700))
     top_y <- round(max(data$mass_T), 0)
     mid_y <- top_y/2
-    axis(side = 2, at = c(0, mid_y, top_y), cex.axis = 1.8,
+    axis(side = 2, at = c(0, mid_y, top_y), cex.axis = cex,
          labels = c(0, mid_y, top_y))
   }
 
   p_dtg <- function (data) {
     plot(data$temp_C, data$deriv, xlab = 'Temperature (C)', ylim = c(0, max(data$deriv) + .0002),
          ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
-         pch = 20, cex = 0.7, cex.lab = 2, yaxt = 'n', xaxt = 'n')
-    axis(side = 1, at = c(100, 300, 500, 700), cex.axis = 1.8,
+         pch = 20, cex = 0.7*cex, cex.lab = 1.2*cex, yaxt = 'n', xaxt = 'n')
+    axis(side = 1, at = c(100, 300, 500, 700), cex.axis = cex,
          labels = c(100, 300, 500, 700))
     top_y <- round(max(data$deriv), 3)
     mid_y <- top_y/2
-    axis(side = 2, at = c(0, mid_y, top_y), cex.axis = 1.8,
+    axis(side = 2, at = c(0, mid_y, top_y), cex.axis = cex,
          labels = c(0, mid_y, top_y))
   }
 

### 2018-08-07 R/plot.process.R
add space around single plots

@@ -36,7 +36,7 @@ plot.process <- function (x, plot_type = NULL, cex = 1, ...) {
   p_dtg <- function (data) {
     plot(data$temp_C, data$deriv,
          xlab = 'Temperature (C)',
-         ylim = c(0, max(data$deriv) + .0002),
+         ylim = c(0, max(data$deriv) + .0003),
          ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
          pch = 20, cex = 0.7*cex,
          cex.lab = 1.2*cex,
@@ -51,9 +51,11 @@ plot.process <- function (x, plot_type = NULL, cex = 1, ...) {
   }
 
   if (!is.null(plot_type) & isTRUE(plot_type == 'mass')) {
+    par(mar = c(5, 5, 1, 1))
     p_massloss(df)
   }
   if (!is.null(plot_type) & isTRUE(plot_type == 'rate')) {
+    par(mar = c(5, 5, 1, 1))
     p_dtg(df)
   }
   if (is.null(plot_type)) {

### 2018-08-07 README.Rmd
correct pkgdown and add text to readme
update headers and add website links

@@
 
-## Why deconvolution?
+# Why deconvolution?
 
@@
 
-## Installation
+# Installation
 
@@
 
-## Basic use
+<hr>
+
+# Basic use
 
@@
 
-You can see the full worked example in the vignette, which you can access on the or in R:
+You can see the full worked example in the vignette, which you can access on the [website](http://smwindecker.github.io/mixchar) or in R:
 ```{r}
@@
 
+A detailed discussion of the methodology is also on the [website](http://smwindecker.github.io/Background).
+
 This is still a work in progress!
@@
 
-## Acknowledgements
+<hr>
+
+# Acknowledgements
 Thank you to Nick Tierney for valuable feedback during development. Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project.

### 2018-08-07 R/component_weights.R
wrap \dontrun to examples

@@ -4,11 +4,12 @@
 #' @return Extract mean fractions of the object
 #' @keywords thermogravimetry fraser-suzuki deconvolution
 #' @examples
+#' \dontrun{
 #' data(juncus)
 #' tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96, temp_type = 'C')
 #' output <- deconvolve(tmp)
 #' component_weights(output)
-#'
+#' }
 #' @export
 
 component_weights <- function (object) {

### 2018-08-07 R/model_fit.R

@@ -4,11 +4,12 @@
 #' @return $minpack.lm of the object
 #' @keywords thermogravimetry fraser-suzuki deconvolution
 #' @examples
+#' \dontrun{
 #' data(juncus)
 #' munge <- process(juncus, 'temp_C', 'mass_loss', 18.96, temp_type = 'C')
 #' output <- deconvolve(munge)
 #' model_fit(output)
-#'
+#' }
 #' @export
 
 model_fit <- function (object) {

### 2018-08-08 README.Rmd
remove `build_vignettes = TRUE` from install instructions, correct code with new process function

--- 2018-08-03 README.Rmd
@@
 install.packages("devtools")
-devtools::install_github("smwindecker/mixchar", build_vignettes = TRUE)
+devtools::install_github("smwindecker/mixchar")
 ```
 
-## Basic use
+<hr>
 
-Data from thermogravimetric analysis is usually exported as mass loss with temperature. An example dataset for the species *Juncus amabilis* is included in the package:
+Below we will show a basic implementation of the package.
+For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/Background).
+You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar) or in the vignette that you can access via R as follows:
+
+```{r, eval = FALSE}
+browseVignettes('mixchar')
+```
+
+# Basic use
+
+Data from thermogravimetric analysis is usually exported in one of two forms: as mass loss or mass remaining (mg) by temperature.
+An example dataset that contains mass loss data for the species *Juncus amabilis* is included in the package:
+
 ```{r}
@@
 
-We can use the function `process()` to take the derivative of this mass loss data, resulting in rate of mass loss over temperature data.
-To do so you simply need to specify the dataset, identify which columns contain temperature and mass loss data, and provide a value for the starting mass of the sample.
-The function defaults to temperature data in Celsius, but you can also modify to indicate the data is provided in Kelvin, by adding `temp_type = 'K'`.
+We can use the function `process()` to take the derivative of this data, resulting in rate of mass loss over temperature data.
+To do so you need to specify the dataset, the initial mass of sample, the name of the temperature data column, and the name of your mass loss or mass data column.
+If you have mass loss data you can specify with `mass_loss` argument, if it's mass remaining data you can use the `mass` argument.
+You only need to provide one.
+The function defaults to temperature data in Celsius, but you can also indicate the data is provided in Kelvin, by adding `temp_units = 'K'`.
+
 ```{r}
-tmp <- process(juncus, temp = 'temp_C', mass = 'mass_loss', init_mass = 18.96)
+tmp <- process(juncus, 
+               init_mass = 18.96, 
+               temp = 'temp_C', 
+               mass_loss = 'mass_loss')
 tmp
@@
 
-The default plot function for the derivative data shows you both the original mass loss curve and the derivative rate of mass loss curve.
+The default plot function for the derivative data shows you both the mass with temperature curve and the derivative rate of mass loss curve.
 
-Processed data then simply needs to be deconvolved into its constituent parts.
+Processed data then needs to be deconvolved into its constituent parts.
 The deconvolve function takes care of this step, by cropping the derivative data to exclude dehydration and then running the Fraser-Suzuki mixture model and estimating individual curve parameters and weights.
+
 ```{r}
@@
 The `deconvolve()` function results in a variety of outputs.
-You can use a variety of accessor functions to look at these.
+You can use a accessor functions to look at these.
 `component_weights()` will display the weights of each carbon component, `rate_data()` will show you the modified dataset used for fitting, `model_fit()` will show you the model fit, and `temp_bounds()` will print the temperature values at which the data were cropped for analysis.
-You can also plot the resulting output using the default plotting function.
+You can also plot the resulting output using the default plotting function, which can be in black and white or in colour.
 
-You can see the full worked example in the vignette, which you can access on the or in R:
-```{r}
-vignette('mixchar')
-```
+<hr>
+
+# Contribution
 
@@
 
-## Acknowledgements
-Thank you to Nick Tierney for valuable feedback during development. Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project.
+# Acknowledgements
+Thank you to Nick Tierney and David Wilkinson for valuable feedback during development.
+Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project.

### 2018-08-08 R/component_weights.R
change process function inputs, change examples accordingly

@@ -6,7 +6,8 @@
 #' @examples
 #' \dontrun{
 #' data(juncus)
-#' tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96, temp_type = 'C')
+#' tmp <- process(juncus, init_mass = 18.96,
+#'                temp = 'temp_C', mass_loss = 'mass_loss')
 #' output <- deconvolve(tmp)
 #' component_weights(output)
 #' }

### 2018-08-08 R/deconvolve.R

@@ -13,14 +13,19 @@
 #' you have selected the number of curves in the n_curves parameter.
 #' @param upper_vec vector of upper bound values for nls. Only specify this vector if
 #' you have selected the number of curves in the n_curves parameter.
-#' @return decon list containing amended dataframe, bounds, model output, mass fractions
+#' @return decon list containing amended dataframe, temperature bounds,
+#' minpack.lm model fit, the number of curves fit, and estimated component weights
 #' @keywords thermogravimetry fraser-suzuki deconvolution
-#' @importFrom stats integrate setNames loess
 #' @examples
 #' \dontrun{
 #' data(juncus)
-#' tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96)
+#' tmp <- process(juncus, init_mass = 18.96,
+#'                temp = 'temp_C', mass_loss = 'mass_loss')
 #' output <- deconvolve(tmp)
+#' my_starting_vec <- c(height_1 = 0.003, skew_1 = -0.15, position_1 = 250, width_1 = 50,
+#                       height_2 = 0.006, skew_2 = -0.15, position_2 = 320, width_2 = 30,
+#                       height_3 = 0.001, skew_3 = -0.15, position_3 = 390, width_3 = 200)
+#' output <- deconvolve(tmp, n_curves = 3, start_vec = my_starting_vec)
 #' }
 #' @export
 
@@ -65,6 +70,7 @@ deconvolve <- function (process_object,
     n_peaks <- 4
   }
 
+  # assign starting values for parameters
   if (is.null(start_vec) & n_peaks == 3) {
     theta <- c(0.003, -0.15, 250, 50,
                0.006, -0.15, 320, 30,
@@ -80,6 +86,7 @@ deconvolve <- function (process_object,
     theta <- start_vec
   }
 
+  # assign lower bound for parameter estimates
   if (is.null(lower_vec) & n_peaks == 3) {
     lb <- c(0, -0.33, 0, 50,
             0, -0.33, 290, 0,
@@ -95,6 +102,7 @@ deconvolve <- function (process_object,
     lb <- lower_vec
   }
 
+  # assign upper bound for parameter estimates
   if (is.null(upper_vec) & n_peaks == 3) {
     ub <- c(2, 0.25, 280, 100,
             2, 0.25, 380, 50,
@@ -125,8 +133,8 @@ deconvolve <- function (process_object,
 
   # output
   output <- list(data = mod_df,
[…]

### 2018-08-08 R/inflection.R

@@ -14,11 +14,12 @@ three_peaks <- function (x) {
 #' @keywords internal
 #' @return returns a list of values. $x returns the inflections points within x.
 #' @importFrom zoo rollapply zoo
+#' @importFrom stats loess
 ## script cred https://stats.stackexchange.com/questions/36309/how-do-i-find-peaks-in-a-dataset
 
 inflection <- function(x, y, w = 1, ...) {
   n <- length(y)
-  y.smooth <- loess(y ~ x, ...)$fitted
+  y.smooth <- stats::loess(y ~ x, ...)$fitted
   y.max <- zoo::rollapply(zoo::zoo(y.smooth),
                           2*w+1,
                           max,

### 2018-08-08 R/model_fit.R

@@ -6,12 +6,13 @@
 #' @examples
 #' \dontrun{
 #' data(juncus)
-#' munge <- process(juncus, 'temp_C', 'mass_loss', 18.96, temp_type = 'C')
-#' output <- deconvolve(munge)
+#' tmp <- process(juncus, init_mass = 18.96,
+#'                temp = 'temp_C', mass_loss = 'mass_loss')
+#' output <- deconvolve(tmp)
 #' model_fit(output)
 #' }
 #' @export
 
 model_fit <- function (object) {
-  object$minpack.lm
+  object$model_fit
 }

### 2018-08-08 R/param_select.R

@@ -2,13 +2,14 @@
 #'
 #' This function otimises parameter selection so that the model will ultimately converge.
 #'
-#' @param theta vector of starting values for each of 12 parameters
-#' @param lb vector of lower bounds on each of 12 parameters
+#' @param theta vector of starting values for each parameter
+#' @param lb vector of lower bounds on each parameter
+#' @param ub vector of upper bounds on each parameter
 #' @param model mathematical function to be applied
 #' @param temp temperature values
 #' @param obs DTG mass values
+#' @param seed random seed for optimiser
 #' @param restarts number of times for optimiser to restart
-#' @param ranseed random seed for optimiser
 #' @return optimised starting parameter values
 #' @keywords internal
 #' @importFrom nloptr nloptr

### 2018-08-08 R/plot.decon.R

@@ -15,9 +15,9 @@
 
 plot.decon <- function (x, bw = TRUE, ...) {
 
-  temp <- seq(x$bounds[1], x$bounds[2], length.out = nrow(x$data))
+  temp <- seq(x$temp_bounds[1], x$temp_bounds[2], length.out = nrow(x$data))
   data <- x$data
-  fit <- x$minpack.lm
+  fit <- x$model_fit
 
   params <- as.data.frame(summary(fit)$coefficients[,1])
 

### 2018-08-08 R/print.decon.R

@@ -14,7 +14,7 @@ print.decon <- function (x, ...) {
 
   cat(paste0('Deconvolution by ', x$n_curves,'-part Fraser-Suzuki
              mixture model fitted to \n',
-             nrow(x$data), ' datapoints from ', x$bounds[1],
-             ' to ', x$bounds[2], ' degrees C.'))
+             nrow(x$data), ' datapoints from ', x$temp_bounds[1],
+             ' to ', x$temp_bounds[2], ' degrees C.'))
 
 }

### 2018-08-08 R/print.process.R

@@ -14,8 +14,8 @@ print.process <- function (x, ...) {
 
   cat(paste('Derivative thermogravimetry data (DTG)
             calculated for\n', nrow(x$data), 'datapoints from',
-            round(x$bounds[1], 2), 'to',
-            round(x$bounds[2], 2), 'degrees C.'))
+            round(x$temp_range[1], 2), 'to',
+            round(x$temp_range[2], 2), 'degrees C.'))
 
 }
 

### 2018-08-08 R/process.R

@@ -4,67 +4,97 @@
 #' the derivative of mass loss
 #'
 #' @param data dataframe
+#' @param init_mass numeric value of initial sample mass in mg
 #' @param temp column name containing temperature values
-#' @param mass column name containing mass loss values in grams
-#' @param init_mass numeric value of initial sample mass in grams
-#' @param temp_type specify units of temperature, default = Celsius.
-#' Specify 'K' if in Kelvin
-#' @return decon list containing amended dataframe, bounds,
-#' model output, mass fractions
+#' @param mass_loss column name containing mass loss values in mg
+#' @param mass column name containing mass values in mg
+#' @param temp_units specify units of temperature, default = Celsius.
+#' Can specify 'K' or 'Kelvin' if in Kelvin
+#' @return process list containing modified dataframe, initial mass
+#' of sample, and maximum and minimum temperature values
 #' @keywords thermogravimetry fraser-suzuki deconvolution
-#' @importFrom stats integrate setNames
 #' @examples
 #' data(juncus)
-#' tmp <- process(juncus, 'temp_C', 'mass_loss', 16.85)
+#' tmp <- process(juncus, init_mass = 18.96,
+#'                temp = 'temp_C', mass_loss = 'mass_loss')
 #'
 #' @export
 
-process <- function (data, temp, mass, init_mass,
-                     temp_type = 'C') {
+process <- function (data, init_mass, temp,
+                     mass_loss = NULL,
+                     mass = NULL,
+                     temp_units = 'C') {
 
+  # subset provided data to avoid presence of
+  # other columns with conflicting names
+  subset <- data[, c(temp, mass_loss, mass)]
+
+  # check that mass data is provided
+  if (is.null(mass_loss) & is.null(mass)) {
+    stop('Specify either mass or mass loss
+         data column name')
+  }
+
+  # check temperature inputs
   temp_measures <- c('C', 'Celsius', 'K', 'Kelvin')
 
-  if (!isTRUE(is.element(temp_type, temp_measures))) {
+  if (!isTRUE(is.element(temp_units, temp_measures))) {
[…]

### 2018-08-08 R/rate_data.R

@@ -5,7 +5,8 @@
 #' @keywords thermogravimetry fraser-suzuki deconvolution
 #' @examples
 #' data(juncus)
-#' tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96, temp_type = 'C')
+#' tmp <- process(juncus, init_mass = 18.96,
+#'                temp = 'temp_C', mass_loss = 'mass_loss')
 #' rate_data(tmp)
 #'
 #' @export

### 2018-08-08 R/temp_bounds.R

@@ -5,13 +5,15 @@
 #' @keywords thermogravimetry fraser-suzuki deconvolution temperature
 #' @examples
 #' data(juncus)
-#' tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96, temp_type = 'C')
+#' tmp <- process(juncus, init_mass = 18.96,
+#'                temp = 'temp_C', mass_loss = 'mass_loss')
 #' temp_bounds(tmp)
 #'
 #' @export
 
 temp_bounds <- function (object) {
 
-  object$bounds
+  if (class(object) == 'process') return(object$temp_range)
+  if (class(object) == 'decon') return(object$temp_bounds)
 
 }

### 2018-08-08 R/weight_quantiles.R

@@ -10,12 +10,12 @@
 weight_quantiles <- function (output, seed) {
 
   # least squares estimate:
-  est <- stats::coef(output$minpack.lm)
+  est <- stats::coef(output$model_fit)
 
   # variance-covariance matrix, assuming truncated
   # multivariate normal distribution over LS surface
-  sry <- summary(output$minpack.lm)
-  residvar <- stats::deviance(output$minpack.lm) / sry$df[2]
+  sry <- summary(output$model_fit)
+  residvar <- stats::deviance(output$model_fit) / sry$df[2]
   vcov <- sry$cov.unscaled * residvar
 
   # random draws of parameters, proportional to likelihood
@@ -77,8 +77,8 @@ weight_quantiles <- function (output, seed) {
 get_weights <- function (param_vec, output) {
 
   n_curves <- output$n_curves
-  lower_temp <- output$bounds[1]
-  upper_temp <- output$bounds[2]
+  lower_temp <- output$temp_bounds[1]
+  upper_temp <- output$temp_bounds[2]
 
   if (n_curves == 3) {
     curve_vec <- 1:3
@@ -106,6 +106,7 @@ get_weights <- function (param_vec, output) {
 #' @param param_vec vector of parameters
 #' @param lower_temp lower temperature bound
 #' @param upper_temp upper temperature bound
+#' @importFrom stats integrate
 #' @return weight of component
 #'
 
@@ -131,10 +132,10 @@ wt_component <- function (j,
 
   # weight percent of each component,
   # where the integral is the fraction
-  # of initial mass of that compoenent.
-  wt <- integrate(Vectorize(f_j),
-                  lower = lower_temp,
-                  upper = upper_temp)$value * 100
+  # of initial mass of that component.
+  wt <- stats::integrate(Vectorize(f_j),
+                         lower = lower_temp,
+                         upper = upper_temp)$value * 100
 
   wt
 }

### 2018-08-08 manuscript/manuscript.Rnw
modify size of plot in manuscript
revise authors, add packages, add version requirement

@@
 3. Trevathan-Tackett, Stacey M. \\
-4. Catford, Jane A. \\
-5. Macreadie, Peter I. \\
 4. Golding, Nick.
@@
 3. Research Fellow, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
-4. Assistant Professor, Biological Sciences, University of Southampton, Highfield Campus, Southampton SO17 1BJ, UK \\
-5. Associate Professor, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
-6. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia
+4. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia
 
@@
 <<eval = FALSE>>=
-plot(deriv_juncus)
+plot(deriv_juncus, cex = 2)
 @
@@
 Rate of mass loss scaled by initial mass of sample.', out.width = '0.7\\linewidth', asp = 1, fig.align = 'center'>>=
-par(mar = c(5,5,1,1))
 plot(output_juncus, bw = FALSE)
@@
 The Fraser-Suzuki family of functions are exported to allow users to create their own plots from the model outputs. Detailed descriptions of how to do so are included in the package vignettes.
+
+<<>>=
+stt <- read.table("../mixchar.notes/USATtLeaf_data.txt", fill = TRUE, header = FALSE, skip = 46, skipNul = TRUE, fileEncoding="UTF-16LE")
+colnames(stt) <- c("time", "temp", "weight", "deriv")
+@
 
@@
 \section*{Programming language}
-R version XXX or higher.
+R version 3.2.0 or higher.
 
@@
 \section*{Dependencies}
-R packages: \verb|minpack.lm|, \verb|nloptr|, \verb|tmvtnorm|, \verb|zoo|.
+R packages: \verb|graphics|, \verb|minpack.lm|, \verb|nloptr|, \verb|stats|, \verb|tmvtnorm|, \verb|zoo|.
 
@@
 Nick Tierney for reviewing an early version of the package.
+We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for assistance in the field collecting plant specimens.
 We would like to thank the University of Melbourne Department of Chemical and Biomolecular Engineering for access to and training on the TGA-FTIR.
 Vegetation collection for data used to build and verify the model was conducted under Victorian Department of Environment, Land, Water and Planning Permit No 10007429.
-We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for assistance in the field collecting plant specimens.
 

### 2018-08-08 README.Rmd
remove <hr> because not showing up properly in .md
remove print.process output

@@
 
-<hr>
-
 # Installation
@@
 ```
-
-<hr>
 
@@
                mass_loss = 'mass_loss')
-tmp
 ```
@@
 
-<hr>
-
 # Contribution
@@
 # Acknowledgements
+
 Thank you to Nick Tierney and David Wilkinson for valuable feedback during development.

### 2018-08-10 README.Rmd
add vignette install option

@@
 For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/Background).
-You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar) or in the vignette that you can access via R as follows:
+You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar) or in the vignette that you can access via R by installing with the `build_vignettes` argument as follows:
 
 ```{r, eval = FALSE}
+devtools::install_github("smwindecker/mixchar", build_vignettes = TRUE)
 browseVignettes('mixchar')

### 2018-08-10 R/plot.process.R
ensure that graphical parameters are reset

@@ -64,4 +64,5 @@ plot.process <- function (x, plot_type = NULL, cex = 1, ...) {
     p_dtg(df)
   }
 
+  par(mfrow = c(1,1))
 }

### 2018-08-10 R/weight_quantiles.R
change so mean is listed before upper and lower estimates for weights

@@ -57,9 +57,9 @@ weight_quantiles <- function (output, seed) {
   # weights calculated from the maximum likelihood estimates
   means <- get_weights(est, output)
 
-  all_weights <- rbind(CI_df, means)
+  all_weights <- rbind(means, CI_df)
   all_weights$value_type <- row.names(all_weights)
-  all_weights$value_type[all_weights$value_type == 3] <- 'mean'
+  all_weights$value_type[all_weights$value_type == 1] <- 'mean'
 
   rownames(all_weights) <- c()
 

### 2018-08-10 README.Rmd
revise intro on readme

@@
 
-Ecologists are often interested in determining the composition of plant cell wall biomass.
-Proportions of the primary carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.
+Plant cell wall biomass is composed of a range of different types of carbon.
+Proportions of primary carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.
 Traditional methods for calculation of these components involve wet chemistry methods that can be monetarily and environmentally costly.

### 2018-08-10 README.Rmd
make it so that 'peak' refers to individual curves and 'curve' to overal curve

@@
 Processed data then needs to be deconvolved into its constituent parts.
-The deconvolve function takes care of this step, by cropping the derivative data to exclude dehydration and then running the Fraser-Suzuki mixture model and estimating individual curve parameters and weights.
+The deconvolve function takes care of this step, by cropping the derivative data to exclude dehydration and then running the Fraser-Suzuki mixture model and estimating individual peak parameters and weights.
 
@@
 
-Although most biomass samples have only three main components (corresponding to hemicellulose, cellulose, and lignin), some have a second hemicellulose curve in the low temperature range.
-The function will decide whether three or four curves are best, but you can override it by modifying the `n_curves` argument.
+Although most biomass samples have only three main components (corresponding to hemicellulose, cellulose, and lignin), some have a second hemicellulose peak in the low temperature range.
+The function will decide whether three or four peaks are best, but you can override it by modifying the `n_peaks` argument.
 The function also has built in starting values for the nonlinear optimisation.

### 2018-08-10 R/deconvolve.R

@@ -6,13 +6,13 @@
 #' @param lower_temp lower temperature bound to crop dataset, default to 120
 #' @param upper_temp upper temperature bound to crop dataset, default to 700
 #' @param seed random seed for nloptr optimiser
-#' @param n_curves number of curves optional specification
+#' @param n_peaks number of curves optional specification
 #' @param start_vec vector of starting values for nls function. Only specify this vector if
-#' you have selected the number of curves in the n_curves parameter.
+#' you have selected the number of curves in the n_peaks parameter.
 #' @param lower_vec vector of lower bound values for nls. Only specify this vector if
-#' you have selected the number of curves in the n_curves parameter.
+#' you have selected the number of curves in the n_peaks parameter.
 #' @param upper_vec vector of upper bound values for nls. Only specify this vector if
-#' you have selected the number of curves in the n_curves parameter.
+#' you have selected the number of curves in the n_peaks parameter.
 #' @return decon list containing amended dataframe, temperature bounds,
 #' minpack.lm model fit, the number of curves fit, and estimated component weights
 #' @keywords thermogravimetry fraser-suzuki deconvolution
@@ -25,7 +25,7 @@
 #' my_starting_vec <- c(height_1 = 0.003, skew_1 = -0.15, position_1 = 250, width_1 = 50,
 #                       height_2 = 0.006, skew_2 = -0.15, position_2 = 320, width_2 = 30,
 #                       height_3 = 0.001, skew_3 = -0.15, position_3 = 390, width_3 = 200)
-#' output <- deconvolve(tmp, n_curves = 3, start_vec = my_starting_vec)
+#' output <- deconvolve(tmp, n_peaks = 3, start_vec = my_starting_vec)
 #' }
 #' @export
 
@@ -33,7 +33,7 @@ deconvolve <- function (process_object,
                         lower_temp = 120,
                         upper_temp = 700,
                         seed = 1,
-                        n_curves = NULL,
+                        n_peaks = NULL,
                         start_vec = NULL,
                         lower_vec = NULL,
                         upper_vec = NULL) {
@@ -57,16 +57,16 @@ deconvolve <- function (process_object,
   temp <- mod_df$temp_C
   obs <- mod_df$deriv
 
[…]

### 2018-08-10 R/weight_quantiles.R

@@ -76,15 +76,15 @@ weight_quantiles <- function (output, seed) {
 
 get_weights <- function (param_vec, output) {
 
-  n_curves <- output$n_curves
+  n_peaks <- output$n_peaks
   lower_temp <- output$temp_bounds[1]
   upper_temp <- output$temp_bounds[2]
 
-  if (n_curves == 3) {
+  if (n_peaks == 3) {
     curve_vec <- 1:3
   }
 
-  if (n_curves == 4) {
+  if (n_peaks == 4) {
     curve_vec <- 0:3
   }
 

### 2018-08-11 manuscript/manuscript.Rnw
update manuscript

@@
 2. Associate Professor, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
-3. Research Fellow, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
+3. Research Fellow, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3125, Australia \\
 4. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia
@@
 
-Ecologists are often interested in determining the composition of plant cell wall biomass.
+Importance of cell walls in ecosystems. characterisation is important in ecosystem and functional ecology because cell wall carbon makes up XXX of soil C.
+
 Proportions of the primary carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.
@@
 \section*{Introduction}
+
 Plant cell wall biomass is composed of a range of different types of carbon.
+
+i think you've moved quite quickly through a range of ideas in this one sentence: multiple components, components matter, composition differs between species, composition effects on ecosystem.
+I'd say that these proportions influence precesses like energy release under combustion and decomposition of litter.
+Biomass carbon in different plant species may vary in their composition of these compounds, with flow on effects on litter decomposition where various species occur.
+
 Ecologists can use these proportions of biomass carbon to make generalisations about species' effects on ecosystem processes such as litter decomposition, which links plant biomass to the global carbon cycle \citep{cornwell2008}.
-Biofuels researchers use proportions of biomass carbon types to estimate kinetic decay parameters of species' tissue.
-Traditional methods for calculation of lignocellulosic biomass involve wet chemistry assays for carbon component analysis, which are time-consuming and adversely impact the environment through use of sulfuric acid and acetic anhydride, among other chemicals.
-Thermogravimetric analysis (TGA) is an alternative method, already in use among biofuels researchers, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in a $N_2$ environment, termed pyrolysis).
+Biofuels researchers use proportions of biomass carbon types to estimate kinetic decay parameters of species' tissue \citep{chen2017,orfao2001,hu2016}.
+Traditional methods for calculation of lignocellulosic biomass involve wet chemistry assays for carbon component analysis \citep{fengel}, which are time-consuming and adversely impact the environment through use of sulfuric acid and acetic anhydride, among other chemicals.
+Thermogravimetric analysis (TGA) is an alternative method, already in use among biofuels researchers, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in an $N_2$ environment, termed pyrolysis).
 \\
 \\
-Mass loss during pyrolysis can be regarded as the sum of the degradation of the main components of the sample \textemdash hemicelluloses, cellulose, and lignin \citep{hu2016,cheng2015,perejon2011,orfao2001,muller-hagedorn2007}.
+Mass loss during pyrolysis can be regarded as the sum of the degradation of the main components of the sample \textemdash often simplified as hemicelluloses, cellulose, and lignin \citep{hu2016,cheng2015,perejon2011,orfao2001,muller-hagedorn2007}.
 Therefore, the multi-peaked rate of mass loss curve can be mathematically separated into constituent parts with a mixture model \textemdash termed deconvolution.
-By integrating under these individual curves, we can estimate the contribution of each component to the overall initial sample.
-This method has been validated by studies comparing estimates to experimental measurements \citep{yang2006}.
+XXXXXXX add mixture model citations here.
+The component peaks identified by the mixture model represent the proportion of initial mass of each component lost over time.
+The integral, or area under the peak, therefore gives us an estimate of the proportion of that component in the overall sample.
+Thermogravimetric analysis with deconvolution has been validated by studies comparing estimates to wet chemistry measurements \citep{yang2006}.
 Plant trait measurement is guided by the principle of standardised, widely reproducible methods \citep{perez-harguindeguy2013}, but much of the published literature use commercial software to deconvolve the rate of mass loss curve \citetext{for example OriginPro \citealp{chen2017}, PeakFit \citealp{perejon2011}, Fityk \citealp{perejon2011}, or Datafit \citealp{cheng2015}}.
-Software accessibility and reproducibility may be one reason why thermogravimetric analysis for carbon type estimation has not yet been widely adopted by functional ecologists, despite being previously used to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucaplyts \citealp{orfao2001}}.
-In addition, proprietary software inhibits researchers already conducting this type of analysis from making their analyses independently reproducible.
+Proprietary software inhibits researchers already conducting this type of analysis from making their analyses independently reproducible.
+Software accessibility and reproducibility may be one reason why thermogravimetric analysis for carbon type estimation has not yet been widely adopted by functional ecologists, despite being previously used to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucalyptus trees \citealp{orfao2001}}.
 \\
@@
 
-\textbf{\textit{Collect and load data}}\\
+\textbf{\textit{Litter collection and preparation}}\\
 We developed and tested the functions in this package using the thermogravimetric decay data for litter of 29 different plant species.
@@
 We dried the fresh litter at 60 $^{\circ}$C for 72 hours and ground litter to \textless $40 \mu m$ using a Retsch Centrifugal Mill ZM200.
+\\
+\\
 We pyrolysed 10\textendash20 mg subsamles of dry, ground litter in an N$_2$ environment from 30\textendash800 $^{\circ}$C at a temperature ramp of 10 $^{\circ}$C/min using a Netzsch TGA-FTIR thermogravimetric analyser (Department of Biomedical Engineering, University of Melbourne).
-The resulting data is mass loss in grams against temperature (Fig.~\ref{Fig:massloss}).
+The resulting data is mass loss (mg) against temperature (Fig.~\ref{Fig:massloss}).
 
@@
 
-\textbf{\textit{Process data}}\\
-After we've loaded our data, we need to calculate the rate of mass loss across temperature.
-To do so, the \verb|process| function takes the derivative of our mass loss data, taking as arguments the dataset, the column names for the temperature and mass loss data, and a value for the starting mass of the sample.
-The function defaults to temperature data in Celsius, but you can also indicate the data is provided in Kelvin, by specifying the argument \verb|temp_type = K|.
+<<echo = FALSE, fig.cap = '\\label{Fig:massloss} Mass across temperature \\textit{Juncus amabilis}.', out.width = '.49\\linewidth'>>=
+tmp <- process(juncus, init_mass = 18.96,
+               temp = 'temp_C', mass_loss = 'mass_loss')
+plot(tmp, plot_type = 'mass')
+@
+
+\textbf{\textit{Deconvolution}}\\
+\textit{Rate of mass loss}\\
+After we've loaded our data, we need to calculate the rate of mass loss by taking the derivative.
+The \verb|process| function needs the dataset, the initial mass of sample, the name of the temperature data column, and the name of the mass column (mg).
 
@@
 deriv_juncus <- process(juncus,
-                        temp = 'temp_C',
-                        mass = 'mass_loss',
-                        init_mass = 18.96)
+                        init_mass = 18.96,          # initial mass of sample
+                        temp = 'temp_C',            # temperature data column name
+                        mass_loss = 'mass_loss',    # mass loss data column name
+                        temp_units = 'C')           # 'C' is the default setting
 deriv_juncus
@@
 
-The output of the \verb|process| function is a list of three items: the modified dataframe including the derivative thermogravimetric rate of mass loss data (DTG), the initial mass value that you supplied, and the maximum and minimum temperature of your data.
-If you \verb|plot()| the output of the \verb|process| function you will get two curves: the mass of sample across time and the rate of mass loss curve (Fig.~\ref{Fig:process}).
-If you're only interested in one plot, you can specify \verb|plot_type = mass| or \verb|plot_type = rate|.
+The output of the \verb|process| function is a list of three items: the modified dataframe including the derivative thermogravimetric rate of mass loss data (DTG), the initial mass value that was supplied, and the maximum and minimum temperature of values in the data.
+Plotting this output will results in two curves: the mass of sample across temperature and the rate of mass loss curve (Fig.~\ref{Fig:rateloss}).
+The rate of mass loss curve is a multi-peaked curve encompassing three main phases \citep{orfao2001}:
 
-<<eval = FALSE>>=
-plot(deriv_juncus, cex = 2)
-@
-
-<<echo = FALSE, fig.cap = '\\label{Fig:process} Process function output from \\textit{Juncus amabilis} example dataset.', fig.subcap = c('\\label{Fig:massloss} Thermogravimetric mass loss curve.', '\\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample.'), out.width = '.49\\linewidth', fig.asp = 1, fig.ncol = 2>>=
-par(mar = c(5, 5, 2, 1))
-plot(deriv_juncus, plot_type = 'mass')
-par(mar = c(5, 5, 2, 1))
-plot(deriv_juncus, plot_type = 'rate')
-@
-
-\begin{table}[!ht]
-	\caption{Exported functions}
-	\label{Tab:functions}
-	\centering
-	\footnotesize
-	\begin{tabularx}{\linewidth}{llX}
-        		\toprule
-        		Function family & Function name & Description \\
-        		\midrule
-		Data & \verb|juncus| & Example thermogravimetric data for \textit{Juncus amabilis} \\
-		Data & \verb|marsilea| & Example thermogravimetric data for \textit{Marsilea drumondii} \\
-		Basic use & \verb|process()| & Calculates the derivative rate of mass loss of thermogravimetric data \\
-		Basic use & \verb|deconvolve()| & Deconvolves derivative rate of mass loss data \\
-		Accessor function & \verb|temp_bounds()| & Access temperature bounds used to crop data for mixture model \\
-		Accessor function & \verb|rate_data()| & Access processed dataframe including mass loss, rate of mass loss, and temperature \\
-		Accessor function & \verb|model_fit()| & Access fit of nonlinear mixture model \\
-		Accessor function & \verb|component_weights()| & Access mean, upper, and lower bounds for component weight estimates \\
-		Fraser-Suzuki function & \verb|fs_function()| & Fraser-Suzuki equation for a single curve \\
-		Fraser-Suzuki function & \verb|fs_mixture()| & Fraser-Suzuki mixture model equation \\
-		Fraser-Suzuki function & \verb|fs_model()| & Non-linear model implementation of Fraser-Suzuki mixture model \\
-		S3 method & \verb|print(<process>)| & Default print method for process object (derived from \verb|process()|) \\
-		S3 method & \verb|plot(<process>)| & Default plot method for process object (derived from \verb|process()|) \\
-		S3 method & \verb|print(<deconvolve>)| & Default print method for decon object (derived from \verb|deconvolve()|) \\
-		S3 method & \verb|plot(<deconvolve>)| & Default plot method for process object (derived from \verb|deconvolve()|) \\
-        		\bottomrule
-	\end{tabularx}
-\end{table}
-
-\textbf{\textit{Deconvolve data}}\\
-Once we have calculated the rate of mass loss, we use the \verb|deconvolve| function to estimate the proportions of carbon components.
-Under the hood, it does so with a series of steps: it crops the derivative rate of mass loss data, estimates parameter values from the non-linear model, and finally integrates under each resulting curve to estimate weight proportions of primary components.
-We explain these steps in detail below.
-\\
-\\
-\textit{Cropping DTG data}\\
-The rate of mass loss (i.e. negative first derivative or DTG) is a multi-peaked curve (Fig.~\ref{Fig:rateloss}) encompassing three main phases \citep{orfao2001}:
 \begin{enumerate}
@@
 \end{enumerate}
+
+<<echo = FALSE, fig.cap = '\\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample for \\textit{Juncus amabilis}.
+Line segments 1, 2, and 3 on represent mass loss phases.', out.width = '.49\\linewidth'>>=
+plot(deriv_juncus, plot_type = 'rate')
+segments(x0 = 40, y0 = 0.0018, x1 = 40, y1 = 0.002, lwd = 3, col = 'darkgrey')
+segments(x0 = 40, y0 = 0.002, x1 = 120, y1 = 0.002, lwd = 3, col = 'darkgrey')
+segments(x0 = 120, y0 = 0.0018, x1 = 120, y1 = 0.002, lwd = 3, col = 'darkgrey')
+text(x = ((120-40)/2+40), y = 0.0024, '1', cex = 2, col = 'darkgrey')
+
+segments(x0 = 120, y0 = 0.0078, x1 = 120, y1 = 0.008, lwd = 3, col = 'darkgrey')
+segments(x0 = 120, y0 = 0.008, x1 = 650, y1 = 0.008, lwd = 3, col = 'darkgrey')
+segments(x0 = 650, y0 = 0.0078, x1 = 650, y1 = 0.008, lwd = 3, col = 'darkgrey')
+text(x = 400, y = 0.0076, '2', cex = 2, col = 'darkgrey')
+
+segments(x0 = 650, y0 = 0.0008, x1 = 650, y1 = 0.001, lwd = 3, col = 'darkgrey')
+segments(x0 = 650, y0 = 0.001, x1 = 790, y1 = 0.001, lwd = 3, col = 'darkgrey')
+segments(x0 = 790, y0 = 0.0008, x1 = 790, y1 = 0.001, lwd = 3, col = 'darkgrey')
+text(x = ((790-650)/2+650), y = 0.0014, '3', cex = 2, col = 'darkgrey')
+@
+
+\textit{Crop DTG data}\\
 Since the overall DTG curve thus represents the loss of extractives, water, inorganic matter, and volatiles in addition to our components of interest \citep{hu2016}, we isolate mass loss from our primary biomass components by cropping the DTG data to Phase 2 (120\textendash650 $^{\circ}$C).
@@
 
-where mass ($m$) is expressed as a fraction of mass at temperature $T$ ($M_T$) of the initial sample mass ($M_0$) (Eq.~\ref{eqn:fraction}), $c_i$ is the mass of component $i$ that is decayed (Eq.~\ref{eqn:decayed_mass}), and the mass loss curve of each individual component ($\frac{d\alpha_{i}}{dT}$) is the derivative of $\alpha_i$, the conversion of mass at a given temperature ($M_{Ti}$), from the initial ($M_{0i}$), given total mass lost between the initial and final ($M_{\infty i}$) temperature for each curve  (Eq.~\ref{eqn:alpha}).\\
+where mass ($m$) is expressed as a fraction of mass at temperature $T$ ($M_T$) of the initial sample mass ($M_0$) (Eq.~\ref{eqn:fraction}), $c_i$ is the mass of component $i$ that is decayed (Eq.~\ref{eqn:decayed_mass}), and the mass loss curve of each individual component ($\frac{d\alpha_{i}}{dT}$) is the derivative of $\alpha_i$, the conversion of mass at a given temperature ($M_{Ti}$), from the initial ($M_{0i}$), as a proportion of total mass lost between the initial and final ($M_{\infty i}$) temperature for each peak  (Eq.~\ref{eqn:alpha}).\\
 \\
-Although most of our results can be described with only $n = 3$ peaks, corresponding to a single curve each of hemicelluose, cellulose, and lignin, some species yield a second hemicellulose peak at a lower temperature, resulting in $n = 4$ independent curves.
+Although most of our results can be described with only $n = 3$ peaks, corresponding to a single peak each of hemicelluose, cellulose, and lignin, some litter samples yield a second hemicellulose peak at a lower temperature, resulting in $n = 4$ independent peaks.
 This is because the soluble carbohydrates in plant tissue can take many forms, including xylan, amylose, etc., which apparently degrade at different temperatures \citep[see also][]{chen2017,muller-hagedorn2007}.
-\verb|deconvolve| will decide whether three or four curves are best using an internal function that determines if there is a peak below 220 $^{\circ}$C.
-Upon inspection of your curve you can override this by modifying the \verb|n_curves| argument.\\
+\verb|deconvolve| will decide whether three or four peaks are best using an internal function that determines if there is a peak below 220 $^{\circ}$C.
+Upon inspection of your curve you can override this by specifying the \verb|n_peaks| argument.\\
 \\
-In order to fit the mixture model, we must determine the shape of the individual curves ($\frac{d\alpha_{i}}{dT}$) that are summed to produce it.
+In order to fit the mixture model, we must determine the shape of the individual peaks ($\frac{d\alpha_{i}}{dT}$) that are summed to produce it.
 Many different functions have been proposed: the asymmetric bi-Gaussian \citep{sun2015}, logistic \citep{barbadillo2007}, Weibull \citep{cai2007}, asymmetric double sigmoidal \citep{chen2017}, and the Fraser-Suzuki function \citep{perejon2011,hu2016}.
-Comparisons of several techniques \citep{svoboda2013,perejon2011,cheng2015} found that the Fraser-Suzuki function best fit these kinetic curves, since it allows for asymmetry (a parametric examination of the Fraser-Suzuki function can be found in Fig.~\ref{Fig:fs_simulation}).
-We therefore use the Fraser-Suzuki function to describe the rate expression of a single curve (Eq.~\ref{eqn:fs_function}) as follows:
+Comparisons of several techniques \citep{svoboda2013,perejon2011,cheng2015} found that the Fraser-Suzuki function best fit these kinetic peaks, since it allows for asymmetry (a parametric examination of the Fraser-Suzuki function can be found in Fig.~\ref{Fig:fs_simulation}).
+We therefore use the Fraser-Suzuki function to describe the rate expression of a single peak (Eq.~\ref{eqn:fs_function}) as follows:
 
@@
 
-where T is temperature ($^\circ$C), and the parameters $h_i$, $s_i$, $p_i$, and $w_i$ are height, skew, position, and width of the curve, respectively.
+where T is temperature ($^\circ$C), and the parameters $h_i$ ($^{\circ}$C^{-1}), $s_i$, $p_i$ ($^{\circ}$C), and $w_i$ ($^{\circ}$C) are height, skew, position, and width of the peak, respectively.
 In total, our model estimates 12 or 16 parameters, one for each parameter of Eq.~\ref{eqn:fs_function} for either 3 or 4 primary components.
@@
 \verb|deconvolve| uses non-linear optimisation with residual sum of squares to fit the rate expression \citetext{as in \citealp{cheng2015}}.
-Starting values were selected based on curves depicted in the literature \citep{muller-hagedorn2007} and from the results of running an identical deconvolution on pure cellulose and lignin samples.
+Starting values for all parameters were selected based on curves depicted in the literature \citep{muller-hagedorn2007} and from the results of running an identical deconvolution on pure cellulose and lignin samples.
 Hemicelluloses decay in a reasonably narrow band beginning at a lower temperature \citep{muller-hagedorn2007}, so we used 270 for position and 50 for width.
@@
 These starting values can also be modified in the \verb|deconvolve| function with the \verb|start_vec|, \verb|lower_vec|, and \verb|upper_vec| arguments.
+
+Mixture modelling is hard, and very sensitive to  starting values.
+therefore one needs good starting values for the non-kinear mxture model step.
+but one cannt just give a all round set of these.
+instead by intersting a good routine to find good starting values, we use an optimisation.
+
 These initial starting values are optimised before model fitting using the \verb|NLOPTR_LN_BOBYQA| algorithm \citep{bobyqa} within the \verb|nloptr| \citep{nloptr} package.
@@
 \\
+
 \textit{Component weights}\\
-Once overall curve parameters are fit, we can pass each components's parameter estimates to a single Fraser-Suzuki function, and calculate the weight of the component in the overall sample by integrating under the curve (Eq.~\ref{eqn:integration}).
+Once overall curve parameters are fit, we can pass each component's parameter estimates to a single Fraser-Suzuki function, and calculate the weight of the component in the overall sample by integrating under the peak (Eq.~\ref{eqn:integration}).
 To estimate the uncertainty of the weight predictions, \verb|deconvolve| will calculate the 95\% interval of the weight estimates across a random sample of parameter estimates, drawn in proportion to their likelihood.
@@
 
-We interpret that the curve located around 250\textendash270 $^\circ$C corresponds to primary hemicelluloses (HC), around 310\textendash330 $^\circ$C to cellulose (CL), and around 330\textendash350 $^\circ$C to lignin (LG).
-If present, the fourth curve located below 200 $^\circ$C corresponds to the most simple hemicelluloses (HC-1).
-The second dataset included in the package, \verb|marsilea|, is an example of a four-curve deconvolution.
+We interpret that the peak located around 250\textendash270 $^\circ$C corresponds to primary hemicelluloses (HC), around 310\textendash330 $^\circ$C to cellulose (CL), and around 330\textendash350 $^\circ$C to lignin (LG).
+If present, the fourth peak located below 200 $^\circ$C corresponds to the most simple hemicelluloses (HC-1).
+The second dataset included in the package, \verb|marsilea|, provides an example of a four-peak deconvolution.
 A worked example can be found in the package vignettes.
@@
 }
-\item{the number of curves,
+\item{the number of peaks,
 <<>>=
-output_juncus$n_curves
+output_juncus$n_peaks
 @
 }
-\item{and the mean and upper and lower estimates of the weight of each component.
+\item{and the mean, 2.5\% and 97.5\% estimates, median, and standard deviation of the weight of each component.
 <<>>=
@@
 If you \verb|plot()| the output of the \verb|deconvolve| function you will see the result of the deconvolution (Fig.~\ref{Fig:decon}).
-This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components curves.
+This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components peaks.
 The default plot is in black and white, but you can plot a colour version that uses colour-blind friendly \verb|viridis| colours \citep{viridis} by specifying \verb|bw = FALSE|.
@@
 @
+
+\begin{table}[!ht]
+	\caption{Exported functions}
+	\label{Tab:functions}
+	\centering
+	\footnotesize
+	\begin{tabularx}{\linewidth}{llX}
+        		\toprule
+        		Function family & Function name & Description \\
+        		\midrule
+		Data & \verb|juncus| & Example thermogravimetric data for \textit{Juncus amabilis} \\
+		Data & \verb|marsilea| & Example thermogravimetric data for \textit{Marsilea drumondii} \\
+		Basic use & \verb|process()| & Calculates the derivative rate of mass loss of thermogravimetric data \\
+		Basic use & \verb|deconvolve()| & Deconvolves derivative rate of mass loss data \\
+		Accessor function & \verb|temp_bounds()| & Access temperature bounds used to crop data for mixture model \\
+		Accessor function & \verb|rate_data()| & Access processed dataframe including mass loss, rate of mass loss, and temperature \\
+		Accessor function & \verb|model_fit()| & Access fit of nonlinear mixture model \\
+		Accessor function & \verb|component_weights()| & Access mean, upper, and lower bounds for component weight estimates \\
+		Fraser-Suzuki function & \verb|fs_function()| & Fraser-Suzuki equation for a single peak \\
+		Fraser-Suzuki function & \verb|fs_mixture()| & Fraser-Suzuki mixture model equation \\
+		Fraser-Suzuki function & \verb|fs_model()| & Non-linear model implementation of Fraser-Suzuki mixture model \\
+		S3 method & \verb|print(<process>)| & Default print method for process object (derived from \verb|process()|) \\
+		S3 method & \verb|plot(<process>)| & Default plot method for process object (derived from \verb|process()|) \\
+		S3 method & \verb|print(<deconvolve>)| & Default print method for decon object (derived from \verb|deconvolve()|) \\
+		S3 method & \verb|plot(<deconvolve>)| & Default plot method for process object (derived from \verb|deconvolve()|) \\
+        		\bottomrule
+	\end{tabularx}
+\end{table}
+
+1. How robust is this (testing with Stacy’s data)
+show with a few samples
+- to show different machine
+- to show a variety of sample types
+how to include these in the manuscript?
+Discuss limitations of estimates
+how reliable are they?
+
+3.
+Mixture modelling is hard, with a large statistical literature.
+Google Geoff Maclachlan.
+He has written the seminal text Finite mixture models https://scholar.google.com/citations?user=1bYCHtsAAAAJ&hl=en
+-- add a bit of a discussion section at end.
+Discuss nature of statistical inference of mixture models.
+quite tricky in general
+ref paper slike McLachlan and Peele
+requires good starting points
+many combinations of peaks create the same overall curve
+to use the package well, different starting values should be tested out.
+
+4. Future work
+The package was developed using thermogravimetric data for 29 different wetland plant species, as well as pure samples of cellulose (carboxy-methyl cellulose) and lignin (alkali lignin from Sigma Aldrich).
+These data came from the same TGA-FTIR machine and were exported in the same format.
+For this reason, the package was also tested on thermogravimetric data exported from a different machine in a different format, on different species and plant parts in order to test behaviour of the package.
+
+Below we present results from
+
+add in discussion that happy to develop for data of other machines/in other formats
+
+tools that already exist
+mixtools
+how does my approach compare with traditional mixture model estimation?
+
+Statistical inference of mixture models
 
@@
 	\item[Name:] \url{https://github.com/smwindecker/mixchar/}
-	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
-	\item[Licence:] Open license under which the software is licensed.
-	\item[Date published:] dd/mm/yy
+	\item[Persistent identifier:] DOI:10.5281/zenodo.1343849 https://doi.org/10.5281/zenodo.1343849
+	\item[Licence:] MIT and open license as found on https://github.com/smwindecker/mixchar/releases/tag/v0.1.0.
+	\item[Date published:] 11/08/2018
 \end{description}
@@
 The authors would like to thank Dr.
-Nick Tierney for reviewing an early version of the package.
+Nick Tierney and David Wilkinson for reviewing an early version of the package.
 We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for assistance in the field collecting plant specimens.

### 2018-08-12 README.Rmd
add DOI badge
correct url for website articles

@@
 [![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
+
+[![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)
 
@@
 Below we will show a basic implementation of the package.
-For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/Background).
-You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar) or in the vignette that you can access via R by installing with the `build_vignettes` argument as follows:
+For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/mixchar/articles/Background.html).
+You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar/articles/mixchar.html) or in the vignette that you can access via R by installing with the `build_vignettes` argument as follows:
 

### 2018-08-12 README.Rmd
remove build_vignettes line that may be causing pandoc error

@@
 For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/mixchar/articles/Background.html).
-You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar/articles/mixchar.html) or in the vignette that you can access via R by installing with the `build_vignettes` argument as follows:
-
-```{r, eval = FALSE}
-devtools::install_github("smwindecker/mixchar", build_vignettes = TRUE)
-browseVignettes('mixchar')
-```
+You can also find a full worked example on the [website](http://smwindecker.github.io/mixchar/articles/mixchar.html).
 

### 2018-08-13 manuscript/manuscript.Rnw
revise operating system and CRAN notes

@@
 \section*{Operating system}
-The package can work with either Windows, Mac OS X, or Linux.
+The package was tested on Windows, Mac OS X, and Linux.
 
@@
 
-{\bf Archive} (e.g. institutional repository, general repository) (required – please see instructions on journal website for depositing archive copy of software in a suitable repository)
+{\bf Archive}
 
 \begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] The name of the archive.
+	\item[Name:] CRAN
 	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
@@
 	\item[Publisher:] Name of the person who deposited the software.
-	\item[Version published:] The version number of the software archived.
+	\item[Version published:] 0.1.0
 	\item[Date published:] dd/mm/yy
@@
 
-{\bf Code repository} GitHub
+{\bf Code repository}
 
 \begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] \url{https://github.com/smwindecker/mixchar/}
+	\item[Name:] Github \url{https://github.com/smwindecker/mixchar/}
 	\item[Persistent identifier:] DOI:10.5281/zenodo.1343849 https://doi.org/10.5281/zenodo.1343849

### 2018-08-15 tests/testthat/test-optimisation.R
remove empty test

@@ -1,11 +1,0 @@
-context("Test for non-linear optimisation")
-
-test_that("param_select function produces the same results with random seed set", {
-
-
-
-
-
-
-
-})

### 2018-08-15 tests/testthat/test-model_parameterisation.R
add test for fs_model

@@ -11,3 +11,30 @@ test_that("rmse returns correct value", {
   expect_equal(rmse(obs, pred), val)
 
 })
+
+test_that("model output correct", {
+
+  tmp <- process(juncus, init_mass = 18.96,
+                 temp = 'temp_C', mass_loss = 'mass_loss')
+
+  output <- deconvolve(tmp)
+  params <- model_parameters(output)
+  start_params <- c(height_1 = params[1,2], skew_1 = params[2,2],
+                    position_1 = params[3,2], width_1 = params[4,2],
+                    height_2 = params[5,2], skew_2 = params[6,2],
+                    position_2 = params[7,2], width_2 = params[8,2],
+                    height_3 = params[9,2], skew_3 = params[10,2],
+                    position_3 = params[11,2], width_3 = params[12,2])
+
+  lb <- c(0, -0.33, 0, 50,
+          0, -0.33, 290, 0,
+          0, -0.29, 330, 160)
+  ub <- c(2, 0.25, 280, 100,
+          2, 0.25, 380, 50,
+          2, 0.25, 430, 250)
+
+  fit <- fs_model(rate_data(tmp), start_params, lb, ub)
+
+  expect_equal(fs_model(rate_data(tmp), start_params, lb, ub), fit)
+
+})

### 2018-08-15 tests/testthat/test-fraser_suzuki.R
modify names of tests for fraser-suzuki functions

@@ -1,13 +1,13 @@
 context("Test for Fraser-Suzuki functions")
 
-test_that("function returns correct y value", {
+test_that("fs_function returns correct y value", {
 
   fxn_value <- fs_function(500, 10, .3, 600, 200)
   expect_equal(fxn_value, 3.75394, tolerance = 1e-3)
 
 })
 
-test_that("mixture works properly", {
+test_that("fs_mixture works properly", {
 
   fxn_value <- fs_mixture(500, .1, .3, 200, 100, .2, .25, 400, 60, .15, .26, 600, 200)
   expect_equal(fxn_value, 0.06263259)

### 2018-08-15 tests/testthat/test-component_weights.R
correct input names for test

@@ -26,8 +26,8 @@ test_that("correct weights returned", {
                height_3 = .15, skew_3 = .26, position_3 = 600, width_3 = 200,
                height_0 = .08, skew_0 = .22, position_0 = 180, width_0 = 150)
 
-  output3 <- list(n_curves = 3, bounds = c(120, 700))
-  output4 <- list(n_curves = 4, bounds = c(120, 700))
+  output3 <- list(n_peaks = 3, temp_bounds = c(120, 700))
+  output4 <- list(n_peaks = 4, temp_bounds = c(120, 700))
 
   expect_equal(get_weights(params3, output3), c(HC = 1096.957, CL = 1306.482, LG = 2603.153), tolerance = 1e-3)
   expect_equal(get_weights(params4, output4), c(HC_1 = 1155.978, HC_2 = 1096.957, CL = 1306.482, LG = 2603.153), tolerance = 1e-3)

### 2018-08-15 R/model_parameters.R
correct model parameters function and add test

@@ -14,6 +14,12 @@
 #' @export
 
 model_parameters <- function (object) {
-  fit <- object$model_fit
-  as.data.frame(summary(fit)$coefficients[,1])
+
+  params <- as.data.frame(summary(object$model_fit)$coefficients[,1])
+  colnames(params) <- 'parameter_value'
+  params$parameter_name <- row.names(params)
+  row.names(params) <- c()
+  params <- params[,c(2,1)]
+
+  params
 }

### 2018-08-15 tests/testthat/test-accessor_functions.R

@@ -3,16 +3,20 @@ context("Test for accessor functions")
 test_that("accessor functions return correct values", {
 
   data(juncus)
-  tmp <- process(juncus, 'temp_C', 'mass_loss', 18.96)
+  tmp <- process(juncus, 18.96, 'temp_C', mass_loss = 'mass_loss')
   output <- deconvolve(tmp, lower_temp = 130, upper_temp = 660)
 
-  expect_equal(temp_bounds(output), output$bounds)
+  expect_equal(temp_bounds(output), output$temp_bounds)
   expect_identical(rate_data(tmp), tmp$data)
   expect_identical(model_fit(tmp), tmp$minpack.lm)
   expect_identical(component_weights(output), output$weights)
 
-
   params <- as.data.frame(summary(output$model_fit)$coefficients[,1])
+  colnames(params) <- 'parameter_value'
+  params$parameter_name <- row.names(params)
+  row.names(params) <- c()
+  params <- params[,c(2,1)]
+
   expect_identical(model_parameters(output), params)
 
 })

### 2018-08-15 README.Rmd
ensure badges all appear right placement

@@
 [![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
-
 [![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)
@@
 
-Below we will show a basic implementation of the package.
-For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/mixchar/articles/Background.html).
-You can also find a full worked example on the [website](http://smwindecker.github.io/mixchar/articles/mixchar.html).
+Below we will show a basic implementation of the package. For a detailed step by step workflow, see the [workflow vignette on the website](http://smwindecker.github.io/mixchar/articles/mixchar.html).
+
+For a detailed discussion of the methodology, please see the [methodology vignette on the website](http://smwindecker.github.io/mixchar/articles/Background.html).
 

### 2018-08-15 R/deconvolve.R
correct example that was causing error in .Md file

@@ -23,8 +23,8 @@
 #'                temp = 'temp_C', mass_loss = 'mass_loss')
 #' output <- deconvolve(tmp)
 #' my_starting_vec <- c(height_1 = 0.003, skew_1 = -0.15, position_1 = 250, width_1 = 50,
-#                       height_2 = 0.006, skew_2 = -0.15, position_2 = 320, width_2 = 30,
-#                       height_3 = 0.001, skew_3 = -0.15, position_3 = 390, width_3 = 200)
+#'                      height_2 = 0.006, skew_2 = -0.15, position_2 = 320, width_2 = 30,
+#'                      height_3 = 0.001, skew_3 = -0.15, position_3 = 390, width_3 = 200)
 #' output <- deconvolve(tmp, n_peaks = 3, start_vec = my_starting_vec)
 #' }
 #' @export
@@ -145,3 +145,4 @@ deconvolve <- function (process_object,
   decon_output
 
 }
+

### 2018-08-15 manuscript/manuscript.Rnw
add stt examples

@@
 After we've loaded our data, we need to calculate the rate of mass loss by taking the derivative.
-The \verb|process| function needs the dataset, the initial mass of sample, the name of the temperature data column, and the name of the mass column (mg).
+The \verb|process| function needs the dataset, the initial mass of sample, the name of the temperature data column, and the name of the mass column (mg), which can be specified either as mass loss data with the \verb|mass_loss| argument or as mass data with the \verb|mass| argument.
 
@@
 The output of the \verb|process| function is a list of three items: the modified dataframe including the derivative thermogravimetric rate of mass loss data (DTG), the initial mass value that was supplied, and the maximum and minimum temperature of values in the data.
-Plotting this output will results in two curves: the mass of sample across temperature and the rate of mass loss curve (Fig.~\ref{Fig:rateloss}).
-The rate of mass loss curve is a multi-peaked curve encompassing three main phases \citep{orfao2001}:
+Plotting this output results in two curves: the mass of sample across temperature and the rate of mass loss (Fig.~\ref{Fig:rateloss}).
+The rate of mass loss is a multi-peaked curve encompassing three main phases \citep{orfao2001}:
 
@@
 Lignin typically decays beginning at a high temperature and over a wide interval \citep{chen2015}, so position and width began at 410 and 200, respectively.
-These starting values can also be modified in the \verb|deconvolve| function with the \verb|start_vec|, \verb|lower_vec|, and \verb|upper_vec| arguments.
+Default starting values were tested on litter from 30 plant species, encompassing herbaceous, graminoid, as well as woody species.
+However, they can also be modified with the \verb|start_vec|, \verb|lower_vec|, and \verb|upper_vec| arguments if needed.
 
@@
 \\
+
+<<>>=
+output_juncus <- deconvolve(deriv_juncus)
+output_juncus
+@
 
@@
 
-<<>>=
-output_juncus <- deconvolve(deriv_juncus)
-output_juncus
-@
-
-The output of the \verb|deconvolve| function is a list of five items:
+\textbf{\textit{Package outputs}}\\
+The output of the \verb|deconvolve| function is a list of five items that can be retrieved with accessor functions:
 \begin{enumerate}
-\item{the data used to fit the function,
+\item{the processed dataset that results from the \verb|process| function, useful if for playing around with other modelling approaches or plotting options, and accessed with \verb|rate_data()|:
 <<>>=
@@
 }
-\item{the upper and lower temperature bounds to which the data were cropped,
+\item{the temperature values at which the data were cropped for analysis, accessed with \verb|temp_bounds()|:
 <<>>=
@@
 }
-\item{the model fit including parameter estimates,
+\item{the output of the mixture model and estimated parameter values for height, skew, position, and width for each peak.
+Peak 1 is hemicellulose, peak 2 is cellulose, and peak 3 is lignin.
+If present, the optional fourth peak located at the lowest temperature interval will be listed as peak 0.
+Accessed with \verb|model_fit()|:
 <<eval = FALSE>>=
@@
 }
-\item{the number of peaks,
+\item{the number of peaks:
 <<>>=
@@
 }
-\item{and the mean, 2.5\% and 97.5\% estimates, median, and standard deviation of the weight of each component.
+\item{and the mean, 2.5\% and 97.5\% estimates, median, and standard deviation of the weight of each component that can be accessed with \verb|component_weights()|:
 <<>>=
@@
 \end{enumerate}
-If you \verb|plot()| the output of the \verb|deconvolve| function you will see the result of the deconvolution (Fig.~\ref{Fig:decon}).
-This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components peaks.
+
+Plotting the output of the \verb|deconvolve| function shows the underlying DTG data, the overall mixture model curve, as well as the components peaksof the deconvolution (Fig.~\ref{Fig:decon}).
 The default plot is in black and white, but you can plot a colour version that uses colour-blind friendly \verb|viridis| colours \citep{viridis} by specifying \verb|bw = FALSE|.
@@
 
-The Fraser-Suzuki family of functions are exported to allow users to create their own plots from the model outputs. Detailed descriptions of how to do so are included in the package vignettes.
+The Fraser-Suzuki family of functions are exported to allow users to create their own plots from the model outputs. You can use these in conjunction with the parameter estimates, accessed as follows:
 
 <<>>=
-stt <- read.table("../mixchar.notes/USATtLeaf_data.txt", fill = TRUE, header = FALSE, skip = 46, skipNul = TRUE, fileEncoding="UTF-16LE")
-colnames(stt) <- c("time", "temp", "weight", "deriv")
+juncus_parameters <- model_parameters(output_juncus)
 @
@@
 
+The package was developed using thermogravimetric data for 29 different wetland plant species, as well as pure samples of cellulose (carboxy-methyl cellulose) and lignin (alkali lignin from Sigma Aldrich).
+These data came from the same TGA-FTIR machine and were exported in the same format.
+For this reason, the package was also tested on thermogravimetric data exported from a different machine in a different format, on different species and plant parts in order to test behaviour of the package.
 1. How robust is this (testing with Stacy’s data)
@@
 
-3.
-Mixture modelling is hard, with a large statistical literature.
-Google Geoff Maclachlan.
-He has written the seminal text Finite mixture models https://scholar.google.com/citations?user=1bYCHtsAAAAJ&hl=en
--- add a bit of a discussion section at end.
-Discuss nature of statistical inference of mixture models.
-quite tricky in general
-ref paper slike McLachlan and Peele
-requires good starting points
-many combinations of peaks create the same overall curve
-to use the package well, different starting values should be tested out.
+\section*{Quality control}
+Something about passing CRAN check with no errors or warnings, or notes.
 
-4. Future work
-The package was developed using thermogravimetric data for 29 different wetland plant species, as well as pure samples of cellulose (carboxy-methyl cellulose) and lignin (alkali lignin from Sigma Aldrich).
-These data came from the same TGA-FTIR machine and were exported in the same format.
-For this reason, the package was also tested on thermogravimetric data exported from a different machine in a different format, on different species and plant parts in order to test behaviour of the package.
+All the functions of \verb|mixchar| were tested to see if they produced the desired output.
+The workflow was tested on thermogravimetric data from two different TGA-FTIR machines, and on samples outside those used to build the package.
 
-Below we present results from
+\textit{Seagrass blade}
+<<echo = FALSE>>=
+source('stt_analysis.R')
+sg_leaf <- process_data('data/seagrass_leaf.txt')
+@
 
-add in discussion that happy to develop for data of other machines/in other formats
+after loading the data, and using the process function, we can inspect the plots:
+<<>>=
+plot(sg_leaf)
+@
 
-tools that already exist
-mixtools
-how does my approach compare with traditional mixture model estimation?
+we can determine that this sample needs a fourth peak, and the lower and upper bounds modified.
+<<>>=
+sg_out <- deconvolve(sg_leaf,
+                     n_peaks = 4,
+                     lower_temp = 150,
+                     upper_temp = 600)
+plot(sg_out, bw = FALSE)
+@
+the outcome looks good.
 
-Statistical inference of mixture models
+\textit{Seagrass rhizome}
+similarly needed 4 peaks specified and bounds.
+<<echo = FALSE>>=
+sg_rhiz <- process_data('data/seagrass_rhizome.txt')
+@
 
-\section*{Quality control}
-All the functions of \verb|mixchar| were tested to see if they produced the desired output.
+<<>>=
+sg_rh_out <- deconvolve(sg_rhiz,
+                        n_peaks = 4,
+                        lower_temp = 150,
+                        upper_temp = 600)
+plot(sg_rh_out, bw = FALSE)
+@
+
+\textit{Seagrass root}
+<<echo = FALSE>>=
+sg_root <- process_data('data/seagrass_root.txt')
+@
+
+<<>>=
+sg_root_out <- deconvolve(sg_root,
+                          lower_temp = 150,
+                          upper_temp = 600)
+plot(sg_root_out, bw = FALSE)
+@
+
+\textit{Macroalgae}
+<<echo = FALSE>>=
+ma_leaf <- process_data('data/macroalgae_leaf.txt')
+@
+
+<<>>=
+plot(ma_leaf)
+@
+
+<<>>=
+start_vec <- c(0.002, -0.15, 250, 50,
+               0.003, -0.15, 310, 50,
+               0.006, -0.15, 350, 30,
+               0.001, -0.15, 410, 200)
+ub <- c(2, 0.2, 260, 80,
+        2, 0.2, 330, 90,
+        2, 0.2, 380, 50,
+        2, 0.2, 430, 250)
+ma_out <- deconvolve(ma_leaf,
+                     n_peaks = 4,
+                     start_vec = start_vec,
+                     upper_vec = ub,
+                     lower_temp = 150,
+                     upper_temp = 600)
+plot(ma_out, bw = FALSE)
+@
 
@@
 
+3.
+Mixture modelling is hard, with a large statistical literature.
+Google Geoff Maclachlan.
+He has written the seminal text Finite mixture models https://scholar.google.com/citations?user=1bYCHtsAAAAJ&hl=en
+-- add a bit of a discussion section at end.
+Discuss nature of statistical inference of mixture models.
+quite tricky in general
+ref paper slike McLachlan and Peele
+requires good starting points
+many combinations of peaks create the same overall curve
+to use the package well, different starting values should be tested out.
+
 For those that wish to contribute to the package, it is hosted on Github.
-Contributors can log issues via the issues tracker (\url{https://github.com/smwindecker/mixchar/issues}) or submit a pull request to add functionality to the package.
+Contributors can log issues, for example with alternative data foramts, via the issues tracker (\url{https://github.com/smwindecker/mixchar/issues}) or submit a pull request to add functionality to the package.
 
@@
 The authors would like to thank Dr.
-Nick Tierney and David Wilkinson for reviewing an early version of the package.
+Nick Tierney and David Wilkinson for reviewing an early version of the package as well as CRAN reviewers for useful additions.
 We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for assistance in the field collecting plant specimens.

### 2018-08-15 manuscript/stt_analysis.R

@@ -1,0 +1,24 @@
+
+# assuming all your data is in the same format
+process_data <- function (file) {
+
+  # this is the line you're already familiar with that reads in your data
+  df <- read.table(file, fill = TRUE, header = FALSE, skip = 46,
+                   skipNul = TRUE, fileEncoding="UTF-16LE")
+
+  # assigns column names
+  colnames(df) <- c("time", "temp", "weight", "deriv")
+
+  # It looks like the initial mass is stored on line 12, so this line just
+  # reads that so it can be passed into the next function automatically
+  init_mass <- read.table(file, nrows = 1, fill = TRUE, header = FALSE, skip = 11,
+                          skipNul = TRUE, fileEncoding="UTF-16LE")[,2]
+
+  # process data given the initial mass, and column names given
+  tmp <- mixchar::process(df, init_mass = init_mass,
+                          temp = 'temp',
+                          mass = 'weight')
+
+  # return this object
+  tmp
+}

### 2018-08-16 README.Rmd
add cran badge

@@
 [![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)
+[![](http://www.r-pkg.org/badges/version/mixchar)
 

### 2018-08-18 README.Rmd
devel version. add cran install to readme

--- 2018-08-15 README.Rmd
@@
 
+[![CRAN](http://www.r-pkg.org/badges/version/mixchar)
 [![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
@@
 
-You can install `mixchar` from [GitHub](https://github.com/) with:
+You can install `mixchar` by:
+
+```{r, eval = FALSE}
+install.packages("mixchar")
+```
+
+or install the development version from [GitHub](https://github.com/) with:
 

### 2018-08-18 R/weight_quantiles.R
name sd output column

@@ -64,6 +64,7 @@ weight_quantiles <- function (output, seed) {
   all_weights <- rbind(means, CI_df, sd)
   all_weights$value_type <- row.names(all_weights)
   all_weights$value_type[all_weights$value_type == 1] <- 'mean'
+  all_weights$value_type[all_weights$value_type == 5] <- 'sd'
 
   rownames(all_weights) <- c()
 

### 2018-10-02 manuscript/manuscript.Rmd
updated manuscript

---
title: "markdown_test_man"
author: "Saras Windecker"
date: "17/09/2018"
output: 
  pdf_document:
    template: jors_template.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2018-10-02 manuscript/manuscript.Rnw
updated manuscript

--- 2018-08-13 manuscript/manuscript.Rnw
@@
 \captionsetup{justification=raggedright, singlelinecheck=false}
-
-\usepackage{pgfplots}
-\pgfplotsset{compat=1.16}
-\pgfplotsset{width=16cm}
+%
+% \usepackage{pgfplots}
+% \pgfplotsset{compat=1.16}
+% \pgfplotsset{width=16cm}
 
@@
 \section*{Abstract}
-
-Importance of cell walls in ecosystems. characterisation is important in ecosystem and functional ecology because cell wall carbon makes up XXX of soil C.
-
-Proportions of the primary carbon types are useful for estimating kinetic decay parameters or for calculation of intrinsic plant traits.
-Traditional methods for calculation of these components involve wet chemistry methods that can be monetarily and environmentally costly.
-Thermogravimetric analysis is an alternative method, already in use in the biofuel field, that involves pyrolysing dry, ground plant litter and estimating components from resulting mass decay peaks.
-Since different carbon types break down relatively independently during different temperature phases, we can separate the multi-peaked rate of mass loss curve into constituent parts using a mixture model.
-This package conducts this peak separation analysis in a open-source and reproducible way using R.
-This methodology has been tested on a range of plant litter composed primarily of soluble carbohydrates, hemicellulose, cellulose, and lignin.
+Plant cell wall biomass is composed of a range of different types of carbon.
+Estimating the proportions of the primary carbon types affects how cell walls decompose, an important part of the ecosystem because their decay contributes to soil carbon.
+Traditional methods of calculating these components involve wet chemistry methods that can be costly and degrade the environment.
+Thermogravimetric analysis is an alternative method, already used by biofuel researchers, that involves pyrolysing dry, ground plant litter and estimating contribution of carbon components from resulting mass decay curve.
+Because carbon types break down relatively independently, we can apply a mixture model to the multi-peaked rate of mass loss curve to identify mass loss of each carbon component.
+The \verb|mixchar| package conducts this peak separation analysis in an open-source and reproducible way using R.
+\verb|mixchar| has been tested over a range of plant litter types, composed primarily of the soluble carbohydrates: hemicellulose, cellulose, and lignin.
 
@@
 \section*{Introduction}
-
-Plant cell wall biomass is composed of a range of different types of carbon.
-
-i think you've moved quite quickly through a range of ideas in this one sentence: multiple components, components matter, composition differs between species, composition effects on ecosystem.
-I'd say that these proportions influence precesses like energy release under combustion and decomposition of litter.
-Biomass carbon in different plant species may vary in their composition of these compounds, with flow on effects on litter decomposition where various species occur.
-
-Ecologists can use these proportions of biomass carbon to make generalisations about species' effects on ecosystem processes such as litter decomposition, which links plant biomass to the global carbon cycle \citep{cornwell2008}.
-Biofuels researchers use proportions of biomass carbon types to estimate kinetic decay parameters of species' tissue \citep{chen2017,orfao2001,hu2016}.
-Traditional methods for calculation of lignocellulosic biomass involve wet chemistry assays for carbon component analysis \citep{fengel}, which are time-consuming and adversely impact the environment through use of sulfuric acid and acetic anhydride, among other chemicals.
-Thermogravimetric analysis (TGA) is an alternative method, already in use among biofuels researchers, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in an $N_2$ environment, termed pyrolysis).
+Plant cell wall biomass is composed of a range of different types of carbon \citep{chen2017,orfao2001,hu2016}.
+We can use the relative proportion of these carbon components to understand species characteristics, such as litter decomposition \citep{cornwell2008}.
+Traditional methods for calculating lignocellulosic biomass involve wet chemistry assays for carbon component analysis \citep{fengel} through the use of sulfuric acid and acetic anhydride, among other chemicals.
+These chemicals, however, can adversely impact the environment.
+Thermogravimetric analysis (TGA) is an alternative method, already in use among biofuel researchers, to approximate these carbon compounds.
+In this method, we use mass loss data obtained by heating a biomass sample (in an $N_2$ environment, termed pyrolysis) to estimate the different carbon components.
 \\
 \\
-Mass loss during pyrolysis can be regarded as the sum of the degradation of the main components of the sample \textemdash often simplified as hemicelluloses, cellulose, and lignin \citep{hu2016,cheng2015,perejon2011,orfao2001,muller-hagedorn2007}.
-Therefore, the multi-peaked rate of mass loss curve can be mathematically separated into constituent parts with a mixture model \textemdash termed deconvolution.
-XXXXXXX add mixture model citations here.
-The component peaks identified by the mixture model represent the proportion of initial mass of each component lost over time.
+Mass loss during complete pyrolysis can be regarded as the sum of the degradation of the main components of the sample, often simplified to the three main components: hemicelluloses, cellulose, and lignin \citep{hu2016,cheng2015,perejon2011,orfao2001,muller-hagedorn2007}.
+The rate of mass loss is generally a multi-peaked curve, that can then be mathematically separated into its constituent parts with a mixture model, in a process termed `deconvolution' \citep{mclachlan2000,kauppinen1981}.
+The component peaks identified by the mixture model represent the proportion of initial mass of each component lost during pyrolysis.
 The integral, or area under the peak, therefore gives us an estimate of the proportion of that component in the overall sample.
-Thermogravimetric analysis with deconvolution has been validated by studies comparing estimates to wet chemistry measurements \citep{yang2006}.
-Plant trait measurement is guided by the principle of standardised, widely reproducible methods \citep{perez-harguindeguy2013}, but much of the published literature use commercial software to deconvolve the rate of mass loss curve \citetext{for example OriginPro \citealp{chen2017}, PeakFit \citealp{perejon2011}, Fityk \citealp{perejon2011}, or Datafit \citealp{cheng2015}}.
-Proprietary software inhibits researchers already conducting this type of analysis from making their analyses independently reproducible.
-Software accessibility and reproducibility may be one reason why thermogravimetric analysis for carbon type estimation has not yet been widely adopted by functional ecologists, despite being previously used to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucalyptus trees \citealp{orfao2001}}.
+A number of studies have validated this approach, using thermogravimetric analysis with deconvolution, with studies comparing its estimates of carbon components to those achieved with wet chemistry measurements \citep{yang2006}.
+Other researchers have also previously used this method to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucalyptus trees \citealp{orfao2001}}.
 \\
 \\
-The \verb|mixchar| package provides an open-source set of functions to perform this deconvolution.
-Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, \verb|mixchar| provides specific guidelines related to thermal decay curve analysis and carbon component estimation.
-Detailed vignettes and several default plotting options are included in order to maximise utility and ease of uptake for researchers interested in this method.
+For the most part, researchers have used commercial software to deconvolve the rate of mass loss curve \citetext{for example OriginPro \citealp{chen2017}, PeakFit \citealp{perejon2011}, Fityk \citealp{perejon2011}, or Datafit \citealp{cheng2015}}.
+The majority of proprietary software employ point-and-click interfaces that prevent independent replication of the deconvolution analysis.
+The inability of other researchers to reproduce readily another's experimental results using this software, a guiding principle of functional trait measurement \citep{perez-harguindeguy2013}, might in part explain why thermogravimetric analysis has not been widely adopted by functional ecologists.\\
+\\
+The \verb|mixchar| package in R is an open-source tool for the deconvolution of thermal decay curves from thermogravimetric analysis.
+Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, our \verb|mixchar| package provides specific guidelines for using thermal decay curve analysis to estimate carbon components.
+Detailed vignettes and several default plotting options are included in \verb|mixchar| so that researchers interested to adopt this method can easily and readily do so for the purpose of estimating carbon components in plant biomass samples.
 
@@
 \textbf{\textit{Litter collection and preparation}}\\
-We developed and tested the functions in this package using the thermogravimetric decay data for litter of 29 different plant species.
-Two species from this set are available as datasets in the package \textemdash the freshwater reed \textit{Juncus amabilis} (accessed as \verb|juncus|) and the freshwater fern \textit{Marsilea drumondii} (accessed as \verb|marsilea|).
-To ensure component estimates are an accurate representation of the original composition of the litter, it is important to dry samples as quickly as possible to prevent decomposition.
-Plant litter collected for this analysis was placed in moist plastic bags and stored in dark coolers until transported to the lab, and then moved to a dark, refrigerated room.
-We dried the fresh litter at 60 $^{\circ}$C for 72 hours and ground litter to \textless $40 \mu m$ using a Retsch Centrifugal Mill ZM200.
+We collected the litter for development of this package from three freshwater wetlands surrounding Melbourne, Victoria (sites within 60 km of -37.455, 144.985).
+We then dried the samples as quickly as possible after collection to ensure our component estimates were an accurate representation of the original composition of the litter samples we collected.
+In the field, we placed the plant litter collected for this analysis in moist plastic bags and stored them in dark coolers until we could transport them to the lab where they were promptly dried at 60 $^{\circ}$C for 72 hours.
+We ground our dry litter to \textless $40 \mu m$ using a Retsch Centrifugal Mill ZM200.
 \\
 \\
-We pyrolysed 10\textendash20 mg subsamles of dry, ground litter in an N$_2$ environment from 30\textendash800 $^{\circ}$C at a temperature ramp of 10 $^{\circ}$C/min using a Netzsch TGA-FTIR thermogravimetric analyser (Department of Biomedical Engineering, University of Melbourne).
-The resulting data is mass loss (mg) against temperature (Fig.~\ref{Fig:massloss}).
+We pyrolysed 10\textendash20 mg subsamples of dry, ground litter in an N$_2$ environment from 30\textendash800 $^{\circ}$C at a temperature ramp of 10 $^{\circ}$C/min using a Netzsch TGA-FTIR thermogravimetric analyser (Department of Biomedical Engineering, University of Melbourne).
+\\
+\\
+We developed and tested the functions of our \verb|mixchar| package using the thermogravimetric decay data of the litter of 29 different plant species.
+Two species from our data are available as datasets in the package \textemdash the freshwater reed \textit{Juncus amabilis} (accessed as \verb|juncus|) and the freshwater fern \textit{Marsilea drumondii} (accessed as \verb|marsilea|).
+The data resulting from the pyrolysis is mass loss (mg) against temperature (Fig.~\ref{Fig:massloss}).
 
@@
 
-<<echo = FALSE, fig.cap = '\\label{Fig:massloss} Mass across temperature \\textit{Juncus amabilis}.', out.width = '.49\\linewidth'>>=
+<<echo = FALSE, fig.cap = '\\label{Fig:massloss} Mass across temperature \\textit{Juncus amabilis}.', out.width = '.6\\linewidth', fig.align = 'center'>>=
 tmp <- process(juncus, init_mass = 18.96,
                temp = 'temp_C', mass_loss = 'mass_loss')
-plot(tmp, plot_type = 'mass')
+plot(tmp, plot_type = 'mass', cex = 1.5)
 @
 
-\textbf{\textit{Deconvolution}}\\
+\textbf{\textit{Deconvolution using mixchar}}\\
 \textit{Rate of mass loss}\\
-After we've loaded our data, we need to calculate the rate of mass loss by taking the derivative.
-The \verb|process| function needs the dataset, the initial mass of sample, the name of the temperature data column, and the name of the mass column (mg).
+After completing the thermogravimetric analysis, the resulting data can be loaded into R.
+Using \verb|mixchar|, the \verb|process| function calculates the rate of mass loss by taking the derivative of mass loss over temperature data.
+To do so, \verb|process()| needs the dataset, the initial mass of the sample, the name of the temperature data column, and the name of the mass column (mg).
+The mass column can be specified either as mass loss data with the \verb|mass_loss| argument or as mass data with the \verb|mass| argument (since TGA-FITR machines can export data in either form).
 
@@
 
-The output of the \verb|process| function is a list of three items: the modified dataframe including the derivative thermogravimetric rate of mass loss data (DTG), the initial mass value that was supplied, and the maximum and minimum temperature of values in the data.
-Plotting this output will results in two curves: the mass of sample across temperature and the rate of mass loss curve (Fig.~\ref{Fig:rateloss}).
-The rate of mass loss curve is a multi-peaked curve encompassing three main phases \citep{orfao2001}:
+The \verb|process| function produces the modified dataframe, which includes the derivative thermogravimetric rate of mass loss data (DTG), the initial mass value that was supplied, and the maximum and minimum temperature values in the data.
+Plotting the output of the \verb|process| function yields the mass of sample across temperature curve (Fig.~\ref{Fig:massloss}) and the rate of mass loss curve (Fig.~\ref{Fig:rateloss}).
+The rate of mass loss is a multi-peaked curve encompassing three main phases \citep{orfao2001}:
 
@@
 	\item A wide mid-range of high mass loss, caused by devolatilisation of primary biomass carbon components, between approximately 120\textendash650 $^{\circ}$C.
-	\item A final period of little mass loss when carbonaceous material associated with the inorganic fraction decomposes, after approximately 650 $^{\circ}$C.
+	\item A final period of little mass loss when carbonaceous material associated with the inorganic fraction combusts, after approximately 650 $^{\circ}$C.
 \end{enumerate}
@@
 <<echo = FALSE, fig.cap = '\\label{Fig:rateloss} Derivative thermogravimetric rate of mass loss across temperature, scaled by initial mass of sample for \\textit{Juncus amabilis}.
-Line segments 1, 2, and 3 on represent mass loss phases.', out.width = '.49\\linewidth'>>=
-plot(deriv_juncus, plot_type = 'rate')
+Line segments 1, 2, and 3 represent mass loss phases.', out.width = '.6\\linewidth', fig.align = 'center'>>=
+plot(deriv_juncus, plot_type = 'rate', cex = 1.5)
 segments(x0 = 40, y0 = 0.0018, x1 = 40, y1 = 0.002, lwd = 3, col = 'darkgrey')
@@
 
-\textit{Crop DTG data}\\
-Since the overall DTG curve thus represents the loss of extractives, water, inorganic matter, and volatiles in addition to our components of interest \citep{hu2016}, we isolate mass loss from our primary biomass components by cropping the DTG data to Phase 2 (120\textendash650 $^{\circ}$C).
-The \verb|deconvolve| function defaults to cropping at 120 $^{\circ}$C and 700 $^{\circ}$C, but these can be modified with the \verb|lower_temp| and \verb|upper_temp| arguments.\\
+\textit{Subset DTG data}\\
+Since the overall DTG curve represents the loss of extractives, water, inorganic matter, and volatiles in addition to the components in which we are interested \citep{hu2016}, we isolate mass loss from our primary biomass components by subsetting the DTG data to Phase 2.
+The \verb|deconvolve| function defaults to temperature bounds at 120 $^{\circ}$C and 700 $^{\circ}$C, but these can be modified with the \verb|lower_temp| and \verb|upper_temp| arguments.\\
 \\
 \textit{Non-linear mixture model}\\
-Biomass components decompose relatively independently because they do not interact much during thermal volatilisation \citep{yang2006}.
-Therefore, the cropped DTG curve can be mathematically deconvolved into constituent parts using a mixture model.
+Biomass components combust relatively independently because they do not interact very much during thermal volatilisation \citep{yang2006}.
+Therefore, the subsetted DTG curve can be mathematically deconvolved into constituent parts using a mixture model.
 The derivative rate of mass loss equation ($\frac{dm}{dT}$) can be expressed as the sum of $n$ independent reactions (Eq.~\ref{eqn:mixture_model}), as follows \citep{orfao2001}:
@@
 \\
-Although most of our results can be described with only $n = 3$ peaks, corresponding to a single peak each of hemicelluose, cellulose, and lignin, some litter samples yield a second hemicellulose peak at a lower temperature, resulting in $n = 4$ independent peaks.
+Although the carbon distribution of many species can be described with only $n = 3$ peaks, corresponding to a single peak for each of hemicelluose, cellulose, and lignin, some litter samples yield a second hemicellulose peak at a lower temperature, resulting in $n = 4$ independent peaks.
 This is because the soluble carbohydrates in plant tissue can take many forms, including xylan, amylose, etc., which apparently degrade at different temperatures \citep[see also][]{chen2017,muller-hagedorn2007}.
-\verb|deconvolve| will decide whether three or four peaks are best using an internal function that determines if there is a peak below 220 $^{\circ}$C.
-Upon inspection of your curve you can override this by specifying the \verb|n_peaks| argument.\\
+\verb|deconvolve()| will decide whether three or four peaks are best using an internal function that determines if there is a peak below 220 $^{\circ}$C.
+Alternatively, upon inspection of the curve, we can specify manually the number of peaks with the \verb|n_peaks| argument.\\
 \\
-In order to fit the mixture model, we must determine the shape of the individual peaks ($\frac{d\alpha_{i}}{dT}$) that are summed to produce it.
+In order to fit the mixture model to the data, we must decide upon the shape of the individual peaks ($\frac{d\alpha_{i}}{dT}$) that are summed to produce it.
 Many different functions have been proposed: the asymmetric bi-Gaussian \citep{sun2015}, logistic \citep{barbadillo2007}, Weibull \citep{cai2007}, asymmetric double sigmoidal \citep{chen2017}, and the Fraser-Suzuki function \citep{perejon2011,hu2016}.
-Comparisons of several techniques \citep{svoboda2013,perejon2011,cheng2015} found that the Fraser-Suzuki function best fit these kinetic peaks, since it allows for asymmetry (a parametric examination of the Fraser-Suzuki function can be found in Fig.~\ref{Fig:fs_simulation}).
+Researchers have compared several techniques \citep{svoboda2013,perejon2011,cheng2015} and found that the Fraser-Suzuki function best fit these kinetic peaks.
+This is because the Fraser-Suzuki function allows for asymmetry (a parametric examination of the Fraser-Suzuki function can be found in Fig.~\ref{Fig:fs_simulation}).
 We therefore use the Fraser-Suzuki function to describe the rate expression of a single peak (Eq.~\ref{eqn:fs_function}) as follows:
@@
 
-where T is temperature ($^\circ$C), and the parameters $h_i$ ($^{\circ}$C^{-1}), $s_i$, $p_i$ ($^{\circ}$C), and $w_i$ ($^{\circ}$C) are height, skew, position, and width of the peak, respectively.
-In total, our model estimates 12 or 16 parameters, one for each parameter of Eq.~\ref{eqn:fs_function} for either 3 or 4 primary components.
+where T is temperature ($^\circ$C), and the parameters $h_i$ ($^{\circ}C^{-1}$), $s_i$, $p_i$ ($^{\circ}$C), and $w_i$ ($^{\circ}$C) are height, skew, position, and width of the peak, respectively.
+In total, our model estimates 12 or 16 parameters, one for each parameter of Eq.~\ref{eqn:fs_function} for either three or four primary components.
 
-<<echo = FALSE, fig.cap = '\\label{Fig:fs_simulation} Parametric study of the Fraser-Suzuki function for deconvolution of derivative thermogravimetric biomass curves: (a) Effect of modifying height; (b) skew; (c) position; and (d) width.', out.width = '\\linewidth', fig.asp = 1>>=
+<<echo = FALSE, fig.cap = '\\label{Fig:fs_simulation} Parametric study of the Fraser-Suzuki function for deconvolution of derivative thermogravimetric biomass curves: Effect of modifying (a) height; (b) skew; (c) position; and (d) width.', out.width = '\\linewidth', fig.asp = 1>>=
 legend_subfig <- function (subfig) {
@@
 
-\verb|deconvolve| uses non-linear optimisation with residual sum of squares to fit the rate expression \citetext{as in \citealp{cheng2015}}.
-Starting values for all parameters were selected based on curves depicted in the literature \citep{muller-hagedorn2007} and from the results of running an identical deconvolution on pure cellulose and lignin samples.
-Hemicelluloses decay in a reasonably narrow band beginning at a lower temperature \citep{muller-hagedorn2007}, so we used 270 for position and 50 for width.
-Linear cellulose crystals decay at a higher temperature, but decay more rapidly after peak temperatures are reached, so starting position was set to 310 and width to 30.
-Lignin typically decays beginning at a high temperature and over a wide interval \citep{chen2015}, so position and width began at 410 and 200, respectively.
-These starting values can also be modified in the \verb|deconvolve| function with the \verb|start_vec|, \verb|lower_vec|, and \verb|upper_vec| arguments.
+Likelihood functions in mixture models have multiple maxima, and therefore\\
+expectation-maximisation algorithms are highly dependent on starting value selection \citep{seidel2000a,seidel2000b}.
+The vector of starting values for the 12 or 16 estimated parameters is based on curves depicted in the literature \citep{muller-hagedorn2007} and from the results of running an identical deconvolution on pure cellulose (carboxy-methyl cellulose) and lignin (alkali lignin from Sigma Aldrich).
+Hemicelluloses decay in a reasonably narrow band beginning at a lower temperature \citep{muller-hagedorn2007}, so we use 270 for position and 50 for width.
+Linear cellulose crystals decay at a higher temperature, but decay more rapidly after peak temperatures are reached, so we set its starting position to 310 and width to 30.
+Lignin typically decays beginning at a high temperature and over a wide interval \citep{chen2015}, so we begin position and width at 410 and 200, respectively.
+\\
+\\
+In an effort to ensure the same starting vector would be useful across a wide variety of different samples, we employ an extra optimisation step before fitting the model.
+The \verb|deconvolve| function first optimises the given starting value vector with 300 restarts of the \verb|NLOPTR_LN_BOBYQA| algorithm \citep{bobyqa} with the \verb|nloptr| \citep{nloptr} package.
+In this way, we can set the given starting value vector so that it works properly on a wide range of samples, and at the same time the starting values we ultimately give to the model are as close as possible to the global maxima for a given dataset.
+\\
+\\
+To fit the non-linear mixture model, we send the optimised starting value vector to the \verb|nlsLM()| function in the \verb|minpack.lm| \citep{minpack.lm} package, which uses the Levenberg-Marquardt algorithm to minimise residual sum of squares.\\
+\\
+The default starting values and two-stage optimisation worked well for our thermogravimetric decay dataset for 29 plant species, encompassing herbaceous, graminoid, as well as woody species.
+Although this result is encouraging it is not altogether surprising because these data were pyrolysed using the same TGA-FTIR machine.
+For this reason, the package was also tested on thermogravimetric data processed from a different machine, including for different species and plant parts.
+Default settings produce well-fit curves for leaf samples from the seagrass species \textit{Thalassia testudinum}, and rhizome and root samples from the seagrass species \textit{Zostera marina} \citetext{Fig.~\ref{Fig:stt_examples}; data for both from \citealp{trevathan-tackett2017}}.\\
 
-Mixture modelling is hard, and very sensitive to  starting values.
-therefore one needs good starting values for the non-kinear mxture model step.
-but one cannt just give a all round set of these.
-instead by intersting a good routine to find good starting values, we use an optimisation.
+<<echo = FALSE>>=
+source('process_test_samples.R')
+@
 
-These initial starting values are optimised before model fitting using the \verb|NLOPTR_LN_BOBYQA| algorithm \citep{bobyqa} within the \verb|nloptr| \citep{nloptr} package.
-Finally, optimised starting values are fit to the non-linear mixture model using \verb|nlsLM()| in the \verb|minpack.lm| \citep{minpack.lm} package.\\
-\\
+<<echo = FALSE, fig.cap = '\\label{Fig:stt_examples} Mass loss and component estimation using default settings for test samples.', out.width = '.49\\linewidth', fig.show = 'hold'>>=
+t.testudinum <- process_test_samples('data/Tt_leaf.txt')
+t.testudinum_output <- deconvolve(t.testudinum)
+
+z.marina_rh <- process_test_samples('data/Zm_rhizome.txt')
+z.marina_rh_output <- deconvolve(z.marina_rh)
+
+z.marina_ro <- process_test_samples('data/Zm_root.txt')
+z.marina_ro_output <- deconvolve(z.marina_ro)
+
+decon_plot <- function (x, ...) {
+
+  temp <- seq(x$temp_bounds[1], x$temp_bounds[2], length.out = nrow(x$data))
+  data <- x$data
+  fit <- x$model_fit
+
+  params <- as.data.frame(summary(fit)$coefficients[,1])
+
+  par(mar = c(5, 5, 1, 1))
+  plot(data$temp_C, data$deriv, xlab = 'Temperature (C)',
+       ylab = expression(paste('Rate of mass loss (-dm/dT) (C'^'-1', ')')),
+       yaxs = 'i', ylim = c(0, max(data$deriv) + 0.06*max(data$deriv)),
+       pch = 20, cex = 0.5, cex.axis = 1.2, cex.lab = 1.5)
+
+  if (x$n_peaks == 4) {
+      y1 <- fs_mixture(temp = temp,
+                       height_1 = params['height_1',],
+                       skew_1 = params['skew_1',],
+                       position_1 = params['position_1',],
+                       width_1 = params['width_1',],
+                       height_2 = params['height_2',],
+                       skew_2 = params['skew_2',],
+                       position_2 = params['position_2',],
+                       width_2 = params['width_2',],
+                       height_3 = params['height_3',],
+                       skew_3 = params['skew_3',],
+                       position_3 = params['position_3',],
+                       width_3 = params['width_3',],
+                       height_0 = params['height_0',],
+                       skew_0 = params['skew_0',],
+                       position_0 = params['position_0',],
+                       width_0 = params['width_0',])
+
+      y5 <- fs_function(temp,
+                        params['height_0',], params['skew_0',],
+                        params['position_0',], params['width_0',])
+
+      lines(temp, y5, lty = 6, lwd = 2.5, col = '#33638DFF')
+
+    }
+
+    if (x$n_peaks == 3) {
+
+      y1 <- fs_mixture(temp = temp,
+                       height_1 = params['height_1',],
+                       skew_1 = params['skew_1',],
+                       position_1 = params['position_1',],
+                       width_1 = params['width_1',],
+                       height_2 = params['height_2',],
+                       skew_2 = params['skew_2',],
+                       position_2 = params['position_2',],
+                       width_2 = params['width_2',],
+                       height_3 = params['height_3',],
+                       skew_3 = params['skew_3',],
+                       position_3 = params['position_3',],
+                       width_3 = params['width_3',])
+
+    }
+
+    y2 <- fs_function(temp,
+                      params['height_1',], params['skew_1',],
+                      params['position_1',], params['width_1',])
+    y3 <- fs_function(temp,
+                      params['height_2',], params['skew_2',],
+                      params['position_2',], params['width_2',])
+    y4 <- fs_function(temp,
+                      params['height_3',], params['skew_3',],
+                      params['position_3',], params['width_3',])
+
+    lines(temp, y1, lty = 1, lwd = 2)
+    lines(temp, y2, lty = 3, lwd = 3.5, col = '#440154FF')
+    lines(temp, y3, lty = 4, lwd = 3.5, col = '#B8DE29FF')
+    lines(temp, y4, lty = 5, lwd = 3.5, col = '#3CBB75FF')
+
+}
+
+# Species name legend
+legend_species <- function (spname, plant_part, y) {
+  legend(600, y,
+         xjust = 1,
+         legend = c(spname, plant_part),
+         text.font = c(3, 1),
+         cex = 1.6,
+         bty = 'n')
+}
+
+decon_plot(t.testudinum_output)
+legend_species('Thalassia testudinum', 'leaves', max(t.testudinum_output$data$deriv))
+decon_plot(z.marina_rh_output)
+legend_species('Zostera marina', 'rhizome', max(z.marina_rh_output$data$deriv))
+decon_plot(z.marina_ro_output)
+legend_species('Zostera marina', 'root', max(z.marina_ro_output$data$deriv))
+
+legend(800, max(z.marina_ro_output$data$deriv),
+       legend = c('DTG data', 'DTG modelled',
+                  'Hemicellulose 1', 'Hemicellulose 2',
+                  'Cellulose', 'Lignin'),
+       ncol = 1,
+       cex = 1.2,
+       bty = 'n',
+       lty = c(NA, 1, 6, 3, 4, 5),
+       pch = c(20, NA, NA, NA, NA, NA),
+       col = c('black', 'black', '#33638DFF',
+               '#440154FF', '#B8DE29FF', '#3CBB75FF'),
+       lwd = 2)
+
+@
+
+Default \verb|mixchar| settings did not, however, perfectly identify the fourth peak in the deconvolution of macroalgae species \textit{Ecklonia radiata} blades \citetext{Fig.~\ref{Fig:Er}a; \citealp{trevathan-tackett2015}}.
+In this case, we can use the option to specify our own starting values, with the \verb|start_vec|, \verb|lower_vec|, and \verb|upper_vec| arguments, in order to better guide the model (Fig.~\ref{Fig:Er}b).\\
+
+<<echo = FALSE>>=
+e.radiata <- process_test_samples('data/Er_blade.txt')
+e.radiata_output <- deconvolve(e.radiata)
+@
+
+<<>>=
+start_vec <- c(0.002, -0.15, 250, 50,           # for hemicellulose 1
+               0.003, -0.15, 310, 50,           # for hemicellulose 2
+               0.006, -0.15, 350, 30,           # for cellulose
+               0.001, -0.15, 410, 200)          # for lignin
+
+# change the upper bounds to ensure the starting vector values are within
+# the allowed range
+ub <- c(2, 0.2, 260, 80,
+        2, 0.2, 330, 90,
+        2, 0.2, 380, 50,
+        2, 0.2, 430, 250)
+
+e.radiata_decon <- deconvolve(e.radiata,
+                              n_peaks = 4,
+                              start_vec = start_vec,
+                              upper_vec = ub,
+                              lower_temp = 150,
+                              upper_temp = 600)
+@
+
+<<echo = FALSE, fig.cap = '\\label{Fig:Er} Component estimation for \\textit{Ecklonia radiata} blades with default (a) and specified starting values (b).', out.width = '.49\\linewidth', fig.align = 'center', fig.show = 'hold'>>=
+plot(e.radiata_output, bw = FALSE)
+text(170, max(e.radiata_output$data$deriv), '(a)', cex = 1.5)
+plot(e.radiata_decon, bw = FALSE)
+text(170, max(e.radiata_output$data$deriv), '(b)', cex = 1.5)
+@
 
 \textit{Component weights}\\
-Once overall curve parameters are fit, we can pass each component's parameter estimates to a single Fraser-Suzuki function, and calculate the weight of the component in the overall sample by integrating under the peak (Eq.~\ref{eqn:integration}).
+After we fit our curve parameters, we can pass each component's parameter estimates to a single Fraser-Suzuki function and integrate under the peak to calculate the weight of the component in the overall sample (Eq.~\ref{eqn:integration}).
 To estimate the uncertainty of the weight predictions, \verb|deconvolve| will calculate the 95\% interval of the weight estimates across a random sample of parameter estimates, drawn in proportion to their likelihood.
@@
 The second dataset included in the package, \verb|marsilea|, provides an example of a four-peak deconvolution.
-A worked example can be found in the package vignettes.
+A worked example can be found in the package vignettes.\\
+\\
+\textbf{\textit{Package outputs}}\\
+The output of the \verb|deconvolve| function is a list of five items:
+\begin{enumerate}
+\item{the dataset that results from the \verb|process| function, useful for testing other modelling approaches or plotting options, and accessed with \verb|rate_data()|:
 
-<<>>=
+<<echo = FALSE>>=
 output_juncus <- deconvolve(deriv_juncus)
-output_juncus
 @
 
-The output of the \verb|deconvolve| function is a list of five items:
-\begin{enumerate}
-\item{the data used to fit the function,
 <<>>=
@@
 }
-\item{the model fit including parameter estimates,
+\item{the output of the mixture model.
+Peak 1 is hemicellulose; peak 2 is cellulose; and peak 3 is lignin.
+If present, the optional fourth peak located at the lowest temperature interval will be listed as peak 0.
+Accessed with \verb|model_fit()|:
 <<eval = FALSE>>=
@@
 \end{enumerate}
-If you \verb|plot()| the output of the \verb|deconvolve| function you will see the result of the deconvolution (Fig.~\ref{Fig:decon}).
-This default plot shows the underlying DTG data, the overall mixture model curve, as well as the components peaks.
-The default plot is in black and white, but you can plot a colour version that uses colour-blind friendly \verb|viridis| colours \citep{viridis} by specifying \verb|bw = FALSE|.
+
+\textbf{\textit{Plotting}}\\
+Plotting the output of the \verb|deconvolve| function shows the underlying DTG data, the overall mixture model curve, as well as the component peaks of the deconvolution (Fig.~\ref{Fig:decon}).
+The default plot is in black and white, but a colour version that uses colour-blind friendly \verb|viridis| colours \citep{viridis} is available by specifying \verb|bw = FALSE|.
 
@@
 Mass loss data overlaid with output of deconvolution.
-Rate of mass loss scaled by initial mass of sample.', out.width = '0.7\\linewidth', asp = 1, fig.align = 'center'>>=
+Rate of mass loss scaled by initial mass of sample.', asp = 1, out.width = '.7\\linewidth', fig.align = 'center'>>=
 plot(output_juncus, bw = FALSE)
@@
 
-The Fraser-Suzuki family of functions are exported to allow users to create their own plots from the model outputs. Detailed descriptions of how to do so are included in the package vignettes.
+The Fraser-Suzuki family of functions are exported (Table~\ref{Tab:functions}) to allow users to create their own plots from the model outputs in conjunction with the parameter estimates, accessed as follows:
 
 <<>>=
-stt <- read.table("../mixchar.notes/USATtLeaf_data.txt", fill = TRUE, header = FALSE, skip = 46, skipNul = TRUE, fileEncoding="UTF-16LE")
-colnames(stt) <- c("time", "temp", "weight", "deriv")
+juncus_parameters <- model_parameters(output_juncus)
+juncus_parameters
 @
@@
 \begin{table}[!ht]
-	\caption{Exported functions}
+	\caption{Exported functions.}
 	\label{Tab:functions}
@@
 		Accessor function & \verb|component_weights()| & Access mean, upper, and lower bounds for component weight estimates \\
+		Accessor function & \verb|model_parameters()| & Access parameter estimates \\
 		Fraser-Suzuki function & \verb|fs_function()| & Fraser-Suzuki equation for a single peak \\
@@
 
-1. How robust is this (testing with Stacy’s data)
-show with a few samples
-- to show different machine
-- to show a variety of sample types
-how to include these in the manuscript?
-Discuss limitations of estimates
-how reliable are they?
-
-3.
-Mixture modelling is hard, with a large statistical literature.
-Google Geoff Maclachlan.
-He has written the seminal text Finite mixture models https://scholar.google.com/citations?user=1bYCHtsAAAAJ&hl=en
--- add a bit of a discussion section at end.
-Discuss nature of statistical inference of mixture models.
-quite tricky in general
-ref paper slike McLachlan and Peele
-requires good starting points
-many combinations of peaks create the same overall curve
-to use the package well, different starting values should be tested out.
-
-4. Future work
-The package was developed using thermogravimetric data for 29 different wetland plant species, as well as pure samples of cellulose (carboxy-methyl cellulose) and lignin (alkali lignin from Sigma Aldrich).
-These data came from the same TGA-FTIR machine and were exported in the same format.
-For this reason, the package was also tested on thermogravimetric data exported from a different machine in a different format, on different species and plant parts in order to test behaviour of the package.
-
-Below we present results from
-
-add in discussion that happy to develop for data of other machines/in other formats
-
-tools that already exist
-mixtools
-how does my approach compare with traditional mixture model estimation?
-
-Statistical inference of mixture models
-
 \section*{Quality control}
-All the functions of \verb|mixchar| were tested to see if they produced the desired output.
+All the functions of \verb|mixchar| were tested to see if they produce the desired output.
+The workflow was tested on thermogravimetric data from two different TGA-FTIR machines, and on samples outside those used to build the package.\\
+\\
+The structure of the package successfully passed the CRAN R CMD check with no errors or warnings, or notes and the results from this check can be found on CRAN.
 
@@
 	\item[Name:] CRAN
-	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
-	\item[Licence:] Open license under which the software is licensed.
-	\item[Publisher:] Name of the person who deposited the software.
+	\item[Persistent identifier:] \url{https://CRAN.R-project.org/package=mixchar}
+	\item[Licence:] MIT and open license as found on \\
+	\url{https://cran.r-project.org/web/packages/mixchar/LICENSE}
+	\item[Publisher:] Saras Windecker
 	\item[Version published:] 0.1.0
-	\item[Date published:] dd/mm/yy
+	\item[Date published:] 16/08/2018
 \end{description}
@@
 \begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] Github \url{https://github.com/smwindecker/mixchar/}
-	\item[Persistent identifier:] DOI:10.5281/zenodo.1343849 https://doi.org/10.5281/zenodo.1343849
-	\item[Licence:] MIT and open license as found on https://github.com/smwindecker/mixchar/releases/tag/v0.1.0.
+	\item[Name:] Github \\
+	\url{https://github.com/smwindecker/mixchar/}
+	\item[Persistent identifier:] DOI:10.5281/zenodo.1343849 \\
+	https://doi.org/10.5281/zenodo.1343849
+	\item[Licence:] MIT and open license as found on \\
+	\url{https://github.com/smwindecker/mixchar/releases/tag/v0.1.0.}
 	\item[Date published:] 11/08/2018
@@
 We expect that this package will be useful to researchers already using thermogravimetric analysis for carbon component estimation, as well as to functional ecologists seeking to test out this approach as an alternative to wet chemistry methods.
-For all users, this method provides a significant improvement on most current softwares available, as it allows fully open-source and transparent analyses.
+For all users, this method improves on most current softwares available to them, as it is fully open-source and transparent.\\
+\\
+Finite mixture models are used to cluster continuous multivariate data.
+Statistical inference of mixture models is notoriously difficult because of their flexibility \citep{mclachlan1988}.
+This is especially true for the Fraser-Suzuki function, which has an additional parameter compared to a Gaussian distribution.
+Many combinations of peaks can create the same overall derivative thermogravimetric curve, and so informed starting values are necessary as they can substantially affect fit.
+To use \verb|mixchar| well, we need in some cases to modify the default starting values.\\
 
-For those that wish to contribute to the package, it is hosted on Github.
-Contributors can log issues via the issues tracker (\url{https://github.com/smwindecker/mixchar/issues}) or submit a pull request to add functionality to the package.
+For those who wish to contribute to the package, it is hosted on Github.
+Contributors can log issues, for example concerning alternative data formats, via the issues tracker (\url{https://github.com/smwindecker/mixchar/issues}) or submit a pull request to add functionality to the package.
 
@@
 The authors would like to thank Dr.
-Nick Tierney and David Wilkinson for reviewing an early version of the package.
-We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for assistance in the field collecting plant specimens.
-We would like to thank the University of Melbourne Department of Chemical and Biomolecular Engineering for access to and training on the TGA-FTIR.
-Vegetation collection for data used to build and verify the model was conducted under Victorian Department of Environment, Land, Water and Planning Permit No 10007429.
+Nick Tierney and David Wilkinson for reviewing an early version of the package as well as CRAN reviewers for useful additions.
+We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for their assistance in the field collecting plant specimens.
+We would also like to thank the University of Melbourne Department of Chemical and Biomolecular Engineering for access to and training on the TGA-FTIR.
+We collected vegetation used to build and verify the model was conducted under Victorian Department of Environment, Land, Water and Planning Permit No 10007429.
 
 \section*{Funding statement}
-The authors would like to acknowledge support from the Australian Research Council Centre of Excellence for Environmental Decisions, the Holsworth Wildlife Reseach Endowment \& The Ecological Society of Australia, and the Melbourne International Research Scholarship and Melbourne International Fee Remission Scholarship from University of Melbourne.
+The authors would like to acknowledge the generous support we received from the Australian Research Council Centre of Excellence for Environmental Decisions, the Holsworth Wildlife Reseach Endowment \& The Ecological Society of Australia, and from University of Melbourne, which provided teh primary author with a Melbourne International Research Scholarship and a Melbourne International Fee Remission Scholarship from University of Melbourne.
 

### 2021-03-03 README.Rmd
update for 2021

@@
 [![CRAN](http://www.r-pkg.org/badges/version/mixchar)
+[![CRAN status](https://www.r-pkg.org/badges/version/mixchar)](https://CRAN.R-project.org/package=mixchar)
 [![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)

### 2021-03-03 README.Rmd

--- 2018-08-18 README.Rmd
@@
   md_document:
-    variant: markdown_github
+    variant: gfm
 ---
@@
 
-[![CRAN](http://www.r-pkg.org/badges/version/mixchar)
+[![CRAN](http://www.r-pkg.org/badges/version/mixchar)](https://cran.r-project.org/package=mixchar)
 [![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
